---
title: "Spurious Regressions"
author: "RWW"
date: "1/15/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Regression Basics

A regression of two completely random variables, in this case normal, should result in about 5% of t-statistics with p-values less than 0.05.  This is the basis for the interpretation of a p-value; how often would we see something this extreme or even more extreme randomly?

```{r}
NReg <- function(junk) {
y1 <- rnorm(200)
y2 <- rnorm(200)
return(summary(lm(y1~y2))$coefficients[2,4])
}
NReg.Result <- data.frame(Res=sapply(1:1000, function(x) {NReg(x)}))
table(NReg.Result$Res < 0.05)
```
Checks out.

## Regressions of Cumulated Time Series

```{r}
Spurious <- function(junk) {
y1 <- cumsum(rnorm(200))
y2 <- cumsum(rnorm(200))
return(summary(lm(y1~y2))$coefficients[2,4])
}
Spurious.Result <- data.frame(Res=sapply(1:1000, function(x) {Spurious(x)}))
```

Finally, let’s plot the p-values.

```{r}
Spurious.Result %>% ggplot(., aes(x=Res)) + geom_histogram(bins=20)
```

This is unexpected.  Over 80% are less than 0.05.  Let's understand a bit of why.  What does a series from each look like?

## Example Series

```{r}
par(mfrow=c(2,1))
plot(seq(1,1000), rnorm(1000), type="l")
plot(seq(1,1000), cumsum(rnorm(1000)), type="l")
```

