---
title: "tidy data Review"
subtitle: "Data 521"  
author: "Robert W. Walker"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE); library(tidyverse); library(dplyr)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer); library(kableExtra)
solarized_dark(
  code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css"
)
```


# An Overview of *dplyr* verbs

```{r, message=FALSE, warning=FALSE}
FastFood <- read_csv("https://github.com/rfordatascience/tidytuesday/raw/master/data/2018/2018-09-04/fastfood_calories.csv")
```


---

```{r, eval=FALSE}
library(skimr)
FastFood %>% skim()
```

---

<small>
```{r, echo=FALSE, results='markup'}
library(skimr)
FastFood %>% skim() %>% kable() %>% kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```
</small>

---
# dplyr verbs

There are four main `dplyr` verbs that we will play with, and some helpers. 
- filter   
--
- select   
--
- mutate   
--
- summarize or summarise  


---
class: center

# `filter()`


---
## filter [1 of 3]

`filter` selects rows according to some set of conditions.  
- Valid with `==`
- Can use `%in%` with a vector `c()`.


```{r}
FastFood %>% filter(restaurant == "Taco Bell")
FastFood %>% filter(restaurant %in% c("Taco Bell","Burger King"))
FastFood %>% filter(startsWith(restaurant,"S")==TRUE) %>% group_by(restaurant) %>% skim()
```


---
## filter [2 of 3]

`filter` selects rows according to some set of conditions.  
- Can use `%in%` with a vector `c()`.

<small>
```{r}
FastFood %>% filter(restaurant%in%c("Taco Bell","Burger King"))
```
</small>

---
## filter [3 of 3]

`filter` selects rows according to some set of conditions.  
- Or more elaborate combinations of elements
- It has to return a logical [TRUE/FALSE] to filter the rows.

---

<small>
```{r, results='markup'}
FastFood %>% filter(startsWith(restaurant,"S")==TRUE) %>% group_by(restaurant) %>% skim() %>% kable() %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
</small>


---
# Inversion with !

<small>
```{r, results='markup'}
FastFood %>% filter(!(startsWith(restaurant,"S")==TRUE)) %>% group_by(restaurant) %>% skim() %>% kable() %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
</small>


---
class: center, middle

# `select()`


---
class: inverse
## select [1/2]

`select` selects columns according to some set of names/conditions.  

<small>
```{r}
FastFood %>% select(restaurant, calories)
```

---
class: inverse
## select [2/2]

`select` selects columns according to some set of names/conditions.  

<small>
```{r}
FastFood %>% select(restaurant,starts_with("vit"))
```

---
class: inverse
## select [2/2]

`select` selects columns according to some set of names/conditions.  Negative selection can occur.

<small>
```{r}
FastFood %>% select(-restaurant)
```



---
class: center, middle

# `mutate()`


---
# mutate [and transmute]

`mutate()` and `transmute()` are the core method for adding variables [columns] to existing data.  The key difference is that `mutate()` retains existing variables while `transmute()` drops them.  Let's see it for sodium, rescaled to grams.

*mutate* will keep all columns.

<small>
```{r}
FastFood %>% 
  mutate(Sodium.Grams = sodium / 1000) %>%
  select(restaurant,Sodium.Grams,sodium,everything())
```
</small>


---
class: center, middle

# `transmute()`


---
## transmute

*transmute* will only keep the called columns.

<small>
```{r}
FastFood %>% transmute(Sodium.Grams = sodium / 1000)
# To keep a variable, copy it.
# FastFood %>% transmute(restaurant = restaurant, Sodium.Grams = sodium / 1000)
```
</small>

---
## NB: Reassigning or newly assigning

To make these `mutate()` a part of the data, we assign it a *new name* or reassign it.

<small>
```{r}
FastFood <- FastFood %>% mutate(Sodium.Grams = sodium / 1000)
My.Fast.Food <- FastFood %>% mutate(Sodium.Grams = sodium / 1000)
```

---

# `mutate()` and `transmute()` can be fancy
## Fixing a Frustration and a little Visual

Virtually all of these functions can embed other functions.  We can use mutate with functions to do pretty fancy things.  Let me isolate the chicken items.

```{r}
FastFood <- FastFood %>% mutate(Chicken = stringr::str_detect(item, 'Chicken|Chick-n'))
```

---

# What's the distribution of Chicken items by chain?

```{r, eval=FALSE}
ggplot(FastFood) +
 aes(x = restaurant, fill = Chicken) +
 geom_bar(position = "dodge") +
 coord_flip() +
 theme_minimal() +
 labs(x="", y="Menu Items", title="Chicken Menu Items by Fast Food Chain")
```


---

```{r, echo=FALSE}
ggplot(FastFood) +
 aes(x = restaurant, fill = Chicken) +
 geom_bar(position = "dodge") +
 coord_flip() +
 theme_minimal() +
 labs(x="", y="Menu Items", title="Chicken Menu Items by Fast Food Chain")
```




---
class: center, middle

# `group_by()`


---
# The Magic of `group_by`

`group_by` is a core `tidyverse` operator for repeating something by groups.  By itself, it simply splits a data object according to the grouping variable(s).

--

**But that is exactly what a pivot table does.**

---
# Grouping and pipes

<small>
```{r, results='markup'}
FastFood %>% group_by(restaurant) %>% skim() %>% kable() %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
</small>


---
# A Two Variable Pivot

<small>
```{r, results='markup'}
FastFood %>% group_by(restaurant,Chicken) %>% skim(Sodium.Grams) %>% kable() %>% kable_styling() %>% scroll_box(width = "100%", height = "50%")
```
</small>

---
# summarise / summarize

Is the analog to creating a pivot table in R by whatever groupings we wish.

```{r}
FastFood %>% group_by(restaurant) %>% summarise(Mean.Protein = mean(protein), Mean.Protein.NA = mean(protein, na.rm=TRUE))
```

---
# summarise

Is the analog to creating a pivot table in R by whatever groupings we wish.

```{r}
FastFood %>% group_by(restaurant, Chicken) %>% summarise(Mean.Protein = mean(protein), Mean.Protein.NA = mean(protein, na.rm=TRUE))
```


---
# ungroup()

We need `ungroup()` when we want to combine `mutate()` and `group_by()` to calculate aggregate statistics for all relevant rows.  Objects retain their `grouped` status unless we actively remove it.

<small>
```{r}
FastFood <- FastFood %>% 
  group_by(restaurant) %>% 
  mutate(Avg.Protein = mean(protein, na.rm=TRUE), Protein.Dev = protein - Avg.Protein) %>%
  ungroup()
```
</small>

---
class: center, middle

# `arrange()`


---
# arrange() [1/2]

We can use arrange to sort a result.  For example,

```{r}
FastFood %>% 
  group_by(restaurant) %>% 
  summarise(Avg.Calories = mean(calories)) %>% 
  arrange(Avg.Calories)
```

---
# arrange() [2/2]

We can use arrange to sort a result, and `desc()` to flip it.  For example,

```{r}
FastFood %>% 
  group_by(restaurant) %>% 
  summarise(Avg.Calories = mean(calories)) %>% 
  arrange(desc(Avg.Calories))
```

---
# A Basic Table: Counts

```{r}
( Restaurant.Table <- FastFood %>% group_by(restaurant) %>% summarise(Count = n()) %>% arrange(Count) )
```

---
# A More Elaborate Table: Counts

```{r}
( Rest.Chicken.Table <- FastFood %>% group_by(restaurant,Chicken) %>% summarise(Count = n()) )
```


---
# A First Data Visualisation [Chained]

```{r}
FastFood %>% 
  group_by(restaurant) %>% 
  summarise(Count = n()) %>%
  ggplot() + aes(x=restaurant, y=Count) + geom_col()
```

---
# Adding in Chicken

```{r}
FastFood %>% 
    group_by(restaurant, Chicken) %>% #<<
    summarise(Count = n()) %>%
    ggplot() + aes(x=restaurant, y=Count, fill=Chicken) + geom_col() #<<
```

---
# More Chaining [`fct_reorder()`]

```{r}
FastFood %>% group_by(restaurant) %>% summarise(Count = n()) %>% ggplot() + aes(x=fct_reorder(restaurant, Count), y=Count) + geom_col() + labs(x="Chain", y="Count") + coord_flip() 
```

---
# Even More Chaining

```{r, fig.height=6}
FastFood %>% group_by(restaurant) %>% summarise(Count = n()) %>% ggplot() + aes(x=fct_reorder(restaurant, desc(Count)), y=Count) + geom_col() + labs(x="Chain", y="Count") + coord_flip() 
```

---
class: inverse

# A Note on Skim

We could do it by hand.

```{r}
FastFood %>% group_by(restaurant) %>% 
  summarise(Mean = mean(calories, na.rm=TRUE), 
            SD = sd(calories, na.rm=TRUE), 
            Min = min(calories, na.rm=TRUE), 
            Median = median(calories, na.rm=TRUE), 
            Max = max(calories, na.rm=TRUE), 
            Q1 = quantile(calories, 0.25, na.rm=TRUE), 
            Q3 = quantile(calories, 0.75, na.rm=TRUE))
```

---
class: inverse

# A Recap

.pull-left[
**Four `dplyr` verbs:**  
- `filter()`  
- `select()`  
- `mutate()` / `transmute()`  
- `summarise()`  
]

.pull-right[
**Two helpers:**  
- `group_by()` and `ungroup()`  
- `arrange()` and `desc()`  
]

---
class: inverse

### Something A Little Bit **Crazy** `r emo::ji("shrug")`

Take our summary function from above.  But now let me embed it in a function so that it will do it for any variable.  Though it will work with any name [calories would do], I will be explicit.  There are some [highlighted] programming tricks here but this could be adapted to any functions we might want.

```{r, echo=TRUE, eval=FALSE}
library(rlang)
summarise.me <- function(data, var) {   #<<
  data <- as.data.frame(data); var <- ensym(var)  #<<
Res <- data %>% summarise(Mean = mean(!! var, na.rm=TRUE), #<<
            SD = sd(!! var, na.rm=TRUE),
            Min = min(!! var, na.rm=TRUE), 
            Q1 = quantile(!! var, 0.25, na.rm=TRUE), 
            Median = median(!! var, na.rm=TRUE), 
            Q3 = quantile(!! var, 0.75, na.rm=TRUE),
            Max = max(!! var, na.rm=TRUE))
return(Res)
}
FastFood %>% summarise.me(., protein)
```

---

```{r, echo=FALSE}
library(rlang)
summarise.me <- function(data, var) {   #<<
  data <- as.data.frame(data); var <- ensym(var)  #<<
Res <- data %>% summarise(Mean = mean(!! var, na.rm=TRUE), #<<
            SD = sd(!! var, na.rm=TRUE),
            Min = min(!! var, na.rm=TRUE), 
            Q1 = quantile(!! var, 0.25, na.rm=TRUE), 
            Median = median(!! var, na.rm=TRUE), 
            Q3 = quantile(!! var, 0.75, na.rm=TRUE),
            Max = max(!! var, na.rm=TRUE))
return(Res)
}
# . is the short form name of whatever is passed in the pipe.  Here it is a data.frame.
FastFood %>% summarise.me(., protein)
# Equivalent to summarise.me(FastFood, protein)
```
