---
title: "telco"
author: "Robert W. Walker"
date: "2020-02-19"
output:
   html_document:
     self_contained: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# telco Churn

The loss of customers is known as churn.  Here is some data on telephone companies that gives us a number of features of the customer and the billing history relevant to this.

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(skimr)
telco <- read_csv(url("https://github.com/robertwwalker/DADMStuff/raw/master/WA_Fn-UseC_-Telco-Customer-Churn.csv"))
skim(telco)
telco <- telco[complete.cases(telco),] # Keep only rows with complete cases
telco.analyse <- telco %>% select(-customerID) # Drop customer ID
telco.F <- mutate_if(telco.analyse, is.character, as.factor)
```


```
install.packages("DataExplorer")
library(DataExplorer)
# Run separately
create_report(telco.F)
```

Remove the missing data.  The outcome of interest is Churn.  Let's look at it and take on a few examples from proportions.  Because it is Yes and No, everything will be about the probability of No unless we turn them to factors and order them backwards.  I will just describe this as the probability of *retention*.

```{r}
Paperless <- telco.analyse %>% filter(PaperlessBilling=="Yes")
Tab.PaperlessY <- xtabs(~PaperlessBilling+Churn, data=Paperless)
prop.table(Tab.PaperlessY, 1)
prop.test(Tab.PaperlessY)
```

For the paperless customers, the probability of retention is 0.65 to 0.68 with 95% confidence.  For the paper customers, we have...

```{r}
PaperBill <- telco.analyse %>% filter(PaperlessBilling=="Yes")
Tab.PaperlessN <- xtabs(~PaperlessBilling+Churn, data=PaperBill)
prop.table(Tab.PaperlessN, 1)
prop.test(Tab.PaperlessN)
```

The probability of retention ranges from 0.82 to 0.85 with 95% confidence.  Because they do not overlap, there must be a difference and paperless customers churn more.

## Comparisons

```{r}
( Tab.Paperless <- xtabs(~PaperlessBilling+Churn, data=telco.analyse) )
prop.table(Tab.Paperless, 1)
prop.test(Tab.Paperless)
```

Paperless clients have a probability of churning that is 0.152 to 0.192 higher than non-paperless clients.

## Phone Service?

Is there a difference in Churn between those with and without phone service?

```{r}
( Tab.PS <- xtabs(~PhoneService+Churn, data=telco.analyse) )
prop.table(Tab.PS, 1)
prop.test(Tab.PS)
```

It seems not.  Those without phone service could be 0.017 less likely or 0.053 more likely to be retained; no difference is certainly among the plausible values.

## Contracts?

```{r}
(Tab.Contract <- table(telco.analyse$Contract, telco.analyse$Churn))
prop.table(Tab.Contract, 1)
prop.test(Tab.Contract)
```
With more than two proportions, the question is, `are the probabilities of churn the same or not`.

Perhaps we should reexamine the row dimension to combine those under contracts of different lengths to one.

# Contracts: Yes or No

First, use mutate to separate those under contract from those that are month-to-month.  Second, I will examine the table and the proportions from the table calculated by rows.

```{r}
TAC <- telco.analyse %>% mutate(No.Contract = (Contract=="Month-to-month"))
table(TAC$No.Contract, TAC$Churn)
prop.table(table(TAC$No.Contract, TAC$Churn), 1)
```

Those under contract have a six percent churn rate while those not under contract churn just under forty-three percent of the time.  It is likely that contracts are a very useful way to diminish the likelihood of churn.  How much?  We can use the test of proportions to examine this.

```{r}
prop.test(table(TAC$No.Contract, TAC$Churn))
```

In evaluating the claim of no difference, the probability of no difference is estimated to be basically zero [2.2e-16].  So what are the likely values?  With 95% confidence, the probability of churning is between 0.34 and 0.377 more likely for those without a contract.
