---
title: tidyTuesday - Tuition
author: RWW
date: '2018-04-03'
slug: tidytuesday-tuition
categories:
  - R
  - tidyverse
tags:
  - tidyverse
  - R
  - tidyTuesday
---

I found a great example on tidyTuesday that I wanted to work on.  `@JakeKaupp` tweeted his `#tidyTuesday`: a very cool slope plot of tuition changes averaged by state over the last decade.  It is a very informative graphic.  The only tweak is a simple embedded line plot that uses color in a creative way to show growth rates.  All of the R code for this is on [Jake Kaupp's GitHub](https://github.com/jkaupp).  The specific file is [here](https://raw.githubusercontent.com/jkaupp/tidyweek/master/R/plot.R).  I did not add much.  All I wanted was some idea of how the growth rates correspond over the period.  I added a cumulative growth rate and encoded the color scheme with it enabling me to play with *viridis*.  The *col_tab* is my creation.  I also moved around the labels so that everyone gets a color coded label and we can see who is where, more or less.  Enjoy!

```{r BorrowedCode, message=FALSE, warning=FALSE, fig.height=8, fig.width=8}
library(readxl)
library(tidyverse)
library(glue)
library(ggrepel)
library(viridis)
tidy_data <-  readRDS(url("https://github.com/robertwwalker/academic-mymod/raw/master/data/tuition/Tuition.rds")) %>%
  gather(year, avg_tuition, -State) %>%
  rename(state = State)

# tidy_data <-  readRDS("../../data/tuition/Tuition.rds") %>%
#  gather(year, avg_tuition, -State) %>%
#  rename(state = State)

nat_avg <- tidy_data %>%
  filter(year %in% c("2005-06", "2015-16")) %>%
  group_by(year) %>%
  summarize(avg_tuition = mean(avg_tuition)) %>%
  mutate(state = "National Average")


plot_data <- tidy_data %>%
  filter(year %in% c("2005-06", "2015-16")) %>%
  left_join(select(nat_avg, year, nat_avg = avg_tuition), by = "year") %>%
  bind_rows(nat_avg)

labels <- plot_data %>%
  group_by(state) %>%
  filter(all(avg_tuition > nat_avg)) %>%
  pull(state) %>%
  unique()

plot <- plot_data %>%
  ggplot(., aes(x = year, y = avg_tuition, group = state)) +
  geom_text_repel(data = filter(plot_data, state %in% labels, year == "2015-16"), aes(label = state), direction = "y", nudge_x = 0.1, segment.size = 0.1, hjust = 0, family = "Oxygen", size = 3) +
  geom_path(color = "grey50", size = 0.5, alpha = 0.5) +
  geom_point(color = "grey50") +
  geom_path(data = nat_avg, color = "red", size = 1) +
  geom_point(data = nat_avg, color = "red") +
  scale_y_continuous(labels = scales::dollar) +
  labs(x = NULL, y = NULL, title = "Comparison of the average US tuition growth between 2005 and 2015", subtitle = "Eastern and Northeastern students consistently face tutition above the national average, indicated by the red line.", caption = "\nData: http://trends.collegeboard.org/ | Graphic: @jakekaupp") +
  theme_minimal(base_family = "Oswald-Light") +
  theme(panel.grid.minor = element_blank())
print(plot)
```

Now I will modify the original that is kept intact above.

```{r ModPlot}
nat_avg <- tidy_data %>%
  filter(year %in% c("2005-06", "2015-16")) %>%
  group_by(year) %>%
  summarize(avg_tuition = mean(avg_tuition)) %>%
  mutate(state = "National Average")


plot_data <- tidy_data %>%
  filter(year %in% c("2005-06", "2015-16")) %>%
  left_join(select(nat_avg, year, nat_avg = avg_tuition), by = "year") %>%
  bind_rows(nat_avg)

col_tab <- plot_data %>%
    filter(year %in% c("2005-06", "2015-16")) %>%
    group_by(state) %>% 
    mutate(Cum.Growth.Rate = ((avg_tuition - lag(avg_tuition))/lag(avg_tuition)))
col_tab <- col_tab %>% drop_na()
# Join Up the color table
plot_data <- plot_data %>% left_join(select(col_tab, state, Cum.Growth.Rate), by="state")
plot_data <- plot_data %>% 
              arrange(avg_tuition)

labels <- plot_data %>%
      pull(state) %>%
      unique()

my.plot <- plot_data %>%
  ggplot(., aes(x = year, y = avg_tuition, group = state, colour=Cum.Growth.Rate)) +
  geom_path(size = 0.5, alpha = 0.5) + 
  geom_point() + scale_color_viridis(name="Growth") +
  geom_path(data = nat_avg, color = "red", size = 1) +
  geom_point(data = nat_avg, color = "red") +
  scale_y_continuous(labels = scales::dollar) + 
  geom_text_repel(data = filter(plot_data, state %in% labels, year == "2015-16"), aes(label = state), direction = "both", nudge_x = 0.4, nudge_y = 1, segment.size = 0.1, family = "Oxygen", size = 2) +
  labs(x = NULL, y = NULL, title = "Comparison of the average US tuition growth between 2005 and 2015", subtitle = "Eastern and Northeastern students consistently face tutition above the national average [red line].", caption = "\nData: http://trends.collegeboard.org/ | Graphic: @jakekaupp | Tweak color:@PieRatio", cex=0.7) +
  theme_minimal(base_family = "Oswald-Light") +
  theme(panel.grid.minor = element_blank())
ggsave(my.plot, filename = glue('tidyweek-{Sys.Date()}.png'), height = 8, width = 8, dpi = 300)
print(my.plot)
```

