---
title: tidyTuesday Measles
author: RWW
date: '2019-12-16'
slug: tidytuesday-measles
categories:
  - tidyverse
  - R
  - animation
tags:
  - tidyTuesday
  - R
  - gganimate
header:
  caption: ''
  image: ''
  preview: yes
---


## tidyTuesday: December 10, 2019

Replicating plots from [simplystatistics](https://simplystatistics.org/2019/08/28/you-can-replicate-almost-any-plot-with-ggplot2/).  One nice twist is the development of a tidytuesdayR package to grab the necessary data in an easy way.  You can install the package via github.  I will also use `fiftystater` and `ggflags`.

```
devtools::install_github("thebioengineer/tidytuesdayR")
devtools::install_github("ellisp/ggflags")
devtools::install_github("wmurphyrd/fiftystater")
```


```{r}
tuesdata <- tidytuesdayR::tt_load(2019, week = 50)
```


```{r cars}
library(here)
library(tidyverse)
library(ggplot2)
library(ggflags)
library(countrycode)

dat <- tibble(country = toupper(c("US", "Italy", "Canada", "UK", "Japan", "Germany", "France", "Russia")),
              count = c(3.2, 0.71, 0.5, 0.1, 0, 0.2, 0.1, 0),
              label = c(as.character(c(3.2, 0.71, 0.5, 0.1, 0, 0.2, 0.1)), "No Data"),
              code = c("us", "it", "ca", "gb", "jp", "de", "fr", "ru"))

dat %>% mutate(country = reorder(country, -count)) %>%
  ggplot(aes(country, count, label = label)) +
  geom_bar(stat = "identity", fill = "darkred") +
  geom_text(nudge_y = 0.2, color = "darkred", size = 5) +
  geom_flag(y = -.5, aes(country = code), size = 12) +
  scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4)) +   
  geom_text(aes(6.25, 3.8, label = "Source UNODC Homicide Statistics")) + 
  ggtitle(toupper("Homicide Per 100,000 in G-8 Countries")) + 
  xlab("") + 
  ylab("# of gun-related homicides\nper 100,000 people") +
  ggthemes::theme_economist() +
  theme(axis.text.x = element_text(size = 8, vjust = -16),
        axis.ticks.x = element_blank(),
        axis.line.x = element_blank(),
        plot.margin = unit(c(1,1,1,1), "cm")) -> plot2
library(gganimate)
plot2 + transition_manual(code, cumulative=TRUE)
```

Just an animation of the original.  The next one took some playing but ended up exactly how I wanted it.

# Diseases

```{r}
the_disease <- "Measles"
dat <- tuesdata$diseases %>%
  filter(disease == the_disease) %>%
  mutate(rate = count / population * 10000 * 52 / weeks_reporting) 
jet.colors <- colorRampPalette(c("#F0FFFF", "cyan", "#007FFF", "yellow", "#FFBF00", "orange", "red", "#7F0000"), bias = 2.25)
my.dat1 <- dat %>% mutate(state = reorder(state, desc(state)))
my.dat2 <- dat %>% mutate(state = reorder(state, desc(state)), year2 = year)
  ggplot(my.dat1, aes(x=year, y=state, fill = rate)) +
  geom_tile(color = "white", size = 0.35, alpha = 0.2) +
  scale_x_continuous(expand = c(0,0)) +
  scale_fill_gradientn(colors = jet.colors(16), na.value = 'white') +
  theme_minimal() + guides(alpha=FALSE, rate=FALSE) +
  theme(panel.grid = element_blank()) +
        coord_cartesian(clip = 'off') +
        ggtitle(the_disease, subtitle = "{current_frame}") +
        ylab("") +
        xlab("") +  
        theme(legend.position = "bottom", text = element_text(size = 8)) + 
        annotate(geom = "text", x = 1963, y = 50.5, label = "Vaccine introduced", size = 3, hjust = 0) +
  geom_tile(data = my.dat2, aes(x=year, y=state, fill = rate)) + geom_vline(xintercept = 1963, col = "black") -> plotD
library(gganimate)
plotD <- plotD + transition_manual(year2, cumulative=TRUE)
# anim_save(here("static","img","tidyTuesday.gif"), animation = plotD)
plotD
```

# Now a map

```{r}
library(fiftystater)
data("fifty_states") # this line is optional due to lazy data loading
head(fifty_states)
my.dat1 <- dat <- tuesdata$diseases %>%
  filter(disease == the_disease) %>%
  mutate(rate = count / population * 10000 * 52 / weeks_reporting) %>% mutate(state = tolower(state))
data("fifty_states") # this line is optional due to lazy data loading
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
crimes2 <- left_join(crimes, my.dat1)
# map_id creates the aesthetic mapping to the state name column in your data
p <- ggplot(crimes2, aes(map_id = state)) + 
  # map points to the fifty_states shape data
  geom_map(aes(fill = rate), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  scale_fill_gradientn(colors = jet.colors(16), na.value = 'white') +
  labs(x = "", y = "", title = the_disease, subtitle = "{current_frame}") +
  theme(legend.position = "bottom", 
        panel.background = element_blank())
p1 <- p + transition_manual(year, cumulative = FALSE)
# anim_save(here("static","img","animMap.gif"), animation = p1)
p1
```

I found a post on [stackoverflow](https://stackoverflow.com/questions/55967894/combining-two-animated-plot-into-one-gif-mp4) to assist in putting them together.

```{r, eval=FALSE}
appendGIFs <- function(gif1, gif2, gifout="result.gif", vertically=FALSE, 
                       delay=20, convert = "/usr/bin/convert"){
  currentdir <- getwd()
  on.exit(setwd(currentdir))
  tmpdir <- tempdir()
  invisible(file.remove(list.files(tmpdir, full.names = TRUE, pattern = "*.gif$")))
  file.copy(gif1, to = file.path(tmpdir, "gif1.gif"))
  file.copy(gif2, to = file.path(tmpdir, "gif2.gif"))
  setwd(tmpdir)
  command <- sprintf("%s gif1.gif -coalesce gif1-%%05d.gif", convert)
  system(command)
  command <- sprintf("%s gif2.gif -coalesce gif2-%%05d.gif", convert)
  system(command)
  nframes <- length(list.files(tmpdir, pattern = "^gif1-.*gif$"))
  for(i in 1:nframes){
    command <- sprintf("%s gif1-%05d.gif gif2-%05d.gif %sappend gif-%05d.gif", 
                       convert, i-1, i-1, ifelse(vertically, "-", "+"), i)
    system(command)
  }
  command <- sprintf("%s -loop 0 -delay %d gif-*.gif result.gif", convert, delay)
  system(command)
  file.copy("result.gif", file.path(currentdir, gifout), overwrite=TRUE)
}
# appendGIFs(here("static","img","tidyTuesday.gif"),here("static","img","mapAnim.gif"), gifout = here("static","img","result.gif"))
```



<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Wow, you can side-by-side gganimates with imagemagick. That was fun to put together. <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/tidyTuesday?src=hash&amp;ref_src=twsrc%5Etfw">#tidyTuesday</a> An adaptation of measles and a map... <a href="https://t.co/FPOgAOQS84">pic.twitter.com/FPOgAOQS84</a></p>&mdash; Robert Walker (@PieRatio) <a href="https://twitter.com/PieRatio/status/1206508341750456320?ref_src=twsrc%5Etfw">December 16, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
