---
title: 'Non-Profits in Oregon: Socrata is Cool'
author: Robert W. Walker
date: '2020-05-01'
slug: non-profits-in-oregon-socrata-is-cool
categories:
  - R
  - tidyverse
tags:
  - R Markdown
  - Maps
subtitle: ''
summary: ''
authors: []
lastmod: '2020-05-01T23:04:07-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(tidyverse)
library(tigris)
library(sf)
library(forcats)
library(ggthemes)
```


# Socrata: The Open Data Portal

I did not previously know much about precisely how open data portals had evolved.  Oregon's is quite nice and I will take the opportunity to map and summarise non-profits throughout the state.  Here is the data.

```{r}
library(RSocrata)
Oregon.Nonprofits <- read.socrata("https://data.oregon.gov/resource/8kyv-b2kw.csv")
glimpse(Oregon.Nonprofits)
```

## A basic zip code map

```{r, tigris_use_cache = TRUE, results='hide'}
or_zips <- zctas(cb = TRUE, starts_with = "97", class="sf")
or_zips %>% ggplot(., aes(geometry=geometry, group=ZCTA5CE10)) + geom_sf()
```

## Join a summary table by zip code.

I am not exactly sure why this happens.  For whatever reason, the map always has missing chunks

```{r}
ON <- Oregon.Nonprofits %>% group_by(zip_code) %>% summarise(Nonprofits = n_distinct(registry_number)) %>% ungroup()
Map.Me <- left_join(or_zips, ON, by=c("ZCTA5CE10" = "zip_code"))
Map.Me %>% ggplot(., aes(geometry=geometry, fill=Nonprofits)) + geom_sf() + scale_fill_viridis_c()
```

## Some Summary

```{r}
Oregon.Nonprofits %>% 
  group_by(nonprofit_type) %>% 
  summarise(count = n_distinct(registry_number)) %>% 
  ggplot(., aes(x=fct_reorder(stringr::str_wrap(nonprofit_type, 10), count), y=count, fill=nonprofit_type)) + 
  geom_col() + 
  scale_fill_viridis_d() + 
  coord_flip() + 
  labs(title="The Distribution of Oregon Non-Profits", fill="Type", x="") + 
  guides(fill=FALSE) + 
  theme_minimal()
```

