---
title: Visualizing One Quantitative Variable
author: Robert W. Walker
date: '2020-09-13'
slug: visualize-one-quantity
categories:
  - R
tags:
  - plot
subtitle: ''
summary: ''
authors: []
lastmod: '2020-09-13T20:04:06-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=TRUE)
library(tidyverse)
```

# Bonds

A dataset for illustrating the various available visualizations needs a certain degree of richness with manageable size.  The dataset on *Bonds* contains three categorical and a few quantitative indicators sufficient to show what we might wish.

## Loading the Data

```{r}
Bonds <- read.csv(url("https://raw.githubusercontent.com/robertwwalker/DADMStuff/master/BondFunds.csv"))
```

## A Summary

```{r}
library(skimr)
Bonds %>% 
  skim()
```

Most data types are represented.  There is no time variable so dates and the visualizations that go with time series are omitted.

# Data Visualization

First, let us look at visualizations for one quantitative variable.  Let me focus on assets..

## `geom_histogram()`

A histogram divides the data into categories and counts the observations per category.  The width of the categories [on x] is determined by `binwidth=` or the binwidth can be calculated as a function of the range and the number of bins `bin=`.  I will define it as *Gen.Hist*.

### A Base Histogram

```{r}
Gen.Hist <- Bonds %>% 
  ggplot() + 
  aes(x=Assets) + 
  geom_histogram()
Gen.Hist
```


### Histograms [bins]

We can choose more bins. 50?  That is far more than the default of 30.

```{r}
Bin50.Hist <- Bonds %>% 
  ggplot() + 
  aes(x=Assets) + 
  geom_histogram(bins=50)
Bin50.Hist
```

We can also choose fewer bins.  I will choose 10.

```{r}
Bin10.Hist <- Bonds %>% 
  ggplot() + 
  aes(x=Assets) + 
  geom_histogram(bins=10)
Bin10.Hist
```


### Histograms [binwidth]

We can also set the width of bins in the metric of `x`; I will choose 500 (bigger).

```{r}
BinW500.Hist <- Bonds %>% 
  ggplot() + 
  aes(x=Assets) + 
  geom_histogram(binwidth=500)
BinW500.Hist
```

We can also set the width of bins in the metric of `x`; I will choose 50 (smaller width makes more bins).

```{r}
BinW50.Hist <- Bonds %>% 
  ggplot() + 
  aes(x=Assets) + 
  geom_histogram(binwidth=50)
BinW50.Hist
```

## `geom_dotplot()`

`geom_dotplot()` places a dot for every observation in the relevant bin.  We can control the size of the bins [in the original metric] with `binwidth=`.

### Small binwidth

```{r}
Bonds %>% 
    ggplot() + 
    aes(x=Assets) + 
    geom_dotplot(binwidth=10)
```


### Large binwidth

```{r}
Bonds %>% 
    ggplot() + 
    aes(x=Assets) + 
    geom_dotplot(binwidth=1000)
```

### An ?optimal? binwidth

Each dot represents a datum with bins of size 100.

```{r}
Bonds %>% 
    ggplot() + 
    aes(x=Assets) + 
    geom_dotplot(binwidth=100) + labs(y="")
```

## `geom_freqpoly()`

`geom_freqpoly()` is the line equivalent of a histogram.  The arguments are similar, the output doesn't include the bars as it does in the histogram.

```{r}
Bonds %>% 
  ggplot(., aes(x=Assets)) +
  geom_freqpoly()
```

### More bins

```{r}
Bonds %>% 
  ggplot(., aes(x=Assets)) +
  geom_freqpoly(bins=50)
```

### Fewer bins

```{r}
Bonds %>% 
  ggplot(., aes(x=Assets)) +
  geom_freqpoly(bins=10)
```


## `geom_area()`

Is a relative of the histogram with lines connecting the midpoints of the bins and an associated fill from zero.

### Defaults to 30 bins

```{r}
Bonds %>% 
  ggplot(., aes(x=Assets)) + 
  geom_area(stat="bin")
```

### Small binwidth with a large number of bins

I will color in the area with magenta and clean up the theme.

```{r}
Bonds %>% 
   ggplot(., aes(x=Assets)) + 
   geom_area(stat="bin", bins=100, fill="magenta") + theme_minimal()
```


## `geom_density()`

A relative of the histogram and the area plots above, the density plot smooths out the blocks of a histogram with a moving window [known as the bandwidth].


### `geom_density()` outlines


```{r}
Bonds %>% 
   ggplot(., aes(x=Assets)) + 
   geom_density(outline.type = "upper")
Bonds %>% 
   ggplot(., aes(x=Assets)) + 
   geom_density(outline.type = "lower")
Bonds %>% 
   ggplot(., aes(x=Assets)) + 
   geom_density(outline.type = "full")
```


### `geom_density()` adjust

Adjust applies a numeric correction to the bandwidth.  Numbers greater than 1 make the bandwidth bigger [and the graphic smoother] and numbers less than 1 [but greater than zero] make the bandwidth smaller and the graphic more jagged.


```{r}
Bonds %>% 
  ggplot(., aes(x=Assets)) +
  geom_density(adjust=2)
Bonds %>% 
  ggplot(., aes(x=Assets)) +
  geom_density(adjust=1/2)
```


## `geom_boxplot`

A boxplot shows a box of the first and third quartiles and a notch at the median.  The dots above or below denote points outside the hinges.  The hinges [default to 1.5*IQR] show a range of expected data while the individual dots show possible outliers outside the hinges.  To adjust the hinges, the argument `coef=1.5` can be adjusted.

```{r}
Bonds %>% ggplot(., aes(x=Assets)) +
  geom_boxplot()
```

## `geom_qq()`

To compare empirical and theoretical quantiles.  Comparing a distribution to the normal or others is common and this provides the tool for doing so.  The default is a normal.

The empirical cumulative distribution function arises when we sort a quantitative variable and show the percentiles below said value.

```{r}
Bonds %>% 
  ggplot(aes(sample=Assets)) +
  geom_qq()
```

## `stat_ecdf(geom = )`

We could do this with most geometries.  I will show a few.

### `stat_ecdf(geom = "step")`

```{r}
Bonds %>%  
  ggplot(aes(x=Assets)) + 
  stat_ecdf(geom = "point") + 
  stat_ecdf(geom = "step", alpha=0.1) + 
  labs(y="ECDF: Proportion less than Assets") + 
  theme_minimal()
```

### `stat_ecdf(geom = "point")`

```{r}
Bonds %>%  
  ggplot(aes(x=Assets)) + 
  stat_ecdf(geom = "point") + 
  stat_ecdf(geom = "step", alpha=0.1) + 
  labs(y="ECDF: Proportion less than Assets") + 
  theme_minimal()
```

### Combining two

```{r}
Bonds %>%  
  ggplot(aes(x=Assets)) + 
  stat_ecdf(geom = "point") + 
  stat_ecdf(geom = "step", alpha=0.1) + 
  labs(y="ECDF: Proportion less than Assets") + 
  theme_minimal()
```

### `stat_ecdf(geom = "line")`

```{r}
Bonds %>%  
  ggplot(aes(x=Assets)) + 
  stat_ecdf(geom = "line") + 
  labs(y="ECDF: Proportion less than Assets") + 
  theme_minimal()
```

### `stat_ecdf(geom = "area")`

```{r}
Bonds %>%  
  ggplot(aes(x=Assets)) + 
  stat_ecdf(geom = "area", alpha=0.2) + 
  labs(y="ECDF: Proportion less than Assets") + 
  theme_minimal()
```
