---
title: Trying out Leaflet
author: RWW
date: '2019-12-16'
slug: trying-out-leaflet
categories:
  - R
tags:
  - R
  - R Markdown
  - tidyTuesday
header:
  caption: ''
  image: ''
  preview: yes
---

# International Murders

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```


Are among the data for analysis in the tidyTuesday for December 10, 2019.  These are made for a map.

```{r}
library(tidyverse)
library(leaflet)
library(stringr)
library(sf)
library(here)
library(widgetframe)
library(htmlwidgets)
library(htmltools)
options(digits = 3)
set.seed(1234)
theme_set(theme_minimal())
library(tidytuesdayR)
tuesdata <- tt_load(2019, week = 50)
murders <- tuesdata$gun_murders
```

There isn't much data so it should make this a bit easier.  Now for some data.  As it happens, the best way I currently know how to do this is going to involve acquiring a spatial frame.  There is one in the package `tmap`.  First, to load it.  My names are upper case.

```{r}
library(tmap)
data("World")
World <- World %>% mutate(name = toupper(name))
murders[murders$country=="CZECH REPUBLIC","country"] <- "CZECH REP."
murders[murders$country=="HUNGRY","country"] <- "HUNGARY"
murders[murders$country=="REPUBLIC OF KOREA","country"] <- "KOREA"
World.M <- World %>% left_join(., murders, by = c( "name" = "country"))
World.M <- World.M %>% mutate(Murders = count)
tmap_style("white")
tmap_mode("view")
my.map <- tm_shape(World.M) +
    tm_polygons("Murders", title="", palette = "viridis") + tm_layout(panel.labels = "Gun Murders")
lf <- tmap_leaflet(my.map)
frameWidget(lf, height='600')
```

That's convenient because I think I can also modify this for something else.


```{r}
World.M.SF <- sf::as_Spatial(World.M)
l <- leaflet(World.M.SF) %>% setView(0,0,2) %>% addPolygons(weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.5,
    fillColor = ~colorQuantile("YlOrRd", Murders)(Murders),
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE))
esri <- grep("^Esri", providers, value = TRUE)
for (provider in esri) {
    l <- l %>% addProviderTiles(provider, group = provider)
}
l <- l %>%
    addLayersControl(baseGroups = names(esri),
                     options = layersControlOptions(collapsed = FALSE)) %>%
    addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
               position = "bottomleft") %>%
    htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
        })
    }")
# sf:::as_Spatial()
frameWidget(l, height = '600')
```

