---
title: Simple Point Maps in R
author: RWW
date: '2019-12-19'
slug: simple-point-maps-in-r
categories:
  - Maps
  - R
tags:
  - Maps
  - tidyverse
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```


# Mapping Points in R

My goal is a streamlined and self-contained freeware map maker with points denoting addresses.  It is a three step process that involves:  

1. Get a map.  
2. Geocode the addresses into latitude and longitude.  
3. Combine the the two with a first map layer and a second layer on top that contains the points.

From there, it is pretty easy to get fancy using ggplotly to put relevant text hovers into place.

## Get a map.

There are a few map sources that R can access.  Google has now made most features pay to access with generous free allocations.  It is worth it to sign up if one plans to use it frequently.  I have never actually paid for use but I do not use it much.  There are nice instructions in a post by [littlemissdata](https://www.littlemissdata.com/blog/maps).  The other issue is the type of map.  The coordinates are crucial and I will need a map that is bounded on latitude and longitude.  For that purpose, I think I will use `ggmap`.  The `register_google` line invokes my Google API key.


```{r}
library(tidyverse)
library(ggmap)
library(osmdata)
pdx_map <- get_map(getbb("portland oregon"), maptype = "roadmap")
ggmap(pdx_map)
```

## Load Some Data and Geocode it with Google

First, to get the data.  I will create some data using the Portland Center but it could easily be replaced with imported data.

```{r}
Portland.Center <- data.frame(address = c("905 NW 12th Ave, Portland, OR 97209"), stringsAsFactors = FALSE)
Portland.Center <- Portland.Center %>% mutate_geocode(., address)
Portland.Center
```

## Put them together

Because they are same source geocodings, this works directly.

```{r}
ggmap(pdx_map) + geom_point(data=Portland.Center, aes(x=lon, y=lat), size=3, color="magenta")
```

# Now to Try Without Google

First, an open source map.

```{r PDXMap}
pdx.map <- get_stamenmap(getbb("portland oregon"), 
                         zoom = 14)
ggmap(pdx.map)
```

# Free Geocode

```{r}
library(tmaptools)
Geocoded.PDX <- geocode_OSM(Portland.Center$address, as.data.frame = TRUE) %>% select(query, lat, lon)
p1 <- ggmap(pdx.map) + geom_point(data=Geocoded.PDX, aes(x=lon, y=lat, text=query), size=3, color="magenta")
library(plotly)
p1a <- ggplotly(p1)
htmlwidgets::saveWidget(
  widgetframe::frameableWidget(p1a), here:::here('static/img/widgets/smp1map.html'))
```

<iframe width="800" height="600" src="https://rww.science/img/widgets/smp1map.html" frameborder="0" allowfullscreen></iframe>

# Leaflet

A very cool toy is leaflet.  The markers work the way as geom_point but hovers can be replaced with popups of various forms.  I really like this.

```{r}
library(leaflet)
Geocoded.PDX
m <- leaflet() %>% addTiles() %>% addMarkers(., data=Geocoded.PDX, lng=~lon, lat=~lat, popup = ~query)
htmlwidgets::saveWidget(
  widgetframe::frameableWidget(m), here:::here('static/img/widgets/mmmap.html'))
```

<iframe width="600" height="600" src="https://rww.science/img/widgets/mmmap.html" frameborder="0" allowfullscreen></iframe>

