---
title: tidyTuesday does Pizza
author: RWW
date: '2019-10-09'
slug: tidytuesday-does-pizza
categories:
  - tidyverse
  - R
  - Maps
tags:
  - Maps
  - tidyTuesday
  - R
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(ggiraph)
library(ggthemes)
library(patchwork)
library(cowplot)
library(rayshader)
library(emojifont)
library(gridExtra)
library(extrafont)
```

## Pizza Ratings

The `#tidyTuesday` for this week involves pizza shop ratings data.  Let's see what we have.

```{r cars}
pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_jared.csv")
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv")
pizza_datafiniti <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_datafiniti.csv")
summary(pizza_jared)
```

```{r}
summary(pizza_datafiniti)
```

```{r}
summary(pizza_barstool)
```

I will use this data; it contains some Oregon pizzarias.

```{r}
pizza_datafiniti %>% filter(province=="OR")
```

For the first plot, let me show what is going on in Oregon.

```{r ORPizza}
pizzaData <- pizza_datafiniti %>% filter(province=="OR") %>% group_by(name) %>% mutate(Tcount = n(), PriceAvg = mean(price_range_max - price_range_min)) %>% ungroup()
p <- pizzaData %>% ggplot(.) + aes(x=reorder(name,PriceAvg), fill=PriceAvg) + geom_bar() + coord_flip() + labs(x="Pizza Restaurant", y="Count", title="Oregon Pizzerias", caption = "data from #tidyTuesday; sorted by Average Price")
p
```

Now I want a map.

```{r}
pizzaData$group <- 44
states <- map_data("state")
OR.df <- subset(states, region == "oregon")
OR_base <- ggplot(data = OR.df, mapping = aes(x = long, y = lat, group = group)) +
geom_polygon(color = "black", fill = "gray") + labs(title="Oregon Pizzerias")
OR_base
```

```{r}
OR.Pizza <- OR_base + geom_point(data = pizzaData, aes(y=latitude, x=longitude, group=group), color = "red")
OR.Pizza
```

Combine them into one picture

```{r}
grid.arrange(p,OR.Pizza, ncol=2)
```

Now to use a girafe to put this together interactively.

```{r}
theme_set(theme_minimal())
pizzaData <- pizzaData %>% mutate(name = str_remove(name, "['``]"))
# Build the barplot
gg1 <- ggplot(pizzaData, aes(x=reorder(name,PriceAvg), fill=PriceAvg)) +
  geom_bar_interactive(aes(x = name, tooltip = name, data_id = name))  + 
  coord_flip() + scale_fill_viridis_c() + theme(axis.text=element_text(size=8)) +
  labs(x="Pizza Restaurant", y="Count", caption = "data from #tidyTuesday", sub="sorted by Average Price") 
# Build the map
gg2 <- ggplot(data = OR.df, mapping = aes(x = long, y = lat, group = group)) +
  geom_polygon(fill=gray(0.95)) + 
  geom_text_interactive(data = pizzaData, aes(y=latitude, x=longitude, label=emoji('pizza'), tooltip = name, data_id = name), family='EmojiOne', size=2, color="orange") + 
  scale_color_viridis_c(guide=FALSE) +
  theme_nothing()
# Bind them together with girafe
a <- girafe( code = print(gg1 / gg2 + plot_annotation(title="Pizza in Oregon")))
library(widgetframe)
frameWidget(a, width = "100%", height = "100%")
```


The formatting of this is quite off.  For some reason, the frame doesn't control scroll and overplots.


# Rayshader

And a mini-rayshader.  This is a complete lift and replace of the vignette after calculating the Price Midpoint.

```{r, dev='svg'}
states <- map_data("state")
PDF <- pizza_datafiniti %>% mutate(Price.Midpoint = (price_range_min + price_range_max / 2))
mtplot <- ggplot(data = states, mapping = aes(x = long, y = lat)) +
  geom_polygon(color = "black", fill = "gray") + 
  geom_point(data=PDF, aes(x = longitude, y = latitude, color = Price.Midpoint)) + 
  scale_color_viridis_c() + theme_minimal()
plot_gg(mtplot, width = 3.5, multicore = TRUE, windowsize = c(1200, 1200), 
        zoom = 0.5, phi = 35, theta = 30, sunangle = 15, soliddepth = -20)
render_snapshot(clear = TRUE)
```

