---
title: Visualising COVID-19 in Oregon
author: Robert W. Walker
date: '2020-03-24'
slug: covid-19-county-maps-for-oregon
categories:
  - tidyverse
  - web scraping
tags:
  - tidyverse
  - R
subtitle: ''
summary: ''
authors: []
lastmod: '2020-03-24T13:46:49-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
library(tidyverse)
```

## Oregon COVID data

I now have a few days of data.  These data are current as of March 24, 2020.  I will present the first version of these visualizations here and then move the auto-update to a [different location](https://rww.science/r/covid/).  A messy first version of [the scraping exercise](https://rww.science/r/covid/scraping/) is at the bottom of this post.

```{r}
paste0("https://github.com/robertwwalker/rww-science/raw/master/content/R/COVID/data/OregonCOVID",Sys.Date(),".RData")
load(url(paste0("https://github.com/robertwwalker/rww-science/raw/master/content/R/COVID/data/OregonCOVID",Sys.Date(),".RData")))
```

## A base map

Load the `tigris` library then grab the map as an `sf` object; there is a `geom_sf` that makes them easy to work with.  Finally, I join the map to the data.

```{r, message=FALSE, warning=FALSE, results='hide'}
library(tigris); library(rgdal); library(htmltools); library(viridis); library(sf)
counties.t <- counties(state = "41", resolution = "500k", class="sf")
Map.Me <- left_join(counties.t,Oregon.COVID, by=c("NAME" = "County"))
```

# The Whole Thing: An Animation

I will use a ggplot to build Oregon's map and fill it with case numbers.  I have to repel the labels to prevent print overlap [using `ggrepel`], and scheme the colors with viridis.  The last step is to animate it by time.

```{r}
library(ggrepel); library(ggthemes); library(gganimate)
Anim1 <- Map.Me %>% 
  ggplot(., aes(geometry=geometry, fill=Number.of.cases, label=NAME, group=NAME)) + 
  geom_sf() +
  geom_label_repel(stat = "sf_coordinates",
    min.segment.length = 0,
    colour = "white",
    segment.colour = "white",
    size = 3,
    box.padding = unit(0.05, "lines"))  + scale_fill_continuous_tableau("Red") + theme_minimal() + labs(title="COVID-19 in Oregon", subtitle="{frame_time}", x="", y="", caption="Made with R, ggplot2, and ggrepel by @PieRatio \n data: https://govstatus.egov.com/OR-OHA-COVID-19") + transition_time(date)
ResA <- animate(Anim1, end_pause=100, nframes=200)
ResA
```

# Some Data on Testing

```{r}
OR.Testing <- Oregon.Tests %>% group_by(date) %>% summarise(Total = sum(Outcome))
Test1 <- Oregon.Tests %>% ggplot(.) + aes(x=date, y=Outcome, fill=Category, label=Outcome) + geom_col() + geom_label(col="magenta") + scale_fill_viridis_d() + labs(title="COVID-19 Testing in Oregon", y="Tests", subtitle="Total shown as label", caption = "data: https://govstatus.egov.com/OR-OHA-COVID-19") + geom_label(data=OR.Testing, aes(x=date, y=Total+100, label=Total), fill="white", color="black", inherit.aes = FALSE)
Test1
```

# Hospitalization Data

```{r}
Hos1 <- OR.Hosp %>% filter(Hospitalized.!="Total") %>% ggplot(., aes(x=date, y=Number.of.cases,fill=Hospitalized.)) + geom_col() + scale_fill_viridis_d() + labs(x="Date", y="Number of COVID Positives", fill="Hospitalized?", title="Hospitalization Status of COVID-19 Positives in Oregon")
Hos1
```

# Age Data

```{r}
Age1 <- OR.Ages %>% ggplot(., aes(x=date, y=Number.of.cases, fill=Age.group)) + geom_col() + scale_fill_viridis_d() + labs(x="Date", y="Number of COVID-19 Positives")
Age1
```


## A Mapping Function

To save time later, I turned the plots into a function so that I can use to reproduce each frame.  Two inputs to the function, the dataset that is always the merged data from above and the date that I want to plot located in `date1` in a `YYYY-MM-DD` format.

```{r}
Plot.COVID <- function(date1, data) {
data %>% filter(date==date1) %>%
  ggplot(., aes(geometry=geometry, fill=Number.of.cases, label=NAME)) + 
  geom_sf() +
  geom_label_repel(stat = "sf_coordinates",
    min.segment.length = 0,
    colour = "white",
    segment.colour = "white",
    size = 3,
    box.padding = unit(0.05, "lines"))  + scale_fill_continuous_tableau("Red") + 
    theme_minimal() + 
    labs(title="COVID-19 in Oregon", 
         subtitle=date1, x="", y="", 
         caption="Made with R, ggplot2, and ggrepel by @PieRatio \n data: https://govstatus.egov.com/OR-OHA-COVID-19")
}
```

## The Result for 03/18/2020

This is the first date for which I can find data.  The [waybackmachine](https://archive.org/web/) was crucial.

```{r}
Plot.COVID("2020-03-18", Map.Me)
```


## The Result for 03/19/2020

```{r}
Plot.COVID("2020-03-19", Map.Me)
```


## The Result for 03/20/2020

```{r}
Plot.COVID("2020-03-20", Map.Me)
```


## The Result for 03/21/2020

```{r}
Plot.COVID("2020-03-21", Map.Me)
```

## The Result for 03/22/2020

```{r}
Plot.COVID("2020-03-22", Map.Me)
```


## The Result for 03/23/2020

```{r}
Plot.COVID("2020-03-23", Map.Me)
```

## The Result for 03/24/2020

```{r}
Plot.COVID("2020-03-24", Map.Me)
```


## A Scraper

I have written some code here to grab the updates as they post them and add them to the dataset.  Now I need to set a cron job to evaluate this script daily.  It is also worth nothing that the script has required changing over time.  Because I am particularly interested in the county map here, I will only remove a single table.

```{r, eval=FALSE}
library(rvest)
load(paste0("OregonCOVID",Sys.Date()-1,".RData"))
webpage <- read_html("https://govstatus.egov.com/OR-OHA-COVID-19")
tbls <- html_nodes(webpage, "table")
tbls
COVID.New <- webpage %>%
        html_nodes("table") %>%
        .[2] %>%
        html_table(fill = TRUE) %>% data.frame()
# Oregon.Total <- COVID.New %>% mutate(date=as.Date(Sys.Date())) %>% filter(County=="Total") %>% bind_rows(.,Oregon.Total) 
Oregon.COVID <- COVID.New %>% mutate(date=as.Date(Sys.Date())) %>% filter(County!="Total") %>% bind_rows(.,Oregon.COVID) 
# save(Oregon.COVID, file=paste0("OregonCOVID",Sys.Date(),".RData"))
```

### Adding Historical Data Together

```{r, eval=FALSE}
comma.rm.to.numeric <- function(variable) {as.numeric(str_remove_all( {{variable}}, ",")) }
# A function to parse the tables
OHA.Corona <- function(website, date) {
webpage <- read_html(website)
COVID.Head <- webpage %>%
        html_nodes("table") %>%
        .[1] %>%
        html_table(fill = TRUE) %>% data.frame()  # %>% filter(!startsWith(.[[1]],"Total"))
Scraped.date <- names(COVID.Head)[1] %>% str_remove(.,"X.Oregon.Test.Results.as.of.") %>% str_remove(., "..8.00.a.m..Updated.daily.")
names(COVID.Head) <- c("Category","Outcome")
COVID.Head <- COVID.Head %>% mutate(Outcome = comma.rm.to.numeric(Outcome), date=as.Date(date), Scraped.date = Scraped.date) # %>% filter(!startsWith(.[[1]],"Total"))
COVID.County <- webpage %>%
        html_nodes("table") %>%
        .[2] %>%
        html_table(fill = TRUE) %>% 
        data.frame() %>% 
        mutate(date=as.Date(date), 
               Scraped.date = Scraped.date, 
               Negative.test.results = comma.rm.to.numeric(Negative.test.results))
COVID.Age <- webpage %>%
        html_nodes("table") %>%
        .[3] %>%
        html_table(fill = TRUE) %>% data.frame()  %>%  
        mutate(date=as.Date(date), Scraped.date = Scraped.date)
COVID.Hospitalized <- webpage %>%
        html_nodes("table") %>%
        .[4] %>%
        html_table(fill = TRUE) %>% 
        data.frame()  %>% 
        mutate(date=as.Date(date), Scraped.date = Scraped.date)
return(list(Header=COVID.Head, Counties = COVID.County, Ages = COVID.Age, Hospitalized = COVID.Hospitalized))
}
OHA.Corona.3 <- function(website, date) {
webpage <- read_html(website)
COVID.Head <- webpage %>%
        html_nodes("table") %>%
        .[1] %>%
        html_table(fill = TRUE) %>% data.frame() %>% filter(!startsWith(.[[1]],"Total"))
Scraped.date <- names(COVID.Head)[1] %>% str_remove(.,"X.Oregon.Test.Results.as.of.") %>% str_remove(., "..8.00.a.m..Updated.daily.")
names(COVID.Head) <- c("Category","Outcome")
COVID.Head <- COVID.Head %>% mutate(Outcome = as.numeric(str_remove(Outcome,",")))
COVID.Head <- COVID.Head %>% mutate(date=as.Date(date), Scraped.date = Scraped.date)
COVID.County <- webpage %>%
        html_nodes("table") %>%
        .[2] %>%
        html_table(fill = TRUE) %>% data.frame() %>% mutate(date=as.Date(date), Scraped.date = Scraped.date, Negative.test.results = as.numeric(str_remove_all(Negative.test.results, ",")))
COVID.Age <- webpage %>%
        html_nodes("table") %>%
        .[3] %>%
        html_table(fill = TRUE) %>% data.frame() %>% mutate(date=as.Date(date), Scraped.date = Scraped.date)
return(list(Header=COVID.Head, Counties = COVID.County, Ages = COVID.Age))
}
OHA.Corona.2 <- function(website, date) {
webpage <- read_html(website)
COVID.Head <- webpage %>%
        html_nodes("table") %>%
        .[1] %>%
        html_table(fill = TRUE) %>% 
        data.frame()
Scraped.date <- names(COVID.Head)[1] %>% str_remove(.,"X.Oregon.Test.Results.as.of.") %>% str_remove(., "..8.00.a.m..Updated.daily.")
names(COVID.Head) <- c("Category","Outcome")
COVID.Head <- COVID.Head %>% mutate(Outcome = as.numeric(str_remove(Outcome,",")))
COVID.Head <- COVID.Head %>% mutate(date=as.Date(date), Scraped.date = Scraped.date)
COVID.County <- webpage %>%
        html_nodes("table") %>%
        .[2] %>%
        html_table(fill = TRUE) %>% data.frame() %>% mutate(date=as.Date(date), Scraped.date = Scraped.date)
COVID.Age <- webpage %>%
        html_nodes("table") %>%
        .[3] %>%
        html_table(fill = TRUE) %>% data.frame()  %>% filter(!startsWith(.[[1]],"Total")) %>% mutate(date=as.Date(date), Scraped.date = Scraped.date)
return(list(Header=COVID.Head, Counties = COVID.County, Ages = COVID.Age))
}

# March 18 Update
Mar18 <- OHA.Corona.2(website="https://web.archive.org/web/20200319144434/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-18")
# March 19 Update
Mar19 <- OHA.Corona.2(website="https://web.archive.org/web/20200320152224/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-19")
# March 20 Update
Mar20 <- OHA.Corona.2(website="https://web.archive.org/web/20200320202955/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-20")
# March 21 Update
Mar21 <- OHA.Corona.3(website="https://web.archive.org/web/20200321211741/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-21")
# March 22 Update
Mar22 <- OHA.Corona.3("https://web.archive.org/web/20200322205228/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-22")
# March 23 Update
Mar23 <- OHA.Corona(website="https://web.archive.org/web/20200323192410/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-23")
# March 24 Update
Mar24 <- OHA.Corona(website="https://govstatus.egov.com/OR-OHA-COVID-19", date=as.character(Sys.Date()))
Oregon.Tests.All <- bind_rows(Mar24$Header,Mar23$Header,Mar22$Header,Mar21$Header,Mar20$Header,Mar19$Header,Mar18$Header)
Oregon.COVID.All <- bind_rows(Mar24$Counties,Mar23$Counties,Mar22$Counties,Mar21$Counties,Mar20$Counties,Mar19$Counties,Mar18$Counties)
Oregon.COVID.Total <- Oregon.COVID.All %>% filter(County=="Total")
Oregon.COVID <- Oregon.COVID.All %>% filter(County!="Total")
Oregon.Tests <- Oregon.Tests.All[!str_detect(Oregon.Tests.All$Category, "Total"),]
# save.image("~/Sandbox/awful/content/post/2020-03-22-covid-19-county-maps-for-oregon/data/OregonCOVID2020-03-24.RData")
```

