---
title: A Quick and Dirty Introduction to R
author: RWW
date: '2019-10-25'
slug: a-quick-and-dirty-introduction-to-r
categories:
  - R
  - tidyverse
tags:
  - GSM Data
header:
  caption: ''
  image: ''
---

# Some Data

I will start with some inline data.  

```{r, message=FALSE, warning=FALSE}
library(tidyverse); library(skimr);
Support.Times <- structure(list(Screened = c(26.9, 28.4, 23.9, 21.8, 22.4, 25.9, 
26.5, 20, 23.7, 23.7, 22.6, 19.4, 27.3, 25.3, 27.7, 25.3, 28.4, 
24.2, 20.4, 29.6, 27, 23.6, 18.3, 28.1, 20.5, 24.1, 27.2, 26.4, 
24.5, 25.6, 17.9, 23.5, 25.3, 20.2, 26.3, 27.9), Not.Screened = c(24.7, 
19.1, 21, 17.8, 22.8, 24.4, 17.9, 20.5, 20, 26.2, 14.5, 22.4, 
21.1, 24.3, 22, 24.3, 23.9, 19.6, 23.8, 29.2, 19.7, 20.9, 25.2, 
22.5, 23.1, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)), class = "data.frame", row.names = c(NA, -36L))
```

Now I will use the tidyverse to stack it.  This can also be done with `stack(Support.Times)`.

```
stack(Support.Times) %>% drop_na()
```

Using the `tidyverse`, the new data `SSTimes` will stack the data using pivot longer into two variables that I will name `Self.Screen` and `Call.Time` to store the stacked data.  The final command drops the missing data.  Then I will group them and skim them.

```{r}
SSTimes <- Support.Times %>% pivot_longer(., c(Screened,Not.Screened), names_to = "Self.Screen", values_to = "Call.Time") %>% drop_na()
SSTimes %>% group_by(Self.Screen) %>% skim()
```

So I have 25 observations that are not screened and 36 that are screened.  What does it look like?

```{r}
ggplot(SSTimes, aes(x=Self.Screen, y=Call.Time, fill=Self.Screen)) + geom_violin(alpha = 0.2) + scale_fill_discrete(guide=FALSE) + labs(title = "Self Screen and Non-Self Screen Call Times")
```


Here is a picture of the distributions of the two means.

```{r}
gplots::plotmeans(Call.Time~Self.Screen, data=SSTimes, n.label=FALSE, ci.label=TRUE, ylim=c(20,27))
```


What does the t-test look like?

```{r}
t.test(Support.Times$Not.Screened, Support.Times$Screened)
t.test(Call.Time~Self.Screen, data=SSTimes)
```

It is worth noting that R stores a bunch of stuff.  For example, it stores the standard error of the difference and that is worth looking at in this case; the standard error that describes the difference in the averages is `r t.test(Call.Time~Self.Screen, data=SSTimes)$stderr`.

```{r}
Resample.Times <- ResampleProps::ResampleDiffMeans(Support.Times$Screened,Support.Times$Not.Screened)
sd(Resample.Times)
```

