---
title: 'US Census Mapping'
author: RWW
date: '2019-12-09'
slug: uscensus-mapping
categories:
  - R
  - animation
  - tidyverse
tags:
  - tidyTuesday
  - R
  - Maps
header:
  caption: ''
  image: ''
  preview: yes
---


## Searching and Mapping the Census


## Searching for the Asian Population via the Census

To use `tidycensus`, there are limitations imposed by the available tables.  There is ACS -- a survey of about 3 million people -- and the two main decennial census files [SF1] and [SF2].  I will search SF1 for the Asian population.


```{r cars, message=FALSE, warning=FALSE}
library(tidycensus); library(kableExtra)
library(tidyverse); library(stringr)
v10 <- load_variables(2010, "sf1", cache = TRUE)
v10 %>% filter(str_detect(concept, "ASIAN")) %>% filter(str_detect(label, "Female")) %>% kable() %>% scroll_box(width = "100%")
```

There are still 268 to comb through but what seems useful are the bottom rows of the first set of results.

```{r}
library(viridis)
library(sf); library(ggthemes)
# I need supply the names of the variables to fetch from Census: column `name` above
vars10 <- c("P012D031", "P012D032", "P012D033", "P012D034", "P012D035", "P012D036")
# Get the census data with the relevant map by county; 2010 is the most recent
# I used the example from the help file to adapt by dropping the state to get them all and shifting Hawaii and Alaska for visibility.  They are not properly scaled.
MapDat <- get_decennial(geography = "county", variables = vars10, year = 2010,
                    geometry = TRUE, shift_geo = TRUE)
# Map the data with ggplot using geom_sf()
ggplot(MapDat, aes(fill = value, color = value)) + 
  geom_sf() + 
  theme_map() + 
  scale_fill_viridis_c(guide=FALSE)+ 
  scale_color_viridis_c(guide=FALSE) + 
  facet_wrap(~variable)
```

## Totals of the Target Population

```{r pressure, echo=FALSE}
SingleM <- MapDat %>% filter(variable=="P012D031") %>% select(GEOID,NAME,geometry)
MapDatSum <- MapDat %>% group_by(GEOID) %>% summarise(Total = sum(value)) %>% as.data.frame()
MapDatSum <- merge(SingleM,MapDatSum)
PlotlyMe <- ggplot(MapDatSum, aes(fill = Total, text=NAME)) +
     geom_sf(size=0.02, color="white") + theme_map() + scale_fill_viridis_c() +         labs("Asian Females Ages 18 to 34", caption = "Census Table SF1")  
PlotlyMe
```

A plotly

```{r}
library(plotly)
PLM <- ggplotly(PlotlyMe)
library(widgetframe)
frameWidget(PLM)
```

To get rid of some of the messiness because LA is a huge outlier, perhaps it should be binned.

```{r}
MapDatSum <- MapDatSum %>% mutate(Binned.Total = cut_number(Total, 5, ordered_result=TRUE))
PlotlyMe <- ggplot(MapDatSum, aes(fill = Binned.Total, text=NAME)) +
     geom_sf(size=0.02, color="white") + theme_map() + scale_fill_viridis_d() +         labs("Asian Females Ages 18 to 34", caption = "Census Table SF1")  
PlotlyMe
```

# More than 1000 in the Relevant Age Group

```{r}
MapDatSum <- MapDatSum %>% mutate(Total.1000 = as.factor(Total > 1000))
PlotlyMe <- ggplot(MapDatSum, aes(fill = Total.1000, text=NAME)) +
     geom_sf(size=0.02, color="white") + theme_map() + scale_fill_viridis_d() +         labs("Asian Females Ages 18 to 34", caption = "Census Table SF1", fill="More than 1000")  
PlotlyMe
```

# More than 5000 in the Relevant Age Group

```{r}
MapDatSum <- MapDatSum %>% mutate(Total.5000 = as.factor(Total > 5000))
PlotlyMe <- ggplot(MapDatSum, aes(fill = Total.5000)) +
     geom_sf(size=0.02, color="white") + theme_map() + scale_fill_viridis_d() +         labs("Asian Females Ages 18 to 34", caption = "Census Table SF1", fill="More than 5000")  
PlotlyMe
```

# More than 10000 in the Relevant Age Group

```{r}
MapDatSum <- MapDatSum %>% mutate(Total.10K = as.factor(Total > 10000))
PlotlyMe <- ggplot(MapDatSum, aes(fill = Total.10K)) +
     geom_sf(size=0.02, color="white") + theme_map() + scale_fill_viridis_d() +         labs("Asian Females Ages 18 to 34", caption = "Census Table SF1", fill="More than 10000")  
PlotlyMe
```


```{r, eval=FALSE}
# This takes a really long time to run.  It is not evaluated.
library(cartogram)
Carto <- cartogram_cont(
MapDatSum,
"Total",
itermax = 15,
maxSizeError = 1.0001,
prepare = "adjust",
threshold = 0.05
)
```

Load the cartogram already cooked.

```{r}
load(url("https://github.com/robertwwalker/DADMStuff/raw/master/Cartogram.RData"))
ggplot(Carto, aes(fill=Total)) + geom_sf(size=0.01) + theme_map() + labs(caption="A Cartogram")
```
