---
title: New York Times Data on COVID
author: Robert W. Walker
date: '2020-09-21'
slug: new-york-times-data-on-covid
categories:
  - R
tags:
  - plot
  - gganimate
subtitle: ''
summary: ''
authors: []
lastmod: '2020-09-12T20:04:06-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

# New York Times data for the US

The New York Times has a wonderful compilation of United States on the novel coronavirus.  The data update automatically so the following graphics were generated with data retrieved at `r Sys.time()`.


# The Basic State of Things

```{r, message=FALSE, warning=FALSE}
options(scipen=9)
library(tidyverse); library(hrbrthemes); library(patchwork); library(plotly); library(ggdark); library(ggrepel)
CTP <- read.csv("https://covidtracking.com/api/v1/states/daily.csv")
state.data <- read_csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv"))
Rect.NYT <- complete(state.data, state,date)
Rect.NYT <- Rect.NYT %>% group_by(state) %>% mutate(New.Cases = cases - lag(cases, order_by = date), New.Deaths = deaths - lag(deaths, order_by = date)) %>% ungroup()
NYT.Totals <- Rect.NYT %>% group_by(date) %>% summarise(Deaths = sum(deaths, na.rm=TRUE), New.Deaths = sum(New.Deaths, na.rm = TRUE), Cases = sum(cases, na.rm=TRUE), New.Cases = sum(New.Cases, na.rm = TRUE)) %>% ungroup()
library(patchwork)
plot1 <- NYT.Totals %>% ggplot(., aes(x=date, y=Deaths)) + geom_line() + labs(title="Deaths") + dark_mode()
plot2 <- NYT.Totals %>% ggplot(., aes(x=date, y=New.Deaths)) + geom_line() + labs(title="New Deaths") + geom_smooth(fill="white") + dark_mode()
plot3 <- NYT.Totals %>% ggplot(., aes(x=date, y=Cases)) + geom_line() + labs(title="Cases") + dark_mode()
plot4 <- NYT.Totals %>% ggplot(., aes(x=date, y=New.Cases)) + geom_line() + labs(title="New Cases") + geom_smooth(fill="white") + dark_mode()
(plot1 + plot2) / (plot3 + plot4)
```

## Where's the Current Problem?

```{r}
NYTD1 <- Rect.NYT %>% group_by(state) %>% mutate(Cases.7DD = (cases - lag(cases, 7, order_by = date))/ lag(cases, 7, order_by = date), Deaths.7DD = (deaths - lag(deaths, 7, order_by = date))/ lag(deaths, 7, order_by = date))
NYTD1 %>% filter(date > Sys.Date()-8) %>% mutate(Avg.7DD = mean(Cases.7DD, na.rm=TRUE)) %>% top_n(25, Avg.7DD) %>% ggplot(., aes(x=forcats::fct_reorder(state, Avg.7DD), y=Avg.7DD, fill=state)) + geom_col() + coord_flip() + guides(fill=FALSE) + labs(x="", y="Avg. 7 Day Change over the last week", title="Average 7 Day Percent Change in New COVID-19 Cases \nAveraged over the last week")
```


## The Initial vs. The Subsequent

The problem was initially concentrated in New York, New Jersey, Massachusetts, California, and Illinois.  How do things look if we remove those states?

```{r, message=FALSE, warning=FALSE}
NYT.Totals2 <- Rect.NYT  %>% filter(!(state %in% c("California","Massachusetts","New York","New Jersey","Illinois"))) %>% group_by(date) %>% summarise(Deaths = sum(deaths, na.rm=TRUE), New.Deaths = sum(New.Deaths, na.rm = TRUE), Cases = sum(cases, na.rm=TRUE), New.Cases = sum(New.Cases, na.rm = TRUE)) %>% ungroup()
plot1a <- NYT.Totals2  %>% ggplot(., aes(x=date, y=Deaths)) + geom_line() + labs(title="Deaths", subtitle="Excluding CA, NY, NJ, IL, MA") + dark_mode()
plot2a <- NYT.Totals2  %>% ggplot(., aes(x=date, y=New.Deaths)) + geom_line() + labs(title="New Deaths", subtitle="Excluding CA, NY, NJ, IL, MA") + geom_smooth(fill="white") + dark_mode()
plot3a <- NYT.Totals2  %>%  ggplot(., aes(x=date, y=Cases)) + geom_line() + labs(title="Cases", subtitle="Excluding CA, NY, NJ, IL, MA") + dark_mode()
plot4a <- NYT.Totals2  %>% ggplot(., aes(x=date, y=New.Cases)) + geom_line() + labs(title="New Cases", subtitle="Excluding CA, NY, NJ, IL, MA") + geom_smooth(fill="white") + dark_mode()
(plot1a + plot2a) / (plot3a + plot4a)
```


```{r}
plot1 <- NYT.Totals %>% ggplot(., aes(x=date, y=Deaths)) + geom_line() + labs(title="Deaths") + scale_y_log10() + dark_mode()
plot2 <- NYT.Totals %>% ggplot(., aes(x=date, y=New.Deaths)) + geom_line() + labs(title="New Deaths") + geom_smooth(fill="white") + dark_mode()
plot3 <- NYT.Totals %>% ggplot(., aes(x=date, y=Cases)) + geom_line() + labs(title="Cases") + scale_y_log10() + dark_mode()
plot4 <- NYT.Totals %>% ggplot(., aes(x=date, y=New.Cases)) + geom_line() + labs(title="New Cases") + geom_smooth(fill="white") + dark_mode()
(plot1 + plot2) / (plot3 + plot4)
```


# The `@jburnmurdoch` graphics for US States

## Deaths

```{r, message=FALSE, warning=FALSE}
R2.NYT <- Rect.NYT %>% 
  mutate(SelMe = (deaths > 9)) %>% 
  filter(SelMe==TRUE) %>% 
  group_by(state) %>%
  mutate(Counter = row_number()) %>%
  ungroup()
OR.R2 <- R2.NYT %>% filter(fips=="41")
OR.R2A <- R2.NYT %>% filter(fips=="41" & Counter == max(OR.R2$Counter))
PlotA <- R2.NYT %>% 
  ggplot(., aes(x=Counter, y=deaths, color=state)) + 
  geom_line(alpha=0.3) + guides(color=FALSE) + 
  scale_y_log10() + 
  geom_line(data=OR.R2, color="white") + 
  geom_text(data=OR.R2A, aes(x=Counter, y=deaths, label=state), color="white", inherit.aes = FALSE) + 
  labs(x="Days since 10th Death", y="log(Cumulative Deaths)", title="Log-Deaths [Cumulative] given Days Since 10th Death", caption = "data from nytimes/covid-19 on github \n design mimics @jburnmurdoch") + 
  dark_theme_linedraw()
PlotA
```

## Cases

```{r}
R2.NYT <- Rect.NYT %>% 
  mutate(SelMe = (deaths > 9)) %>% 
  filter(SelMe==TRUE) %>% 
  group_by(state) %>%
  mutate(Counter = row_number()) %>%
  ungroup()
OR.R2 <- R2.NYT %>% filter(fips=="41")
OR.R2A <- R2.NYT %>% filter(fips=="41" & Counter == max(OR.R2$Counter))
Plot1 <- R2.NYT %>% ggplot(., aes(x=Counter, y=cases, color=state)) + 
  geom_line(alpha=0.3) + guides(color=FALSE) + geom_line(data=OR.R2, color="white") + 
  geom_text(data=OR.R2A, aes(x=Counter, y=cases, label=state), color="white", inherit.aes = FALSE) +   scale_y_log10() +
  labs(x="Days since 10th Death", y="log(Cumulative Cases)", title="Log-Cases [Cumulative] given Days Since 10th Death", caption = "data from nytimes/covid-19 on github \n design mimics @jburnmurdoch") + 
  dark_theme_linedraw()
Plot1
```

# A Different Definition: Days since 100th Case

```{r}
options(scipen=8)
R2.NYT <- Rect.NYT %>% 
  mutate(SelMe = (cases > 99)) %>% 
  filter(SelMe==TRUE) %>% 
  group_by(state) %>%
  mutate(Counter = row_number()) %>%
  ungroup()
OR.R2 <- R2.NYT %>% filter(fips=="41")
OR.R2A <- R2.NYT %>% filter(fips=="41") %>% filter(date == max(date))
Plot1 <- R2.NYT %>% ggplot(., aes(x=Counter, y=cases, color=state)) + 
  geom_line(alpha=0.3) + 
  guides(color=FALSE) + 
  scale_y_log10() + 
  geom_line(data=OR.R2, color="white") + 
  geom_text(data=OR.R2A, aes(x=Counter, y=deaths, label=state), color="white", inherit.aes = FALSE) + 
  dark_theme_linedraw() + 
  labs(subtitle="Note logarithm", x="Days Since 100th Case", y="Log(Cumulative Cases)")
Plot2 <- R2.NYT %>% 
  ggplot(., aes(x=Counter, y=cases, color=state)) + 
  geom_line(alpha=0.3) + 
  guides(color=FALSE) + 
#  scale_y_log10() +
  geom_line(data=OR.R2, color="white") + 
  geom_text(data=OR.R2A, aes(x=Counter, y=cases, label=state), color="white", inherit.aes = FALSE) + 
  dark_theme_linedraw() +
  labs(x="Days since 100th Case", y="Cumulative Cases")
Plot1 + Plot2
```



## New Cases by State over Time

Let me first track the incidence of new cases by state.  There is no particularly good way to visualize this because New York is wildly different.

```{r, warning=FALSE, message=FALSE}
WCStates <- Rect.NYT %>% filter(date==max(date)) %>% top_n(5, wt=New.Cases) %>% mutate(Top5 = 1)
Rect.NYT %>% ggplot(., aes(x=date, y=New.Cases, color=state)) + 
  geom_line(alpha=0.25) + 
  geom_label_repel(data=WCStates, aes(label=state), inherit.aes = TRUE) +
  guides(color=FALSE) + 
  scale_y_log10() + 
  labs(title="New Cases by State", y="log(New Cases)", subtitle="Note the logarithmic scale.", caption="Data from nytimes/covid-19-data on guthub.") + 
  dark_theme_linedraw()
```

## Aggregate Data over the United States

```{r}
library(patchwork)
ggplot(NYT.Totals, aes(x=date, y=New.Cases)) + geom_line() + labs(x="Date", y="New COVID-19 Cases", title="Daily: New COVID-19 Cases") + dark_theme_linedraw() + theme(axis.text.x = element_text(size=8, angle=45))+ ggplot(NYT.Totals, aes(x=date, y=New.Deaths)) + geom_line() + labs(x="Date", y="New COVID-19 Deaths", title="Daily: New COVID-19 Deaths", subtitle="Note the logarithmic scale.", caption="Data from nytimes/covid-19-data on guthub.") + dark_theme_linedraw() + theme(axis.text.x = element_text(size=8, angle=45))
```

## Totals

```{r}
# A patchwork
ggplot(NYT.Totals, aes(x=date, y=Cases)) + geom_line() + labs(x="Date", y="Total COVID-19 Cases", title="US COVID-19 Cases", subtitle="Note the logarithmic scale.") + theme_modern_rc() + theme(axis.text.x = element_text(size=8, angle=45)) + scale_y_log10() +
ggplot(NYT.Totals, aes(x=date, y=Deaths)) + geom_line() + labs(x="Date", y="Total COVID-19 Deaths", title="US COVID-19 Deaths", subtitle="Note the logarithmic scale.", caption="Data from nytimes/covid-19-data on guthub.") + theme_modern_rc() + theme(axis.text.x = element_text(size=8, angle=45)) + scale_y_log10()
```

## US Death Rate

Given the data, what does the US Case Fatality Rate look like at this point?  Two caveats for this.  The first, uncertainty in the numerator.  The number of deaths is surely undercounted, probably dramatically based on anecdotes from non-medical first responders.  Second, we know the numerator is also undercounted.  Assuming asymptomatic cases, the rules prohibited testing them for a substantial period of time on top of the existing scarcity of tests. 

```{r, message=FALSE, warning=FALSE}
CFR <- NYT.Totals %>% 
  mutate(CFR = round(Deaths / Cases, digits=3)) %>% mutate(CFR.D = (CFR > 0.02)) %>%
ggplot(., aes(x=date, y=CFR)) + 
  geom_line() + 
  geom_point(aes(color=CFR.D)) + 
  labs(title = "Case Fatality Rate of COVID-19 in the US", subtitle="Very uncertain estimate... Numerator and denominator uncertain \n Data: NY Times GitHub", caption="Data from nytimes/covid-19-data on guthub.", color="Greater \n than 0.02") + 
  dark_theme_bw()
GPCFR <- ggplotly(CFR)
library(widgetframe)
frameWidget(GPCFR)
```

## This may prove useful

```{r, message=FALSE, warning=FALSE}
NCFR <- NYT.Totals %>% 
  mutate(CFR = round(New.Cases / New.Deaths, digits=3))
P1 <- NCFR %>% ggplot(., aes(x=date, y=CFR)) + 
  geom_line() + 
  labs(y="New Cases per New Death", title = "New Cases to New Deaths", subtitle="Very uncertain estimate... Numerator and denominator uncertain \n Data: NY Times GitHub", caption="Data from nytimes/covid-19-data on github.") + 
  dark_theme_bw()
GPNCFR <- ggplotly(P1)
library(widgetframe)
frameWidget(GPNCFR)
```


# 50 States?

```{r, message=FALSE, warning=FALSE}
library(fiftystater); library(maptools); library(ggthemes); library(ggmap)
CFR2 <- Rect.NYT %>% filter(date == "2020-05-22") %>% mutate(CFR = round(deaths / cases, digits=3), State = state, state = tolower(State))
CFR2 %>% filter(!(state %in% c("puerto rico","northern mariana islands", "virgin islands", "guam"))) %>% ggplot(., aes(fill=CFR, map_id=state)) + 
  geom_map(map = fifty_states) + 
    expand_limits(x = fifty_states$long, y = fifty_states$lat) +
    coord_map() + scale_fill_continuous_tableau(palette="Classic Red", guide="colourbar") + theme_map() + labs(title="US Case Fatality Rate by State: May 22")
#  geom_point(aes(color=CFR.D)) + 
#  labs(title = "Case Fatality Rate of COVID-19 in the US", subtitle="Very uncertain estimate... Numerator and denominator uncertain \n Data: NY Times GitHub", caption="Data from nytimes/covid-19-data on guthub.", color="Greater \n than 0.02") + 
#  dark_theme_bw()
```

