---
title: "telco"
author: "Robert W. Walker"
date: "2020-02-19"
output:
   html_document:
     self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# telco Churn

The loss of customers is known as churn.  Here is some data on telephone companies that gives us a number of features of the customer and the billing history relevant to this.

```{r, message=FALSE, warning=FALSE}
library(radiant)
library(tidyverse)
library(readr)
library(skimr)
telco <- read_csv("https://github.com/robertwwalker/DADMStuff/raw/master/WA_Fn-UseC_-Telco-Customer-Churn.csv")
skim(telco)
telco <- telco[complete.cases(telco),] # Keep only rows with complete cases
telco.analyse <- subset(telco, select = -customerID) # Drop customer ID
telco.F <- mutate_if(telco.analyse, is.character, as.factor)
```


```
install.packages("DataExplorer")
library(DataExplorer)
# Run separately
create_report(telco.F)
```

Remove the missing data.  The outcome of interest is Churn.  Let's look at it and take on a few examples from proportions.  Because it is Yes and No, everything will be about the probability of No unless we turn them to factors and order them backwards.  I will just describe this as the probability of *retention*.

```{r}
( Tab.PaperlessY <- xtabs(~PaperlessBilling+Churn, data=telco.analyse, subset=telco.analyse$PaperlessBilling=="Yes") )
prop.table(Tab.PaperlessY, 1)
prop.test(Tab.PaperlessY)
```

For the paperless customers, the probability of retention is 0.65 to 0.68 with 95% confidence.  For the paper customers, we have...

```{r}
( Tab.PaperlessN <- xtabs(~PaperlessBilling+Churn, data=telco.analyse, subset=telco.analyse$PaperlessBilling=="No") )
prop.table(Tab.PaperlessN, 1)
prop.test(Tab.PaperlessN)
```

The probability of retention ranges from 0.82 to 0.85 with 95% confidence.  Because they do not overlap, there must be a difference and paperless customers churn more.

## Comparisons

```{r}
( Tab.Paperless <- xtabs(~PaperlessBilling+Churn, data=telco.analyse) )
prop.table(Tab.Paperless, 1)
prop.test(Tab.Paperless)
```

Paperless clients have a probability of churning that is 0.152 to 0.192 higher than non-paperless clients.

## Phone Service?

Is there a difference in Churn between those with and without phone service?

```{r}
( Tab.PS <- xtabs(~PhoneService+Churn, data=telco.analyse) )
prop.table(Tab.PS, 1)
prop.test(Tab.PS)
```

It seems not.  Those without phone service could be 0.017 less likely or 0.053 more likely to be retained; no difference is likely.  Now, let's turn to regression models.  The character variable will cause problems in this case so we will have to analyse it.

```{r}
library(rpart)
split.me <- function(data, prop1=0.7) {
  train <- data[sample(1:nrow(data), size=prop1*nrow(data)),]
  test <- anti_join(data,train)
  return(list(train=train,test=test))
}
split.data <- split.me(telco.analyse, prop1=0.666)
train <- split.data$train
test <- split.data$test
Tree1 <- rpart(as.factor(Churn)~., data = telco.F)
library(partykit)
plot(as.party(Tree1))
```

## A sankey

```{r}
library(sankeytreeR); library(pipeR)
sankeytree(Tree1, tooltip="all")
```


# How does it perform?

A predict function...  Every model has one.

```{r}
# What does predict do?
head(predict(Tree1))
# Predict the Test set using the Training model
test$pred1 <- predict(Tree1, test, "class")
table(test$Churn,test$pred1)
# Conditional Probabilities
prop.table(table(test$Churn,test$pred1), 1)
# The Overall Comparison
prop.table(table(telco.F$Churn))
prop.table(table(test$Churn,test$pred1))
```


# A GLM Regression

```{r}
result <- logistic(
  telco.F, 
  rvar = "Churn", 
  evar = c("tenure", "Contract"), 
  lev = "Yes"
)
summary(result, sum_check = c("vif", "confint", "odds"))
plot(result, plots = "fit", custom = FALSE)
```

Predict a few rows in the original data.

```{r}
head(predict(result, telco.F))
```

