---
title: COVID-19 Scraping
author: Robert W. Walker
date: '2020-03-24'
slug: covid-scraping
categories:
  - tidyverse
  - web scraping
tags:
  - tidyverse
  - R
subtitle: ''
summary: ''
authors: []
lastmod: '2020-03-24T22:46:49-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
library(tidyverse)
```
*NB: This was last updated on March 25, 2020.*

# Building Oregon COVID data

I have a few days of data now.  To rebuild it, I will have to use the [waybackmachine](https://archive.org/web/). The files that I need to locate and follow updates to [this page from Oregon's OHA](https://govstatus.egov.com/OR-OHA-COVID-19).

# A Scraper

Let me explain the logic for the scraper.  *NB: I had to rewrite it; the original versions of the website had three tables without data on hospitalizations.  The state of Oregon is now providing hospitalization data.  They have also changed the reporting of age groups.*  

First, I use `read_html` to read the version of the page. 
Second, parse the individual tables using `html_nodes`, 
Third, render the table using `html_table` and 
Fourth, turn it into a `data.frame`.  

Fifth, There are two other bits of housekeeping.  In a few cases, there are commas formatted into numbers and I also grab the reported date from within the scrape.  

I put these parts into a series of functions.

```{r}
library(rvest); library(htmltools)
# A function to remove commas from numbers.
comma.rm.to.numeric <- function(variable) {
  as.numeric(str_remove_all( {{variable}}, ",")) 
  }
# A function to parse the tables currently
OHA.Corona <- function(website, date) {
webpage <- read_html(website) # 1
COVID.Head <- webpage %>%
        html_nodes("table") %>% # 2
        .[1] %>%  # Grab the first table
        html_table(fill = TRUE) %>%  # 3
        data.frame()  # 4 
# Acquire the scraped date from the heading on the page.  The rest is 5
Scraped.date <- names(COVID.Head)[1] %>% str_remove(.,"X.Oregon.Test.Results.as.of.") %>% str_remove(., "..8.00.a.m..Updated.daily.")
names(COVID.Head) <- c("Category","Outcome") # Change the names
COVID.Head <- COVID.Head %>% 
  mutate(Outcome = comma.rm.to.numeric(Outcome), date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y")) # Create a few variables including the date for checking
# Extract the county data
COVID.County <- webpage %>%
        html_nodes("table") %>% # 2
        .[2] %>%
        html_table(fill = TRUE) %>% # 3 
        data.frame() %>%  # 4
        mutate(date=as.Date(date), # 5
               Scraped.date = as.Date(Scraped.date,"%m.%d.%y"), 
               Negative.test.results = comma.rm.to.numeric(Negative.test.results))
# Extract the age data
COVID.Age <- webpage %>%
        html_nodes("table") %>% #2
        .[3] %>%
        html_table(fill = TRUE) %>% # 3 
        data.frame()  %>%   # 4
        mutate(date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y")) # 5
# Extract the hospitalization data
COVID.Hospitalized <- webpage %>%
        html_nodes("table") %>% # 2
        .[4] %>%
        html_table(fill = TRUE) %>% # 3
        data.frame()  %>%  # 4
        mutate(date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y")) # 5
return(list(Header=COVID.Head, Counties = COVID.County, Ages = COVID.Age, Hospitalized = COVID.Hospitalized))
}
# A function to extract the previous website organization with only three tables.
OHA.Corona.3 <- function(website, date) {
webpage <- read_html(website)
# Extract the header data
COVID.Head <- webpage %>%
        html_nodes("table") %>%
        .[1] %>%
        html_table(fill = TRUE) %>% 
        data.frame()
# Extract the reported date from the website
Scraped.date <- names(COVID.Head)[1] %>% str_remove(.,"X.Oregon.Test.Results.as.of.") %>% str_remove(., "..8.00.a.m..Updated.daily.")
# Change the column names
names(COVID.Head) <- c("Category","Outcome")
# Complete the header data
COVID.Head <- COVID.Head %>% mutate(Outcome = as.numeric(str_remove(Outcome,",")), date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y"))
# Extract the county data
COVID.County <- webpage %>%
        html_nodes("table") %>%
        .[2] %>%
        html_table(fill = TRUE) %>% data.frame() %>% mutate(date=as.Date(date), 
                                                            Scraped.date = as.Date(Scraped.date,"%m.%d.%y"),
                                                            Negative.test.results = comma.rm.to.numeric(Negative.test.results))
# Extract the age data
COVID.Age <- webpage %>%
        html_nodes("table") %>%
        .[3] %>%
        html_table(fill = TRUE) %>% data.frame()  %>% filter(!startsWith(.[[1]],"Total")) %>% mutate(date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y"))
return(list(Header=COVID.Head, Counties = COVID.County, Ages = COVID.Age))
}
OHA.Corona.2 <- function(website, date) {
webpage <- read_html(website)
# Extract the header data
COVID.Head <- webpage %>%
        html_nodes("table") %>%
        .[1] %>%
        html_table(fill = TRUE) %>% 
        data.frame()
# Extract the reported date from the website
Scraped.date <- names(COVID.Head)[1] %>% str_remove(.,"X.Oregon.Test.Results.as.of.") %>% str_remove(., "..8.00.a.m..Updated.daily.")
# Change the column names
names(COVID.Head) <- c("Category","Outcome")
# Complete the header data
COVID.Head <- COVID.Head %>% mutate(Outcome = as.numeric(str_remove(Outcome,",")), date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y"))
# Extract the county data
COVID.County <- webpage %>%
        html_nodes("table") %>%
        .[2] %>%
        html_table(fill = TRUE) %>% data.frame() %>% mutate(date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y"))
# Extract the age data
COVID.Age <- webpage %>%
        html_nodes("table") %>%
        .[3] %>%
        html_table(fill = TRUE) %>% data.frame()  %>% filter(!startsWith(.[[1]],"Total")) %>% mutate(date=as.Date(date), Scraped.date = as.Date(Scraped.date,"%m.%d.%y"))
return(list(Header=COVID.Head, Counties = COVID.County, Ages = COVID.Age))
}
```

Now I invoke the function for each date of valid data.  Which function depends on the data provided as this has changed over time.  You can look at each one via a web browser.

```{r, eval=FALSE}
# March 18 Update
March18 <- OHA.Corona.2(website="https://web.archive.org/web/20200319144434/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-18")
# March 19 Update
March19 <- OHA.Corona.2(website="https://web.archive.org/web/20200320152224/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-19")
# March 20 Update
March20 <- OHA.Corona.2(website="https://web.archive.org/web/20200320202955/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-20")
# March 21 Update
March21 <- OHA.Corona.3(website="https://web.archive.org/web/20200321211741/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-21")
# March 22 Update
March22 <- OHA.Corona.3("https://web.archive.org/web/20200322205228/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-22")
# March 23 Update
March23 <- OHA.Corona(website="https://web.archive.org/web/20200323192410/https://govstatus.egov.com/OR-OHA-COVID-19", date="2020-03-23")
# March 24 Update
March24 <- OHA.Corona(website="https://govstatus.egov.com/OR-OHA-COVID-19", date=as.character(Sys.Date()-1))
```

## Creating the data frames

I need to combine the various tables together by type and take out the totals row in some cases.  This represents the last time that I did it manually.

```{r, eval=FALSE}
# Create test data
Oregon.Tests.All <- bind_rows(March24$Header,March23$Header,March22$Header,March21$Header,March20$Header,March19$Header,March18$Header)
# Drop the row of totals
Oregon.Tests <- Oregon.Tests.All[!str_detect(Oregon.Tests.All$Category, "Total"),]
# Create a summary table
OR.Testing <- Oregon.Tests %>% group_by(date) %>% summarise(Total = sum(Outcome))
# Create county data
Oregon.COVID.All <- bind_rows(March24$Counties,March23$Counties,March22$Counties,March21$Counties,March20$Counties,March19$Counties,March18$Counties)
# Split the county data into one that is exclusively totals and one without the totals
Oregon.COVID.Total <- Oregon.COVID.All %>% filter(County=="Total")
Oregon.COVID <- Oregon.COVID.All %>% filter(County!="Total")
# Create the data by age
OR.Ages <- bind_rows(March24$Ages,March23$Ages,March22$Ages,March21$Ages,March20$Ages,March19$Ages,March18$Ages)  %>% filter(Age.group!="Total")
# Create a summary table by age
OR.AgeT <- OR.Ages %>%  group_by(date) %>% summarise(Total=sum(Number.of.cases))
# Create the hospitalization data
OR.Hosp <- bind_rows(March23$Hospitalized,March24$Hospitalized)
# Save the image
save.image("~/Sandbox/awful/content/R/COVID/data/OregonCOVID2020-03-24.RData")
```

# Automating updates

From here, I did not want to actually have to DO this again; it needed to be automated.  That takes two parts and one of them is not detailed here.  That involves a CRON job; a timer on the computer that executes particular code at chosen intervals.  In this case, I execute the following script hourly because the next option is daily and the time changes.  If I wished to do this in full stack, I would combine the visuals that use this data with the scraper/updater and then gmail the resulting markdown.  For the web, this has to be handled differently without an internal web server for this.

The process works like this.
1. Load the previous day's data.
2, Grab the most recent OHA update.
3. Use an if-else to update the data if there is anything to update; or not.
4. Verify that there is new data by comparing the date on the website to the system's date.
5. Append today's data to what previously existed and remove duplicates.
6. Drop totals where necessary. [or create them]

```{r, message=FALSE, warning=FALSE}
library(rvest); library(htmltools); library(tidyverse); library(rlang)
load(url(paste0("https://rww.science/r/covid/data/OregonCOVID",Sys.Date()-1,".RData"))) # 1
Today <- OHA.Corona(website="https://govstatus.egov.com/OR-OHA-COVID-19", date=as.character(Sys.Date())) # 2
if(Today$Header$date[[1]]==as.Date(Today$Header$Scraped.date[[1]],"%m.%d.%y")) { # 3
# Store Today
eval(parse_expr(paste(months(Sys.Date()),format(Sys.Date(), "%d")," <- Today", sep=""))) # 4
# Create test data
Oregon.Tests.All <- bind_rows(Today$Header,Oregon.Tests.All) %>% distinct(.) # 5
# Drop the row of totals
Oregon.Tests <- Oregon.Tests.All[!str_detect(Oregon.Tests.All$Category, "Total"),]  # 6
# Create a summary table
OR.Testing <- Oregon.Tests %>% group_by(date) %>% summarise(Total = sum(Outcome)) # 6
# Create county data
Oregon.COVID.All <- bind_rows(Today$Counties,Oregon.COVID.All) %>% distinct(.) # 5
# Split the county data into one that is exclusively totals and one without the totals
Oregon.COVID.Total <- Oregon.COVID.All %>% filter(County=="Total") # 6
Oregon.COVID <- Oregon.COVID.All %>% filter(County!="Total")  # 6
# Create the data by age
OR.Ages <- bind_rows(Today$Ages,OR.Ages)  %>% filter(Age.group!="Total") %>% distinct(.) # 5
# Create a summary table by age
OR.AgeT <- OR.Ages %>% group_by(date) %>% summarise(Total=sum(Number.of.cases)) # 6
# Create the hospitalization data
OR.Hosp <- bind_rows(Today$Hospitalized,OR.Hosp) %>% distinct(.) # 5
# Save the imageformat(Sys.Date(), "%d")
save.image(paste0("~/Sandbox/awful/content/R/COVID/data/OregonCOVID",Sys.Date(),".RData")) # Save the data with a date flag in the name.
cat("Added new data...") # Report the updates
} else {
cat("Nothing new to add; have a nice day!") # Report no updates.
}
OR.Testing # Show a little bit of data.
```

