---
title: Spending on Kids
author: Robert W. Walker
date: '2020-09-15'
slug: spending-on-kids
categories:
  - R
  - tidyTuesday
tags:
  - tidyTuesday
  - tidyverse
subtitle: ''
summary: ''
authors: []
lastmod: '2020-09-15T17:22:16-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Spending on Kids

First, let me import the data.

```{r}
kids <- read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-15/kids.csv')
# kids <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-15/kids.csv')
```

Now let me summarise it and show a table of the variables.

```{r}
summary(kids)
```

A table of the variables.  [The definitions are best found here.](https://jrosen48.github.io/tidykids/articles/tidykids-codebook.html)

```{r}
table(kids$variable)
```

It is *very* tidy.  It is probably better shown after a pivot.  50 states, the District of Columbia, and 20 years gives us 1,020 observations.  Let me show it wide. 

```{r}
Big.Wide <- pivot_wider(kids, id_cols = c(state,year), names_from = "variable", values_from = c("raw","inf_adj","inf_adj_perchild"))
Big.Wide
```


# My brief plan

I recently came across a `geofacet` for R.  I want to use it to plot a little bit of this data.  If you want to get a head start, try `install.packages("geofacet", dependencies=TRUE)`.  You can google `geofacet` to get an idea of what a `geofacet` plot is.  I will build one on the fly using a couple of tidy tools: filter, mutate, and joins and then put it together.

```{r}
library(viridis)
library(geofacet)
state_ranks %>% filter(variable=="education") %>% select(state,name) -> mergeMe
p1 <- kids %>% 
  left_join(., mergeMe, by = c('state' = 'name')) %>% 
  filter(variable=="PK12ed")%>% 
  ggplot(., aes(x=year, y=inf_adj_perchild, color=inf_adj_perchild)) + 
  geom_line() + 
  facet_geo(~state.y) + 
  labs(x="year", y="Inflation Adjust Expenditures per child", title="Pre-K Through 12 Education Spending", color="Spend per child", caption="Data from #tidyTuesday: @PieRatio") + 
  scale_color_viridis_c() + theme_void()
p1
```


## Neat-o an Oregon Grid

This isn't very good though....

```{r}
load(url("https://github.com/robertwwalker/rww-science/raw/master/content/R/COVID/data/OregonCOVID2020-09-15.RData"))
OR.County.COVID %>% 
  mutate(County = str_replace(County, " ", "")) %>% 
  ggplot(., aes(x=date, y=Number.of.cases, color=Number.of.cases)) + 
  geom_line(size=1.5) + 
  facet_geo(~ County, grid = "us_or_counties_grid1", label = "name", scales = "free_y") +
  scale_color_viridis_c(option = "plasma") +
  theme_void()
```

