---
title: Visualizing One Qualitative and One Quantitative Variable
author: Robert W. Walker
date: '2020-09-14'
slug: visualize-mixed-data
categories:
  - R
tags:
  - plot
subtitle: ''
summary: ''
authors: []
lastmod: '2020-09-13T20:04:06-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=TRUE)
library(tidyverse)
```

# Bonds

A dataset for illustrating the various available visualizations needs a certain degree of richness with manageable size.  The dataset on *Bonds* contains three categorical and a few quantitative indicators sufficient to show what we might wish.

## Loading the Data

```{r}
Bonds <- read.csv(url("https://raw.githubusercontent.com/robertwwalker/DADMStuff/master/BondFunds.csv"))
```

## A Summary

```{r}
library(skimr)
Bonds %>% 
  skim()
```

Most data types are represented.  There is no time variable so dates and the visualizations that go with time series are omitted.

# Data Visualization

There are three primary visualizations that we might use for the combination of one qualitative and one quantitative indicator.  I will deploy boxplots, violin plots, overlaid densities, and dotplots.


## `geom_boxplot()`

This will construct a boxplot of quantitative y for each value of the qualitative variable placed on x.  This is very hard to read because of the extrema.

```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets)) + 
  geom_boxplot()
```

## `geom_dotplot()`

The number of bins, the axis they are placed on, and the size of the dots are core to dotplots.  It is often simply a matter of trial and error.

```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets, color=Risk)) + 
  geom_dotplot(binaxis="y", bins=50, dotsize=0.3)
```

### Improved

```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets, color=Risk)) + 
  geom_dotplot(binaxis="y", bins=50, dotsize=0.3) + guides(color=FALSE) + theme_minimal()
```


## `geom_violin()`

The most basic violin plot shows a two-sided density plot for each value of x.  By default, all violins have the same area.

```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets)) + 
  geom_violin()
```
### Adjusting the area: `scale=count`

We can adjust the violins to have area proportional to the count of observations by deploying the scale argument set equal to count.

```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets)) + 
  geom_violin(scale="count")
```

### Adjusting the area: `scale=width`

We can also adjust the violins to have equal width.

```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets)) + 
  geom_violin(scale="width")
```

### Adjusting the bandwidth

We can also make the violins smoother or more rigid with the `adjust=` argument.  Numbers greater than one make it smoother.

```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets)) + 
  geom_violin(scale="count", adjust=2)
```

Numbers less than one make it less smooth.


```{r}
Bonds %>% 
  ggplot(., aes(x=Risk, y=Assets)) + 
  geom_violin(scale="count", adjust=1/2)
```


## `geom_density()` with color/fill

We can color the lines of a density plot to try and showcase the various distributions.

```{r}
Bonds %>% 
  ggplot(., aes(x=Assets, color=Risk)) + 
  geom_density()
```
We fill the shape of density plot to try and showcase the various distributions.

```{r}
Bonds %>% 
  ggplot(., aes(x=Assets, fill=Risk)) + 
  geom_density()
```

This almost always needs lightening.

```{r}
Bonds %>% 
  ggplot(., aes(x=Assets, fill=Risk)) + 
  geom_density(alpha=0.2)
```

In this case, it helps to remove the outline.

```{r}
Bonds %>% 
    ggplot(., aes(x=Assets, fill=Risk)) + 
    geom_density(alpha=0.2, color=NA)
```



## `geom_beeswarm()`

Related to the dotplot is the beeswarm.  It requires installing a package with the geometry known as ggbeeswarm.

```
install.packages("ggbeeswarm")
```

```{r}
library(ggbeeswarm)
Bonds %>% ggplot() + aes(x=Risk, y=Assets) + geom_beeswarm()
```

```{r}
library(ggbeeswarm)
Bonds %>% ggplot() + aes(x=Risk, y=Assets, color=Risk) + geom_beeswarm() + guides(color=FALSE)
```
