---
title: 'Alluvial Plots'
author: 'Robert W. Walker'
date: '2019-10-09'
header:
  caption: ''
  image: ''
  preview: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## Alluvial and Sankey Diagrams

The aforementioned plots are methods for visualising the flow of data through a stream of markers.  I was motivated to show this because enough of you deal in orders, tickets, and the like the flow visualisation of a system might prove of use.  I will work with a familiar dataset.  These are data on Admissions at the University of California Berkeley.  The data exist as an internal R file in tabular form.

```{r, message=FALSE}
library(tidyverse)
library(ggalluvial) # if this is not installed, install.packages("ggalluvial")
data("UCBAdmissions") # This dataset is built in as a set of tables.
UCBAdmissions  # What does it look like?
UCBADF <- data.frame(UCBAdmissions)  # Force it into a data.frame
UCBADF  # This is what the data structure needs to look like.
```

## An Alluvial

This is the tidy version that we worked with at the individual level.  To make this code work, change the below locations to import the same data.

```{r DL}
load(url("https://github.com/robertwwalker/academic-mymod/raw/master/data/UCBtidy.RData"))
head(DiscriminationUCB)
```

To put this data in a table, using the `%>%` pipe operator, we will pass the tidy data, group it by the elements of the alluvial, and then generate the counts.

```{r}
DUCBT <- DiscriminationUCB %>% group_by(M.F,Dept,Admit) %>% summarise(count = n()) %>% ungroup()
DUCBT
```


## `ggalluvial()`

The alluvial requires an additional package `ggalluvial`.  We can install it through 

```
install.packages("ggalluvial")
```

What can it do?  It needs data.  The y axis is always the total counts in the cells.  Then we set axes with a number after to show the phases from left to right.  So here, axis1 will be gender and axis two will be Department.  Admitted and non-admitted students `flowed` with colors depicting them move through the system.  We want to track them by their admitted status.  The alluvial itself has y as Frequency and the various axis* as the phases to track.  The outcome of interest enters the fill so that color shows the outcome of interest flowing through the strata.

## With the system data

This is the vignette solution to these data with the package.  Extending it to any data is a two step process.

```{r}
UCBADF %>% ggplot(.,
       aes(y = Freq, axis1 = Gender, axis2 = Dept)) +
  geom_alluvium(aes(fill = Admit), width = 1/12) +
  geom_stratum(width = 1/12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", label.strata = TRUE) +
  scale_x_discrete(limits = c("Gender", "Dept"), expand = c(.05, .05)) + # Fix the x axis
  scale_fill_brewer(type = "qual", palette = "Set1") + # Give it nice colors
  ggtitle("UC Berkeley admissions and rejections, by sex and department") # give it a title
```

# A simple one [or as simple as I can]

A lot of the code is just prettying.  The most basic plot needs this:

```{r}
ggplot(UCBADF,  # plot the data
       aes(y = Freq, axis1 = Gender, axis2 = Dept)) + # what are the named axes
  geom_alluvium(aes(fill = Admit), width = 1/12) + # what variable will fill the paths; Admission here.
  geom_stratum(width = 1/12, fill = "black", color = "grey") + # This set the strata that our people will move through The one 12 is 12 combinations; the two colors here dfine the background and text for the labels.
  geom_label(stat = "stratum", label.strata = TRUE)  # This labels them.
```

Same with our data.

```{r}
ggplot(DUCBT,
       aes(y = count, axis1 = M.F, axis2 = Dept)) +
  geom_alluvium(aes(fill = Admit), width = 1/12) +
  geom_stratum(width = 1/12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", label.strata = TRUE) 
```

## The Titanic: Multiple Phases

```{r}
data("Titanic")
Titanic
TDF <- as.data.frame(Titanic)
TDF
ggplot(TDF,
       aes(y = Freq, axis1 = Class, axis2 = Age, axis3 = Sex, axis4=Survived)) +
  geom_alluvium(aes(fill = Survived), width = 1/24) +
  geom_stratum(width = 1/12, fill = "white", color = "black") +
  geom_label(stat = "stratum", label.strata = TRUE) +
  scale_x_discrete(limits = c("Class", "Age", "Sex")) + # Fix the x axis
  scale_fill_brewer(type = "qual", palette = "Set1") + # Give it nice colors
  ggtitle("The Fate of Titanic Passengers", subtitle="Class, Sex, Age") # give it a title 

```

### Beyonce Palettes

Now for one better, we can combine variables.  I will use the titanic data and combine Age and Sex into a new variable people.  They will now flow through Class to Survival starting with four types of people.  I recently discovered Beyonce palettes; I will use Beyonce 41 for this alluvial.

```{r}
# devtools::install_github("dill/beyonce")
library(beyonce)
TDF2 <- TDF %>% mutate(People = Sex:Age, AgeS = Age:Survived)
ggplot(TDF2,
       aes(y = Freq, axis1 = People, axis2 = Class, axis3=Survived)) +
  geom_alluvium(aes(fill = AgeS), width = 1/24) +
  geom_stratum(width = 1/12, fill = "white", color = "black") +
  geom_label(stat = "stratum", label.strata = TRUE) +
  scale_x_discrete(limits = c("People", "Class", "Survived")) + # Fix the x axis
  scale_fill_manual(values = beyonce_palette(41)) + # Give it nice colors
  ggtitle("The Fate of Titanic Passengers", subtitle="Class, People") + # give it a title
  theme_minimal()
```


