---
title: "tidy data Principles"
subtitle: "Environments, Ordering, and the Nuts and Bolts of R"  
author: "Robert W. Walker"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE); library(tidyverse); library(dplyr)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer); library(kableExtra)
solarized_dark(
  code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css"
)
```


# Let's Get Started:
## An Overview of R and RStudio

RStudio has tons of useful *Addins* that are useful for specialized tasks.  

--

- We will make use of one today: `esquisse`.  

--

- NB: It exports to powerpoint with some assistance packages<sup>A</sup>.

.footnote[[A] Packages are prepared bits of R code that extend the functionality of base R.  The *tidyverse* is one of many entire ecosystems to perform specific tasks; it is optimized for orderly data analysis.  Among other things, R has extensive contributed documentation by specialists operating in those areas.]

--

```{r, eval=FALSE}
install.packages("esquisse")
```


---
# Let's Have a Look at R

R is a *object oriented* programming language for data.
That implies two things.  
- We will have *functions* on *objects* that create new *objects*.   
- It has a command prompt.  `>`  
- Valid R functions, objects, and/or assignments ( `<-`) go there.  
- The help for any function is provided by `?` before the command.

---
# tidy data

We will think and talk about data organized in a `tidy` way where rows represent **cases/units/observations** and columns represent **variables**.  Many standard forms of enterprise data are not stored in this way though they could be.  Accounting data come to mind where there are `data` in the column names.  There are tools that we will later encounter for `pivoting` from long to wide forms where the `tidy` and long forms are synonymous.

---
# R's Variable Types

- Factor: Qualitative labels with attached numbers.  Think key-value.
- Character: Strings of letters and numbers demarcated by quotation marks.
```
There is 'something' or there is "something"
There is 'Hello World!' or there is "Hello World!"
```
- Numeric [integer, double]
- Complex [of you don't know what this means, worry not]
- Logical
- Date

The global environment in RStudio helps us out.

---
# A Brief Bit on R-Markdown

It is a wonderful technology for repeated tasks and for transparent communication with data.  I will use it extensively.  A Markdown is usually a *Sandbox*, it does not start with packages, libraries, or commands.  It is best to work with RStudio via the play button for *code chunks* and the play all above to make sure that everything syncs up.  One can find a template, with associated help under `Help`.

```
File > New file > R Markdown
```

We are working with FastFood.Rmd -- an R Markdown file.

---
# An Example with Excel Data

When the `Environment` tab is active in the top right of the RStudio.  You will see a tab called `Import Dataset`.  The first thing to note is that *R* reads a number of data types [and link to databases and things].

To import Excel data, `From Excel`   
- We have to give it a file name. *NB Paths*.   

```{r}
library(readxl)
{{ url <- "https://github.com/robertwwalker/DADMStuff/raw/master/FastFood.xlsx" }}
destfile <- "FastFood.xlsx"
curl::curl_download(url, destfile)
FastFood <- read_excel(destfile)
```

--

That's not exacly what I hoped for.  
**There are intermediate steps to downloading it and checking the sheets that it does not do with remote files.**

---
# An Example with Excel Data

When the `Environment` tab is active in the top right of the RStudio.  You will see a tab called `Import Dataset`.  The first thing to note is that *R* reads a number of data types [and link to databases and things].

To import Excel data, `From Excel`   
- We have to give it a file name. *NB Paths*.   
- We have to choose a sheet.  
- Types of variables.  
- Missing data values.  
- Ranges  

```{r}
library(readxl)
url <- "https://github.com/robertwwalker/DADMStuff/raw/master/FastFood.xlsx" 
destfile <- "FastFood.xlsx"
curl::curl_download(url, destfile)
{{ FastFood <- read_excel(destfile, sheet = "FastFood", na = "NA") }}
```

**This will have to be added to the RMarkdown file.**

---
# Some Crash R

Operators:
- +
- -
- *
- /
- and many others.
- We will also be concerned with the difference between equals as assigning and equals in math [denoted with two equals signs in succession].

---
# Scoping and Environments

The hardest thing to many learners about R is the scoping requirements and environments.  We will deploy a collection of packages that have a very data centric view of this problem.  Let me use our Fast Food example.  I can type the name to see what it is.  It dumps a lot to my screen.

```{r eval=FALSE}
FastFood
```

---

```{r eval=require('DT'), tidy=FALSE, echo=FALSE}
DT::datatable(FastFood)
```

---
# In the Beginning [Base R]

We referred to things via `$` to unpack it.  The RStudio remains smart about this; the elements in an object are [mostly] unpacked via `$`.  To find just calories in FastFood, I would need:

```{r}
FastFood$calories
```

---
# Functions

And to embed that into a function, I could have a function that takes some variable, call it x, adds them all up and divides by the total number:

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

```{r}
mean(FastFood$calories)
```

--

Now let's try that for protein.

```{r}
mean(FastFood$protein)
```


**Though there is only one missing datum, that is enough to render the result missing.**

---
# How to Adjust for NA?

Now let's try that for protein.

```{r}
mean(FastFood$protein)
```

**Though there is only one missing datum, that is enough to render the result missing.**

If we wish to fix this, we need, from `?mean`:

```{r}
mean(FastFood$protein, na.rm=TRUE)
```


---
# Scoping

That operator `$` is the first encounter with the `scope` of something.  We are trying to pull `protein` from `FastFood`.  There are other basic operators in $R$ to accomplish the same thing.  We could have asked for the [even less typing-efficient] relevant row and column definition with:

```{r}
FastFood[,"protein"]
```

---

If I want more than one, this becomes cumbersome.  The tidyverse, built around a `piping operator` -- `%>%` --, was developed as a solution to a data.frame centric form of analysis.  Here's how it works.  We start with data and `pipe` it so that the names are understood in the context of the data that we begin with.  The main initial helper that we will make use of is `skim` from the `skimr` library.

---

<small>
```{r, results='markup'}
library(skimr)
FastFood %>% skim() %>% kable() %>% kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```
</small>

---
# dplyr verbs

There are four main `dplyr` verbs that we will play with, and some helpers. 
- filter   
--
- select   
--
- mutate   
--
- summarize or summarise  

---
## filter [1 of 3]

`filter` selects rows according to some set of conditions.  
- Valid with `==`
- Can use `%in%` with a vector `c()`.

<small>
```{r}
FastFood %>% filter(restaurant=="Taco Bell")
FastFood %>% filter(restaurant%in%c("Taco Bell","Burger King"))
FastFood %>% filter(startsWith(restaurant,"S")==TRUE) %>% group_by(restaurant) %>% skim()
```
</small>

---
## filter [2 of 3]

`filter` selects rows according to some set of conditions.  
- Can use `%in%` with a vector `c()`.

<small>
```{r}
FastFood %>% filter(restaurant%in%c("Taco Bell","Burger King"))
```
</small>

---
## filter [3 of 3]

`filter` selects rows according to some set of conditions.  
- Or more elaborate combinations of elements

<small>
```{r, results='markup'}
FastFood %>% filter(startsWith(restaurant,"S")==TRUE) %>% group_by(restaurant) %>% skim() %>% kable() %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
</small>


---
class: inverse
## select [1/2]

`select` selects columns according to some set of names/conditions.  

<small>
```{r}
FastFood %>% select(restaurant, calories)
```

---
class: inverse
## select [2/2]

`select` selects columns according to some set of names/conditions.  

<small>
```{r}
FastFood %>% select(restaurant,starts_with("vit"))
```


---
# mutate [and transmute]

`mutate()` and `transmute()` are the core method for adding variables [columns] to existing data.  The key difference is that `mutate()` retains existing variables while `transmute()` drops them.  Let's see it for sodium, rescaled to grams.

*mutate* will keep all columns.

<small>
```{r}
FastFood %>% 
  mutate(Sodium.Grams = sodium / 1000) %>%
  select(restaurant,Sodium.Grams,sodium,everything())
```
</small>


---
## transmute

*transmute* will only keep the called columns.

<small>
```{r}
FastFood %>% transmute(Sodium.Grams = sodium / 1000)
# To keep a variable, copy it.
# FastFood %>% transmute(restaurant = restaurant, Sodium.Grams = sodium / 1000)
```
</small>

---
## NB: Reassigning or newly assigning

To make these `mutate()` a part of the data, we assign it a *new name* or reassign it.

<small>
```{r}
FastFood <- FastFood %>% mutate(Sodium.Grams = sodium / 1000)
My.Fast.Food <- FastFood %>% mutate(Sodium.Grams = sodium / 1000)
```


---
# The Magic of `group_by`

`group_by` is a core `tidyverse` operator for repeating something by groups.  By itself, it simply splits a data object according to the grouping variable(s).

--

**But that is exactly what a pivot table does.**

---
# Grouping and pipes

<small>
```{r, results='markup'}
FastFood %>% group_by(restaurant) %>% skim() %>% kable() %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")

```
</small>

---

# Fixing a Frustration

```{r}
FastFood <- FastFood %>% mutate(Chicken = grepl('Chicken|Chick-n',item))
```

---
# A Two Variable Pivot

<small>
```{r, results='markup'}
FastFood %>% group_by(restaurant,Chicken) %>% skim(Sodium.Grams) %>% kable() %>% kable_styling() %>% scroll_box(width = "100%", height = "50%")
```
</small>

---
# summarise / summarize

Is the analog to creating a pivot table in R by whatever groupings we wish.

```{r}
FastFood %>% group_by(restaurant) %>% summarise(Mean.Protein = mean(protein), Mean.Protein.NA = mean(protein, na.rm=TRUE))
```

---
# summarise

Is the analog to creating a pivot table in R by whatever groupings we wish.

```{r}
FastFood %>% group_by(restaurant, Chicken) %>% summarise(Mean.Protein = mean(protein), Mean.Protein.NA = mean(protein, na.rm=TRUE))
```


---
# ungroup()

We need `ungroup()` when we want to combine `mutate()` and `group_by()` to calculate aggregate statistics for all relevant rows.

<small>
```{r}
FastFood <- FastFood %>% 
  group_by(restaurant) %>% 
  mutate(Avg.Protein = mean(protein, na.rm=TRUE)) %>% 
  ungroup()
```
</small>

---
# arrange() [1/2]

We can use arrange to sort a result.  For example,

```{r}
FastFood %>% 
  group_by(restaurant) %>% 
  summarise(Avg.Calories = mean(calories)) %>% 
  arrange(Avg.Calories)
```

---
# arrange() [2/2]

We can use arrange to sort a result, and `desc()` to flip it.  For example,

```{r}
FastFood %>% 
  group_by(restaurant) %>% 
  summarise(Avg.Calories = mean(calories)) %>% 
  arrange(desc(Avg.Calories))
```

---
# A Basic Table: Counts

```{r}
( Restaurant.Table <- FastFood %>% group_by(restaurant) %>% summarise(Count = n()) %>% arrange(Count) )
```

---
# A More Elaborate Table: Counts

```{r}
( Rest.Chicken.Table <- FastFood %>% group_by(restaurant,Chicken) %>% summarise(Count = n()) )
```

---
# Visualising Restaurants and Chicken

```{r}
Rest.Chicken.Table %>% ggplot() + aes(x=restaurant, y=Count, fill=Chicken) + geom_col() + coord_flip()
```


---
# A First Data Visualisation [Chained]

```{r}
FastFood %>% 
  group_by(restaurant) %>% 
  summarise(Count = n()) %>%
  ggplot() + aes(x=restaurant, y=Count) + geom_col()
```

---
# More Chaining [`fct_reorder()`]

```{r}
FastFood %>% group_by(restaurant) %>% summarise(Count = n()) %>% ggplot() + aes(x=fct_reorder(restaurant, Count), y=Count) + geom_col() + labs(x="Chain", y="Count") + coord_flip() 
```

---
# Even More Chaining

```{r}
FastFood %>% group_by(restaurant) %>% summarise(Count = n()) %>% ggplot() + aes(x=fct_reorder(restaurant, desc(Count)), y=Count) + geom_col() + labs(x="Chain", y="Count") + coord_flip() 
```

---
class: inverse

# A Note on Skim

```{r}
FastFood %>% group_by(restaurant) %>% 
  summarise(Mean = mean(calories), 
            SD = sd(calories), 
            Min = min(calories), 
            Median = median(calories), 
            Max = max(calories), 
            Q1 = quantile(calories, 0.25), 
            Q3 = quantile(calories, 0.75))
```

---
class: inverse

# A Recap

Four `dplyr` verbs:  
- filter  
- select  
- mutate / transmute  
- summarise  
- `group_by` and `ungroup`
- helpers: arrange and desc