---
title: COVID in the US and the World
author: Robert W. Walker
date: '2020-03-25'
slug: covid-in-the-us-and-the-world
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-03-25T23:33:58-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

# The Johns Hopkins dashboard

This is what [Johns Hopkins has provided as a dashboard using ARCGIS](https://coronavirus.jhu.edu/map.html).  They have essentially layered out the data into national and subnational data and then used the arcgis dashboard to cycle through them.

<iframe width="650" height="400" frameborder="0" scrolling="no" marginheight="0" marginwidth="0" title="2019-nCoV" src="//gisanddata.maps.arcgis.com/apps/Embed/index.html?webmap=14aa9e5660cf42b5b4b546dec6ceec7c&extent=77.3846,11.535,163.5174,52.8632&zoom=true&previewImage=false&scale=true&disable_scroll=true&theme=light"></iframe>

# The data

```{r, message=FALSE, warning=FALSE}
library(tidyverse); library(sf); library(rnaturalearth); library(rnaturalearthdata); library(ggmap)
March26JH <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-26-2020.csv"))
```

# A Leaflet

Johns Hopkins also has an extensive collection of data.  Let's see what one set looks like.

```{r, warning=FALSE, message=FALSE}
library(leaflet); library(rMaps); library(leaflet.extras)
L2 <- leaflet(March26JH) %>% 
  addTiles() %>% 
#  addCircles(lng = ~Long, lat = ~Lat, weight = 1, radius = 1, popup = ~Combined_Key) %>% 
  addHeatmap(lng=~Long_,
             lat=~Lat,
             radius = 9,
             intensity = ~Confirmed)
library(widgetframe)
frameWidget(L2)
``` 


# `@jburnmurdoch` of the Financial Times

```{r}
SR.TS <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/who_covid_19_situation_reports/who_covid_19_sit_rep_time_series/who_covid_19_sit_rep_time_series.csv"))
```
Something is wrong with the `3/5/2020` column.  It has two values; one a number and another parenthetical number.  I just remove the parenthetical.

```{r}
SR.TS <- SR.TS %>% mutate(`3/5/2020` = as.numeric(str_remove(`3/5/2020`,"(418)")))
```

# Global Coronavirus Cases

Now it is time to rearrange this data.  Let's start with the global case totals.

```{r}
SR.Global <- SR.TS %>% filter(`Country/Region`=="Globally") %>% pivot_longer(cols=c(4:dim(SR.TS)[[2]])) %>% pivot_wider(., names_from = `Province/States`, values_from = value) %>% mutate(date=as.Date(name, format = "%m/%d/%Y"))
```

## The Plot

```{r}
ggplot(SR.Global) +
 aes(x = date, y = Confirmed) +
 geom_line(size = 1L, colour = "#c6dbef") +
 geom_point(size = 1L, colour = "#c6dbef") +
 labs(x = "Date", y = "Confirmed Cases", title = "Global Cases of Coronavirus") +
 hrbrthemes::theme_ft_rc()
```

# Deaths

```{r}
ggplot(SR.Global) +
 aes(x = date, y = Deaths) +
 geom_line(size = 1L, colour = "#c6dbef") +
 geom_point(size = 1L, colour = "#c6dbef") +
 labs(x = "Date", y = "Confirmed Deaths", title = "Reported Global Deaths from COVID-19") +
 hrbrthemes::theme_ft_rc()
```

That is legitimately odd.

```{r, eval=FALSE}
TS2 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))
Tidy.Counts <- TS2 %>% pivot_longer(., cols=c(5:dim(TS2)[[2]]), names_to = "date", values_to = "Cases")
```

# The US Counties Data

```{r}
library(urbnmapr); library(ggthemes)
USCounties <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")
library(tigris); library(rgdal); library(htmltools); library(viridis); library(sf); library(viridis)
counties.t <- get_urbn_map("counties", sf=TRUE) %>% mutate(fips = county_fips)
# Map.Me <- left_join(counties.t,Oregon.COVID, by=c("NAME" = "County"))
Map.Me <- merge(counties.t, USCounties)
```

The county level choropleth is not a very good plot.  Too much is missing and it is hard to se any variation at all.  The epidemic is currently concentrated.

```{r}
Map.Me %>% filter(date=="2020-03-28") %>% ggplot(., aes(geometry=geometry, fill=cases)) + geom_sf() + scale_fill_viridis_c() + theme_map()
```

I don't really like that so I will put it together with a bubble.

```{r}
# devtools::install_github("hafen/housingData")
Map.Me.2 <- left_join(housingData::geoCounty, USCounties, by="fips")
MM3 <- merge(counties.t,Map.Me.2)
Map1 <- counties.t %>% ggplot(., aes(geometry=geometry)) + geom_sf(color="black", size=0.1, alpha=0.2) + theme_map()
MM3 %>% 
  filter(date=="2020-03-28") %>% 
  ggplot(.) + 
  geom_point(aes(y=lat, x=lon, color=cases, fill=cases, size=cases), alpha=0.35, shape=21, color="red", inherit.aes = FALSE) + 
  scale_size(range = c(.1, 24), name="Population (M)") +  
  guides(size=FALSE) + 
  scale_fill_continuous_tableau(palette = "Red") + 
  labs(title="COVID-19 by County Reporting")
```

# A Leaflet

```{r}
library(leaflet)
MM2 <- Map.Me.2 %>% filter(date=="2020-03-28")
mytext <- paste("County: ", MM2$county.x, "<br/>", 
   "State: ", MM2$state.x, "<br/>", 
   "Cases: ", MM2$cases, "<br/>", 
   "Deaths: ", MM2$deaths, sep="") %>%
   lapply(htmltools::HTML)
mypalette <- colorNumeric(palette="viridis", domain=Map.Me.2$cases, na.color="transparent")
m <- Map.Me.2 %>% filter(date=="2020-03-28") %>% leaflet(.) %>% 
  addTiles()  %>% 
  addCircleMarkers(~lon, ~lat, fillColor = ~mypalette(cases), fillOpacity = 0.2, color="white", radius = ~ sqrt(cases)/2, stroke=FALSE,    label = mytext, labelOptions = labelOptions( style = list("font-weight" = "normal", padding = "3px 8px"), textsize = "13px", direction = "auto")) %>% addLegend(pal=mypalette, values=~cases, opacity=0.9, title = "Cases", position = "bottomright")
m 
```

