---
title: COVID in the US and the World
author: Robert W. Walker
date: '2020-03-25'
slug: covid-in-the-us-and-the-world
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-03-25T23:33:58-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

# New York Times data for the US

```{r, message=FALSE, warning=FALSE}
library(tidyverse); library(hrbrthemes)
state.data <- read_csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv"))
Rect.NYT <- complete(state.data, state,date)
Rect.NYT <- Rect.NYT %>% group_by(state) %>% mutate(New.Cases = cases - lag(cases, order_by = date), New.Deaths = deaths - lag(deaths, order_by = date)) %>% ungroup()
ggplot(Rect.NYT, aes(x=date, y=New.Cases, color=state)) + geom_line() + guides(color=FALSE)
```

```{r}
NYT.Totals <- Rect.NYT %>% group_by(date) %>% summarise(Deaths = sum(deaths, na.rm=TRUE), New.Deaths = sum(New.Deaths, na.rm = TRUE), Cases = sum(cases, na.rm=TRUE), New.Cases = sum(New.Cases, na.rm = TRUE))
library(patchwork)
ggplot(NYT.Totals, aes(x=date, y=New.Cases)) + geom_line() + labs(x="Date", y="New COVID-19 Cases", title="Daily: New COVID-19 Cases") + theme_ipsum() + theme(axis.text.x = element_text(size=8, angle=45))+ ggplot(NYT.Totals, aes(x=date, y=New.Deaths)) + geom_line() + labs(x="Date", y="New COVID-19 Deaths", title="Daily: New COVID-19 Deaths") + theme_ipsum() + theme(axis.text.x = element_text(size=8, angle=45)) 
```


## Totals

```{r}
ggplot(NYT.Totals, aes(x=date, y=Cases)) + geom_line() + labs(x="Date", y="Total COVID-19 Cases", title="Total COVID-19 Cases") + theme_ipsum() + theme(axis.text.x = element_text(size=8, angle=45))+ ggplot(NYT.Totals, aes(x=date, y=Deaths)) + geom_line() + labs(x="Date", y="Total COVID-19 Deaths", title="Total COVID-19 Deaths") + theme_ipsum() + theme(axis.text.x = element_text(size=8, angle=45))
```

## US Death Rate

Given the data, what does the US Case Fatality Rate look like at this point?  Two caveats for this.  The first, uncertainty in the numerator.  The number of deaths is surely undercounted, probably dramatically based on anecdotes from non-medical first responders.  Second, we know the numerator is also undercounted.  Assuming asymptomatic cases, the rules prohibited testing them for a substantial period of time on top of the existing scarcity of tests. 

```{r}
library(hrbrthemes); library(plotly)
CFR <- NYT.Totals %>% mutate(CFR = round(Deaths / Cases, digits=3)) %>% ggplot(., aes(x=date, y=CFR)) + geom_line() + geom_point(color="skyblue") + labs(title = "Case Fatality Rate of COVID-19 in the US", caption="Very uncertain estimate... Numerator and denominator uncertain \n Data: NY Times GitHub")
ggplotly(CFR)
```



# The Johns Hopkins dashboard

This is what [Johns Hopkins has provided as a dashboard using ARCGIS](https://coronavirus.jhu.edu/map.html).  They have essentially layered out the data into national and subnational data and then used the arcgis dashboard to cycle through them.

<iframe width="650" height="400" frameborder="0" scrolling="no" marginheight="0" marginwidth="0" title="2019-nCoV" src="//gisanddata.maps.arcgis.com/apps/Embed/index.html?webmap=14aa9e5660cf42b5b4b546dec6ceec7c&extent=77.3846,11.535,163.5174,52.8632&zoom=true&previewImage=false&scale=true&disable_scroll=true&theme=light"></iframe>

# The data

There are a few different types of data available.  I am relying on the same sources that Johns Hopkins is using for the county level incident data.

```{r, message=FALSE, warning=FALSE}
library(tidyverse); library(sf); library(rnaturalearth); library(rnaturalearthdata); library(ggmap)
March26JH <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-26-2020.csv"))
March29JH <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-29-2020.csv"))
```

# A Leaflet

Let's see what one set looks like.  I am doing this first for March 26; after, I will do March 29.

```{r, warning=FALSE, message=FALSE}
library(leaflet); library(rMaps); library(leaflet.extras)
L2 <- leaflet(March26JH) %>% 
  addTiles() %>% 
#  addCircles(lng = ~Long, lat = ~Lat, weight = 1, radius = 1, popup = ~Combined_Key) %>% 
  addHeatmap(lng=~Long_,
             lat=~Lat,
             radius = 9,
             intensity = ~Confirmed)
library(widgetframe)
frameWidget(L2)
``` 

### March 29

```{r}
L2 <- leaflet(March29JH) %>% 
  addTiles() %>% 
#  addCircles(lng = ~Long, lat = ~Lat, weight = 1, radius = 1, popup = ~Combined_Key) %>% 
  addHeatmap(lng=~Long_,
             lat=~Lat,
             radius = 9,
             intensity = ~Confirmed)
library(widgetframe)
frameWidget(L2)
```


# `@jburnmurdoch` of the Financial Times

Now I will work with the nominal time series of this.

```{r}
SR.TS <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/who_covid_19_situation_reports/who_covid_19_sit_rep_time_series/who_covid_19_sit_rep_time_series.csv"))
```
Something is wrong with the `3/5/2020` column.  It has two values; one a number and another parenthetical number.  I just replace the value.

```{r}
SR.TS$`3/5/2020`[18] <- "128"
SR.TS <- SR.TS %>% mutate(`3/5/2020` = as.numeric(`3/5/2020`))
```

# Global Coronavirus Cases

Now it is time to rearrange this data.  Let's start with the global case totals.

```{r}
SR.Global <- SR.TS %>% filter(`Country/Region`=="Globally") %>% pivot_longer(cols=c(4:dim(SR.TS)[[2]])) %>% pivot_wider(., names_from = `Province/States`, values_from = value) %>% mutate(date=as.Date(name, format = "%m/%d/%Y"))
```

## The Plot

```{r}
ggplot(SR.Global) +
 aes(x = date, y = Confirmed) +
 geom_line(size = 1L, colour = "#c6dbef") +
 geom_point(size = 1L, colour = "#c6dbef") +
 labs(x = "Date", y = "Confirmed Cases", title = "Global Cases of Coronavirus") +
 hrbrthemes::theme_ft_rc()
```

# Deaths

```{r}
ggplot(SR.Global) +
 aes(x = date, y = Deaths) +
 geom_line(size = 1L, colour = "#c6dbef") +
 geom_point(size = 1L, colour = "#c6dbef") +
 labs(x = "Date", y = "Confirmed Deaths", title = "Reported Global Deaths from COVID-19") +
 hrbrthemes::theme_ft_rc()
```

That is legitimately odd.

```{r, eval=FALSE}
TS2 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))
Tidy.Counts <- TS2 %>% pivot_longer(., cols=c(5:dim(TS2)[[2]]), names_to = "date", values_to = "Cases")
```

# The US Counties Data

```{r}
library(urbnmapr); library(ggthemes)
USCounties <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")
library(tigris); library(rgdal); library(htmltools); library(viridis); library(sf); library(viridis)
counties.t <- get_urbn_map("counties", sf=TRUE) %>% mutate(fips = county_fips)
# Map.Me <- left_join(counties.t,Oregon.COVID, by=c("NAME" = "County"))
Map.Me <- merge(counties.t, USCounties)
```

The county level choropleth is not a very good plot.  Too much is missing and it is hard to se any variation at all.  The epidemic is currently concentrated.

```{r}
Map.Me %>% filter(date=="2020-03-28") %>% ggplot(., aes(geometry=geometry, fill=cases)) + geom_sf() + scale_fill_viridis_c() + theme_map()
```

I don't really like that so I will put it together with a bubble.  I have intentionally left out Hawaii and Alaska from this plot.

```{r}
library(rnaturalearth)
# devtools::install_github("hafen/housingData")
Map.Me.2 <- left_join(housingData::geoCounty, USCounties, by="fips")
MM3 <- merge(counties.t,Map.Me.2)
Map1 <- counties.t %>% ggplot(., aes(geometry=geometry)) + geom_sf(color="black", size=0.1, alpha=0.2, fill="white")
Shorty <- MM3 %>% filter(date=="2020-03-28")
world <- ne_countries(scale = "medium", returnclass = "sf")
counties <- st_as_sf(maps::map("county", plot = FALSE, fill = TRUE))
ggplot(data = world) + geom_sf() +
  geom_sf(data = counties, color = "grey", alpha=0.1, size=0.1) +
  coord_sf(xlim = c(-130, -65), ylim = c(20, 55), expand = FALSE) +
  geom_point(data=Shorty, aes(y=lat, x=lon, color=cases, fill=cases, size=cases), alpha=0.35, shape=21, color="red", inherit.aes = FALSE) + 
  scale_size(range = c(.1, 24)) +  
  guides(size=FALSE) + 
  scale_fill_continuous_tableau(palette = "Red") + 
  labs(title="COVID-19 by County Reporting") + theme_map()
```

# A Leaflet

```{r}
library(leaflet)
MM2 <- Map.Me.2 %>% filter(date=="2020-03-28")
mytext <- paste("County: ", MM2$county.x, "<br/>", 
   "State: ", MM2$state.x, "<br/>", 
   "Cases: ", MM2$cases, "<br/>", 
   "Deaths: ", MM2$deaths, sep="") %>%
   lapply(htmltools::HTML)
mypalette <- colorNumeric(palette="viridis", domain=Map.Me.2$cases, na.color="transparent")
m <- Map.Me.2 %>% filter(date=="2020-03-28") %>% leaflet(.) %>% 
  addTiles()  %>% 
  addCircleMarkers(~lon, ~lat, fillColor = ~mypalette(cases), fillOpacity = 0.2, color="white", radius = ~ sqrt(cases)/2, stroke=FALSE,    label = mytext, labelOptions = labelOptions( style = list("font-weight" = "normal", padding = "3px 8px"), textsize = "13px", direction = "auto")) %>% addLegend(pal=mypalette, values=~cases, opacity=0.9, title = "Cases", position = "bottomright")
m 
```

