---
title: tidyTuesday on the Office
author: Robert W. Walker
date: '2020-03-19'
slug: tidytuesday-on-the-office
categories:
  - R
  - tidyTuesday
  - tidyverse
tags:
  - tidyTuesday
  - R
subtitle: ''
summary: ''
authors: []
lastmod: '2020-03-19T14:46:04-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


## The Office



```{r cars, message=FALSE, warning=FALSE}
library(tidyverse)
office_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv')
```

## A First Plot

The number of episodes for the Office by season.

```{r pressure, message=FALSE, warning=FALSE}
library(janitor)
TableS <- office_ratings %>% tabyl(season)
p1 <- TableS %>% ggplot(., aes(x=as.factor(season), y=n, fill=as.factor(season))) + geom_col() + labs(x="Season", y="Episodes", title="The Office: Episodes") + guides(fill=FALSE)
p1
```

# Ratings

How are the various seasons and episodes rated?

```{r, message=FALSE, warning=FALSE}
p2 <- office_ratings %>% ggplot(., aes(x=as.factor(season), y=imdb_rating, fill=as.factor(season), color=as.factor(season))) + geom_violin(alpha=0.3) + guides(fill=FALSE, color=FALSE) + labs(x="Season", y="IMDB Rating") + geom_point()
p2
```


# Patchwork

Using `patchwork`, we can combine multiple plots.

```{r}
library(patchwork)
(p1) / p2
```

# Ratings Part II

Let's show the episode names.  The tooltip doesn't interact well with the violin plot.  It needs points by themselves.

```{r, message=FALSE, warning=FALSE}
library(widgetframe)
p3 <- office_ratings %>% ggplot(., aes(x=as.factor(season), y=imdb_rating, fill=as.factor(season), color=as.factor(season), text=title)) + geom_point()  + guides(fill=FALSE, color=FALSE) + labs(x="Season", y="IMDB Rating") 
# The violin was trashing the tooltip.  I have to get rid of it.
library(plotly)
# ggplotly(p3, tooltip = "text")
p3
```

# Something I Like

A better and more customized version of the violin plot.

```{r}
library(hrbrthemes); library(ggthemes)
ggplot(office_ratings, aes(x=as.factor(season), y=imdb_rating, fill=as.factor(season), color=as.factor(season))) + geom_violin(alpha=0.3) + guides(fill=FALSE, color=FALSE) + labs(x="Season", y="IMDB Rating", title="IMDB Ratings: The Office by Season", caption="a #tidyTuesday") + theme_economist_white() + scale_fill_ipsum() + scale_color_ipsum() + geom_jitter()
```

# A Plotly

`ggplotly` does not love multiple geoms.  In this case, the lines are ignored but the tool tip works.

```{r}
p4 <- ggplot(office_ratings, aes(x=air_date, y=imdb_rating, color=as.factor(season), text=title)) + geom_point() + geom_smooth() +  guides(color=FALSE) + labs(x="Date Aired", y="IMDB Rating")
# The tooltip kills the smooth.
p5 <- ggplotly(p4)
htmlwidgets::saveWidget(
  widgetframe::frameableWidget(p5), here:::here('static/img/widgets/ttop5map.html'))
```

<iframe width="600" height="405" src="https://rww.science/img/widgets/ttop5map.html" frameborder="0" allowfullscreen></iframe>

