---
title: "1 and 2 Sample Means-Proportions"
author: "Robert W. Walker"
date: "2020-02-19"
autosize: true
output: 
  slidy_presentation
---


The Basic Idea
========================================================

Two classes of statistics have known distributions. 

- Means have a t distribution.
- Proportions have a normal distribution if the expected number of both categories exceeds 5.


The Mean: t
========================================================

The t distribution
- is entirely defined by degrees of freedom.
- has as metric, the standard error [in this case of the mean]

***
The equations:
$$
\Large
t = \frac{\overline{x} - \mu}{\frac{s}{\sqrt{n}}} 
$$
and
$$
\Large
\mu = \overline{x} + t(\frac{s}{\sqrt{n}})
$$
The true mean is symmetric about the sample mean with t defining the number of standard errors of the mean above and below.

The t distribution (df=24)
========================================================


```{r Pic1, echo=FALSE}
LEDLifetimes <- structure(list(lifetime = c(37160, 37032, 37975.3, 36694, 39394.7, 
40761.4, 38426, 40746.1, 38439.3, 36634.6, 38006.7, 39460.7, 
37282, 42966.8, 38000, 37031.3, 40910.7, 39562.7, 36563.3, 37349.3, 
34993.9, 36712, 38246.7, 35429.9, 34220.6)), .Names = "lifetime", class = "data.frame", row.names = c(NA, 
-25L))
library(RcmdrMisc)
local({
  .x <- seq(-3.745, 3.745, length.out=1000)  
  plotDistr(.x, pt(.x, df=24), cdf=TRUE, xlab="x", ylab="Density", 
  main=paste("t Distribution:  df=24"))
})
```

***
```{r Q1}
# 99 percent, then 95, 90, and 80
qt(c(0.005,0.995), df=24)
qt(c(0.025,0.975), df=24)
qt(c(0.05,0.95), df=24)
qt(c(0.1,0.9), df=24)
```

LED Lifetimes (df=24)
========================================================

```{r Pic2, echo=FALSE}
local({
  .x <- seq(-3.745, 3.745, length.out=1000)  
  plotDistr(mean(LEDLifetimes$lifetime)+sd(LEDLifetimes$lifetime)/sqrt(25)*.x, pt(.x, df=24), cdf=TRUE, xlab="Hours [average]", ylab="Density", 
  main=paste("Mean LED Lifetimes"))
})
abline(h=c(0.005,0.995), col="red")
abline(h=c(0.05,0.95), col="blue")
```

***
```{r Q2, echo=TRUE}
# 99 percent, then 95, 90, and 80
mean(LEDLifetimes$lifetime)+sd(LEDLifetimes$lifetime)/sqrt(25)*qt(c(0.005,0.995), df=24)
```
```{r Q2a, echo=FALSE}
mean(LEDLifetimes$lifetime)+sd(LEDLifetimes$lifetime)/sqrt(25)*qt(c(0.025,0.975), df=24)
mean(LEDLifetimes$lifetime)+sd(LEDLifetimes$lifetime)/sqrt(25)*qt(c(0.05,0.95), df=24)
mean(LEDLifetimes$lifetime)+sd(LEDLifetimes$lifetime)/sqrt(25)*qt(c(0.1,0.9), df=24)
```

The Complete Picture
==============================

```{r Pic3, echo=FALSE}
par(mfrow=c(2,2))
local({
  .x <- seq(-3.745, 3.745, length.out=1000)  
  plotDistr(.x, pt(.x, df=24), cdf=TRUE, xlab="x", ylab="Density", 
  main=paste("t Distribution:  df=24"))
})
local({
  .x <- seq(-3.745, 3.745, length.out=1000)  
  plotDistr(sd(LEDLifetimes$lifetime)/sqrt(25)*.x, pt(.x, df=24), cdf=TRUE, xlab="x", ylab="Density", 
  main=paste("Scaled t Distribution:  df=24"))
})
local({
  .x <- seq(-3.745, 3.745, length.out=1000)  
  plotDistr(mean(LEDLifetimes$lifetime)+.x, pt(.x, df=24), cdf=TRUE, xlab="x", ylab="Density", 
  main=paste("Shifted t Distribution:  df=24"))
})
local({
  .x <- seq(-3.745, 3.745, length.out=1000)  
  plotDistr(mean(LEDLifetimes$lifetime)+sd(LEDLifetimes$lifetime)/sqrt(25)*.x, pt(.x, df=24), cdf=TRUE, xlab="Hours [average]", ylab="Density", 
  main=paste("Mean LED Lifetimes"))
})
abline(h=c(0.005,0.995), col="red")
abline(h=c(0.05,0.95), col="blue")
```
***

```{r Ans1A}
with(LEDLifetimes, (t.test(lifetime, alternative='two.sided', mu=0.0, 
  conf.level=.95)))
```

Hypothesis Tests
=====================================================

Assume a true mean $\mu$.  How likely, if $\mu$ is true, is the sample mean that we obtained?  Now, $\mu$, $\overline{x}$, $s$, and $n$ are known.  We need only figure out the question and the associated probability.  Do we wish to know....
- whether $\mu$ is equal to some value (two-sided alternative).
- whether $\mu$ is greater than some value.
- whether $\mu$ is less than some value.

***
We will examine the probability of the complements.  We find a sample mean of 36800 given a sample size of 16?  `r (36800-38000)/500`.  The probabilities are 
- `r round(pt(c((36800-38000)/500), df=15), digits=4)` with inequality [one-tail] 
- `r round(2*pt(c((36800-38000)/500), df=15), digits=4)` with not equal to [two-tails].

$$
\Large
t = \frac{36800 - 38000}{\frac{2000}{\sqrt{16}}} = -2.4
$$

=============================
left: 40%
title: false

```{r Pic5a, echo=FALSE}
par(mfrow=c(1,2))
local({
  .x <- seq(-4.073, 4.073, length.out=1000)  
  plotDistr(.x, dt(.x, df=15), cdf=FALSE, xlab="x", ylab="Density", 
  main=paste("t Distribution:  Degrees of freedom=15"), regions=list(c(-4, 
  -2.4)), col=c('#BEBEBE', '#BEBEBE'), legend.pos='topright')
})
local({
  .x <- seq(-3.745, 3.745, length.out=1000)  
  plotDistr(mean(LEDLifetimes$lifetime)+sd(LEDLifetimes$lifetime)/sqrt(16)*.x, pt(.x, df=15), cdf=TRUE, xlab="Hours [average]", ylab="Density", 
  main=paste("Mean LED Lifetimes"))
})
abline(v=36800)
```
***
N=25 [the data]
```{r}
with(LEDLifetimes, (t.test(lifetime, alternative='two.sided', mu=36800, 
  conf.level=.95)))
```

Solving for n
====================================
The equations:
$$
\Large
t = \frac{\overline{x} - \mu}{\frac{s}{\sqrt{n}}} 
$$
and
$$
\Large
n = [\frac{st}{(\overline{x} - \mu)}]^2
$$
We take the size of the necessary confidence interval and divide by the acceptable and assumed margin for error and square the result.  It's not perfect; the realized margin of error depends on the sample as does $s$.  This is hard to solve because t depends on $n$.  

*We can approximate with a normal; it will be less wrong as the required sample gets big.*

Proportions (with a caveat)
=====================================================
There are restrictions on when this works (np and n(1-p) greater than 5).

It allows us to, given data, ask for a reasonable range of the true probability $\pi$ or $p_0$ in a binomial.  It is heavily deployed in survey sampling [especially in the polling silly season].

Equations for Proportions
=======================================================
The equations:
$$
\Large
z = \frac{\hat{p} - \pi}{\sqrt(\frac{p(1-p)}{n}} 
$$
and
$$
\Large
\pi = \hat{p} + z\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}
$$

***

- $\pi$ -- the true probability of a positive response.
- $\hat{p}$ -- the estimated probability/proportion of positive responses.
- $z$ -- quantiles from the standard normal distribution.
- $n$ -- the number of respondents

Food Satisfaction
====================================

- 100 respondents
- 46 satisfied
- What confidence?
  - 95 percent lower bound? $z=-1.645$
  - 95 percent upper bound? $z=1.645$
  - 95 percent central interval? $z=(-1.96,1.96)$
- $\pi$ is unknown.

***
$$
\Large
\pi = 0.46 + z\sqrt{\frac{0.46(1-0.46)}{100}}
$$
$$
\Large
\pi = 0.46 + z*0.05
$$
- What confidence?
  - 95 percent lower bound? $z=-1.645$ `r round(0.46 + qnorm(0.05)*sqrt(0.46*(0.54)/100), digits=3)`
  - 95 percent upper bound? $z=1.645$ `r round(0.46 + qnorm(0.95)*sqrt(0.46*(0.54)/100), digits=3)`
  - 95 percent central interval? $z=(-1.96,1.96)$ `r round(0.46 + qnorm(c(0.025,0.975))*sqrt(0.46*(0.54)/100), digits=3)`

The Distribution
================================================
left: 70%
```{r Ch1a, echo=FALSE}
par(mfrow=c(1,2))
local({
  .x <- seq(0.292, 0.624, length.out=1000)  
  plotDistr(.x, dnorm(.x, mean=0.46, sd=0.05), cdf=FALSE, xlab="x", 
  ylab="Density", 
  main=paste("Normal:  p-hat=0.46, Std. err.=0.05"))
})
local({
  .x <- seq(0.292, 0.624, length.out=1000)  
  plotDistr(.x, pnorm(.x, mean=0.46, sd=0.05), cdf=TRUE, xlab="x", 
  ylab="Density", 
  main=paste("Normal:  p-hat=0.46, Std. err.=0.05"))
})
abline(h=c(0.025,0.975), col="red")
```
***
I reordered the outcomes.


================================
title: false

```{r Res2, echo=FALSE}
FoodSat <- structure(list(Satisfied. = structure(c(1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L), .Label = c("Yes", 
"No"), class = "factor")), row.names = c(NA, -100L), .Names = "Satisfied.", class = "data.frame")
local({
  .Table <- xtabs(~ Satisfied. , data= FoodSat )
#  cat("\nFrequency counts (test is for first level):\n")
#  print(.Table)
  prop.test(rbind(.Table), alternative='two.sided', p=.5, conf.level=.95, 
  correct=FALSE)
})
```
```{r BH2}
p.hat <- 0.46 
p.hat+qnorm(c(0.025,0.975))*sqrt(p.hat*(1-p.hat)/100)
```

The probability of 0.5
=========================================
```{r BH3, echo=FALSE}
local({
  .Table <- xtabs(~ Satisfied. , data= FoodSat )
#  cat("\nFrequency counts (test is for first level):\n")
#  print(.Table)
  prop.test(rbind(.Table), alternative='less', p=.5, conf.level=.95, 
  correct=FALSE)
})
```
***

```{r BH4}
p <- 0.5; p.hat <- 0.46; (p.hat - p)/sqrt(p*(1-p)/100)
pnorm((p.hat - p)/sqrt(p*(1-p)/100))
2*pnorm((p.hat - p)/sqrt(p*(1-p)/100))
p.hat+qnorm(0.95)*sqrt(p^2/100)
```


The Exact Binomial
==========================================

Solves a problem in this way.  *What would $p$ have to be to generate this set of binomial outcomes with the given probability?*  In this instance, it runs through the possible values of p so that 
- 46 or more yes's are 97.5 percent and then that 
- 46 or fewer yes's are 2.5 percent.

***

```{r ExBin2, echo=TRUE}
pbinom(45, size=100, prob=0.3598434)
pbinom(46, size=100, prob=0.5625884)
```


=======================================
title: false

```{r ExBin, echo=FALSE,width=1200}
local({
  .Table <- xtabs(~ Satisfied. , data= FoodSat )
  cat("\nFrequency counts (test is for first level):\n")
  print(.Table)
  binom.test(rbind(.Table), alternative='two.sided', p=.5, conf.level=.95)
})
```

The Famous Survey Margin for Error
=============================================
Find one...

$$
n = \frac{z^2*SE(p)^2}{MOE^2} \\
MOE = \sqrt{\frac{z*\sqrt{SE(p)}}{N}}
$$
***
```{r Exs1, width=800}
sqrt(1.96*0.5/517)
sqrt(1.96*0.5/701)
sqrt(1.96*0.5/657)
sqrt(1.96*0.5/902)
```

If we designed an Oregon poll for 3 percent error with 95% confidence.
===================================================
- The needed z with 95 percent confidence is 1.96
- The MOE is 0.03
- Assume a tie [p=0.5].
- We need 1068.  You should round people up....
```{r ORPoll}
1.96^2*0.5^2/0.03^2
```

From One-Sample to Two
====================================================
The ideas of confidence intervals and hypothesis tests also extend to comparisons among samples.  Before developing these ideas, we need to introduce the key idea of covariance.

Sample covariance is the shared variation in two observed variables defined as (with metric (xy)) - populations would substitute $\mu$ for $\overline{x,y}$:

$$
\Large
Cov(x,y) = \frac{1}{n-1}\sum_{i=1}^{n} (x_{i} - \overline{x})(y_{i} - \overline{y})
$$

The idea of correlation is related, we divide by the standard deviation of the two variables to render it metricless [and absolute between -1 and 1].

$$
\Large
Cor(x,y) = \frac{\sum_{i=1}^{n} (x_{i} - \overline{x})(y_{i} - \overline{y})}{s_{x}s_{y}}
$$

Covariance Matters
======================================================
We can measure covariance.  **But the measured covariance depends on the mean.**

- *If we want to ask if means are different, we must assume something about covariance.*  Either:
  - Independent (Independent sampling)
  - Dependent (Paired/Matched Sampling)

Are the units sampled in **independent** or **dependent** fashion?

The Equations
=========================================================

Are given in your text on 217--221.  The same duality exists here between $\hat{\pi}$ versus hypotheses about $\pi$.  The way this is handled when one claims no difference is different than when one claims a difference [see section 6.2.4, p.222].  

**Simulation renders much of this silly.**

```{r Data2, echo=FALSE}
Defaults <- structure(list(Commercial = c(1L, 0L, 0L, 0L, 0L, 1L, 0L, 0L, 
0L, 0L, 1L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 0L, 1L, 
0L, 0L, 1L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 1L, 
0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 1L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 1L, 1L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 1L, 0L, 0L, 0L, 1L, 0L, 0L, 1L, 0L, 0L, 0L, 1L, 0L, 1L, 0L, 
0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 0L, 
0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 0L, 1L, 0L
), Consumer = c(1L, 0L, 0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 1L, 0L, 
1L, 1L, 0L, 1L, 0L, 0L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 
1L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
1L, 0L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
1L, 0L, 1L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 1L, 0L, 1L, 0L, 0L, 0L, 0L, 1L, 0L, 1L, 0L, 0L, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)), class = "data.frame", row.names = c(NA, 
-200L))
CreditProducts <- structure(list(Credit = structure(c(2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L), .Label = c("No", "Yes"), class = "factor")), row.names = c(NA, 
-200L), class = "data.frame")
```


Statstics and Simulation
========================================

The big idea is that we simulate things because we can.  In old school statistics, the limitations were imposed by the difficulty and need for obtaining analytical solutions.  We can use the computer and sampling to replace these arcane mathematical troubles.

Resampling a Proportion
=======================================================

This idea applies to proportions based on binary data [and next week, to means].  Take the example of CreditProducts.  Let me first show a table of the data and embed the function.

```{r, echo=FALSE}
resample.prop <- function(vec.data, k=1000, tab.col=1) {
 vec.data <- vec.data[complete.cases(vec.data)]
 prop.comp <- sapply(1:k, function(x) { prop.table(table(vec.data[sample(1:length(vec.data), size=length(vec.data), replace=TRUE)]))[[tab.col]]}) 
 prop.comp
}
table(CreditProducts$Credit)
```

The command `resample.prop` requires a vector of data with two outcomes of whatever form.  Yes and No, True and False, Up and Down, or 0 and 1, or even 0 and 10000.  As long as it is binary, the code will work.  It also has a key option, `tab.col` which embeds whether you want the first `1` or second `2` column of the table. Here, I will use 2 because I want the probability of *Yes* on credit products.

```{r}
Cred.Prod.Res <- resample.prop(CreditProducts$Credit, tab.col=2)
binom.test(144,200)
prop.test(144,200)
quantile(Cred.Prod.Res, c(0.025,0.975))
```

The probability distributions are all very similar.  They all attempt to capture the same idea.

Two Independent Sample Comparisons 
===========================================

Embed the same logic.  First, I want a random $\pi$ from sample 1.  Then I want a random $\pi$ from sample 2.  I want to measure the difference between these two random means.  Why measure them separately?  Because I do not know who matches with whom and, oftentimes, we have different size samples and we do not wish to discard relevant information from which to sample these means.  

Two Independent Proportions
===================================================

We have a proportions test to examine whether the probability of yes [in a binomial] is the same or different in two samples.  First, let me illustrate the workflow.

Now I take two samples of binary data and take a random sample of each, calculate the sample proportions, and subtract one from the other.  For this example, let me use data on Defaults.  0 is no default; 1 is a default.  I will again need the second column.  

```{r}
table(Defaults$Commercial)
table(Defaults$Consumer)
```

*****

The command is `resample.ind.prop` that requires two binary vectors as inputs.

```{r, echo=FALSE}
resample.ind.prop <- function(vec.1, vec.2, k=1000, tab.col=1) {
 vec.1 <- vec.1[complete.cases(vec.1)]
 vec.2 <- vec.2[complete.cases(vec.2)]
 diff.prop <- sapply(1:k, function(x) { prop.table(table(vec.1[sample(1:length(vec.1), size=length(vec.1), replace=TRUE)]))[[tab.col]]-prop.table(table(vec.2[sample(1:length(vec.2), size=length(vec.2), replace=TRUE)]))[[tab.col]]}) 
 diff.prop
 }
Defaults.Res.Diff <- resample.ind.prop(Defaults$Commercial,Defaults$Consumer, tab.col=2)
prop.test(x=c(31,19),n=c(200,105))
quantile(Defaults.Res.Diff, c(0.025,0.975))
```

My simulated interval is a bit tighter; the z is an approximation.

Why It Matters: Independence
===========================================================

We want to know if two groups are the same or different in terms of the underlying probability $\pi$ that describes the binomial.  Why?  If they are the same, then whatever it is that determines the two groups can be thought independent of $\pi$.  Knowing which group does not matter.

An Example: Berkeley
===========================================================
```{r}
data("UCBAdmissions")
mosaicplot(apply(UCBAdmissions, c(1, 2), sum),
           main = "Student admissions at UC Berkeley")
```

Or
=========================================================
```{r}
opar <- par(mfrow = c(2, 3), oma = c(0, 0, 2, 0))
for(i in 1:6)
  mosaicplot(UCBAdmissions[,,i],
    xlab = "Admit", ylab = "Sex",
    main = paste("Department", LETTERS[i]))
mtext(expression(bold("Student admissions at UC Berkeley")),
      outer = TRUE, cex = 1.5)
par(opar)
```

The Statistics
======================================================

Now to the statistics.  But first, $\chi^2$.  It's a probability distribution.  It is entirely defined by degrees of freedom.  And it is derived from a squared normal.  If I have to calculate two proportions, I consume two degrees of freedom; if only one proportion need be calculated[meaning they are the same] then only one.  The difference in degrees of freedom is one.  That's our $\chi^2$ parameter: df.

Let's Analyse This
====================================================

```{r, echo=FALSE}
UCB.Admit <- data.frame(stringsAsFactors=FALSE,
         M.F = c("Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Male", "Male", "Male",
                 "Male", "Male", "Male", "Male", "Male", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female", "Female", "Female", "Female", "Female",
                 "Female", "Female"),
       Admit = c("Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "No", "No", "No", "No", "No", "No",
                 "No", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
                 "Yes", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No", "No",
                 "No", "No", "No", "No", "No", "No", "No", "No", "No"),
        Dept = c("A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A",
                 "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B",
                 "B", "B", "B", "B", "B", "B", "B", "B", "B", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C",
                 "C", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D", "D",
                 "D", "D", "D", "D", "D", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E", "E",
                 "E", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
                 "F", "F", "F", "F", "F", "F", "F", "F", "F")
)
```

```{r}
table(UCB.Admit$M.F,UCB.Admit$Admit)
prop.table(table(UCB.Admit$M.F,UCB.Admit$Admit), 1)
# Tests work across the rows.
prop.test(table(UCB.Admit$M.F,UCB.Admit$Admit))
```

So Women are seen, with 95% confidence, to be rejected by Berkeley 0.113 to 0.170 more often, expressed in a difference in probability metric.  Moreover, the probability of Admission is not independent of Male and Female.

What About by Department?
===============================================

```{r}
UCBS.Admit = subset(UCB.Admit, subset=Dept=="A")
table(UCBS.Admit$M.F,UCBS.Admit$Admit)
prop.table(table(UCBS.Admit$M.F,UCBS.Admit$Admit), 1)
# Tests work across the rows.
prop.test(table(UCBS.Admit$M.F,UCBS.Admit$Admit))
```

```{r}
UCBS.Admit = subset(UCB.Admit, subset=Dept=="B")
table(UCBS.Admit$M.F,UCBS.Admit$Admit)
prop.table(table(UCBS.Admit$M.F,UCBS.Admit$Admit), 1)
# Tests work across the rows.
prop.test(table(UCBS.Admit$M.F,UCBS.Admit$Admit))
```

```{r}
UCBS.Admit = subset(UCB.Admit, subset=Dept=="C")
table(UCBS.Admit$M.F,UCBS.Admit$Admit)
prop.table(table(UCBS.Admit$M.F,UCBS.Admit$Admit), 1)
# Tests work across the rows.
prop.test(table(UCBS.Admit$M.F,UCBS.Admit$Admit))
```

```{r}
UCBS.Admit = subset(UCB.Admit, subset=Dept=="D")
table(UCBS.Admit$M.F,UCBS.Admit$Admit)
prop.table(table(UCBS.Admit$M.F,UCBS.Admit$Admit), 1)
# Tests work across the rows.
prop.test(table(UCBS.Admit$M.F,UCBS.Admit$Admit))
```

```{r}
UCBS.Admit = subset(UCB.Admit, subset=Dept=="E")
table(UCBS.Admit$M.F,UCBS.Admit$Admit)
prop.table(table(UCBS.Admit$M.F,UCBS.Admit$Admit), 1)
# Tests work across the rows.
prop.test(table(UCBS.Admit$M.F,UCBS.Admit$Admit))
```

```{r}
UCBS.Admit = subset(UCB.Admit, subset=Dept=="F")
table(UCBS.Admit$M.F,UCBS.Admit$Admit)
prop.table(table(UCBS.Admit$M.F,UCBS.Admit$Admit), 1)
# Tests work across the rows.
prop.test(table(UCBS.Admit$M.F,UCBS.Admit$Admit))
```

One Case Shows a Difference
========================================================

**And it goes in the wrong direction**

Women are less likely to be rejected in Dept A.  The rest suggest Admission is independent of M.F
