---
title: Visualizing One Qualitative Variable
author: Robert W. Walker
date: '2020-09-12'
slug: visualize-one-categorical
categories:
  - R
tags:
  - plot
subtitle: ''
summary: ''
authors: []
lastmod: '2020-09-12T20:04:06-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=TRUE)
library(tidyverse)
```

# Bonds

A dataset for illustrating the various available visualizations needs a certain degree of richness with manageable size.  The dataset on *Bonds* contains three categorical and a few quantitative indicators sufficient to show what we might wish.

## Loading the Data

```{r}
Bonds <- read.csv(url("https://raw.githubusercontent.com/robertwwalker/DADMStuff/master/BondFunds.csv"))
```

## A Summary

```{r}
library(skimr)
Bonds %>% 
  skim()
```

Most data types are represented.  There is no time variable so dates and the visualizations that go with time series are omitted.

# Data Visualization

First, let us look at visualizations for one variable.

## Bar plots and column plots

There are two ways to construct a barplot; we can let ggplot handle it on the raw data or calculate it ourselves.  Let me focus on *Risk*.


## `geom_bar()`

```{r}
Bonds %>% 
  ggplot() + 
  aes(x=Risk) + 
  geom_bar()
```

### Raw Data Bar Plot [color]

```{r}
Bonds %>% 
  ggplot() + 
  aes(x=Risk, color=Risk) + 
  geom_bar()
```


### Raw Data Bar Plot [color and fill]

We could color it.

```{r}
Bonds %>% 
  ggplot() + 
  aes(x=Risk, color=Risk) + 
  geom_bar(fill="white") + 
  guides(color=FALSE)
```

### Raw Data Bar Plot [Fill]

We can fill the shapes.

```{r}
# guides(fill=FALSE) removes the legend
Bonds %>% 
  ggplot(., aes(x=Risk, fill=Risk)) + 
  geom_bar() + 
  guides(fill=FALSE)
```

## `geom_bar()` meets `fill`

We can also deploy `fill` but x is no longer the axis; the axis is some constant value with frequencies filled by the fill.  *This will require some prettying.*

### A Cumulative Bar Plot

```{r}
Basic.Bar <- Bonds %>% 
  ggplot(., aes(x="", fill=Risk)) +
  geom_bar()
Basic.Bar
```

The prettying will require that I eliminate the x axis [set it to empty], include a theme, and give it proper labels.

### Enhanced Cumulative Bar Plot

```{r}
Bonds %>% ggplot(., aes(x="", fill=Risk)) +
  geom_bar() + 
  labs(x="", y="Number of Funds") +
  theme_minimal() + 
  theme(axis.text.x= element_blank())
```

### Proportion Bar Plot

```{r}
Bonds %>% 
  ggplot(., aes(x="", fill=Risk)) +
  geom_bar(position="fill") +
  labs(x="", y="Proportion of Funds")
```

The prettying will require that I eliminate the x axis [set it to empty], include a theme, and give it proper labels.

### Enhanced Proportion Bar Plot

```{r}
Bonds %>% ggplot(., aes(x="", fill=Risk)) +
  geom_bar(position="fill") + 
  labs(x="", y="Propotion of Funds") +
  theme_minimal()
```

## geom_col()

```{r}
Risk.Table <- table(Bonds$Risk) %>% data.frame()
Risk.Table %>% 
  ggplot(., aes(x=Var1, y=Freq)) + 
  geom_col()
```

### Beautifying `geom_col()`

Now it really needs some beautification.

```{r}
Risk.Table %>% 
  ggplot(., aes(x=Var1, y=Freq, fill=Var1)) + 
  geom_col() + 
  labs(x="Risk Levels", y="Number of Funds") + 
  theme_minimal() + 
  theme(axis.text.x= element_blank()) + 
  scale_fill_viridis_d() + 
  guides(fill=FALSE)
```

## `position = "fill"`

The two commands are symmetric in the sense that x as axis always splits it into multiple parts.  `fill` will prove very useful with a two dimensional table.

```{r}
Risk.Table %>% 
  ggplot(., aes(x=1, y=Freq, fill=Var1)) +
  geom_col(position = "fill") + 
  labs(x="Risk Levels", y="Number of Funds") +
  theme_minimal() + 
  theme(axis.text.x= element_blank()) +
  scale_fill_viridis_d() + 
  guides(fill=FALSE)
```

## A lollipop chart

A lollipop chart is a combination of two geometries.  It is a basic scatterplot combining one qualitative variable and the quantitative count of the number of observations.  The head of the lollipop is a point while there is an accompanying line segment from (x,0) to (x,Freq) where Freq is the default name for a count from a table.

### Basic Lollipop Chart

```{r}
Risk.Table %>% 
  ggplot(., aes(x=Var1, y=Freq, color=Var1)) + 
  geom_point(size=6) + 
  labs(x="Risk Level", y="Number of Funds", color="Risk Level")+ 
  geom_segment(aes(xend=Var1, y=0, yend=Freq)) +
  theme_minimal()
```

### Slicked Lollipop Chart by Adjusting Segment Size

```{r}
Risk.Table %>% 
  ggplot(., aes(x=Var1, y=Freq, color=Var1)) + 
  geom_point(size=6) + 
  labs(x="Risk Levels", y="Number of Funds")+ 
  geom_segment(aes(xend=Var1, y=0, yend=Freq), size=1.5) +
  theme_minimal()  + 
  guides(color=FALSE)
```



```{r}
Risk.Table %>% 
  ggplot(., aes(x=Var1, y=Freq, color=Var1)) + 
  geom_point(size=6) + 
  labs(x="Risk Levels", y="Number of Funds")+ 
  geom_segment(aes(xend=Var1, y=0, yend=Freq)) + 
  theme_minimal()  + 
  scale_color_viridis_d() + 
  guides(color=FALSE) + 
  coord_flip()
```

### A Lollipop Table [geom_label()]

Now I will switch up the points to be the actual values as text.  For this, I use the `geom_text` aesthetic that requires a `label` to be assigned.  I also want to put down the lines before the text to avoid overlap.

```{r}
Risk.Table %>% 
  ggplot(., aes(x=Var1, y=Freq, color=Var1, label=Freq)) +
  labs(x="Risk Levels", y="Number of Funds")+ 
  geom_segment(aes(xend=Var1, y=0, yend=Freq)) + 
  geom_label(size=6) + 
  theme_minimal()  + 
  scale_color_viridis_d() + 
  guides(color=FALSE) + 
  coord_flip()
```


### A Lollipop Table [geom_text() inverse]

The ggplot is built in layers so the segment before the label makes sure that the white shows up.  The fill and a discrete color are combined to create this graphical table.

```{r}
Risk.Table %>% 
  ggplot(., aes(x=Var1, y=Freq, color=Var1, fill=Var1, label=Freq)) +
  geom_segment(aes(xend=Var1, y=0, yend=Freq), size=1.5) +
  geom_label(size=6, color="white") + 
  labs(x="Risk Levels", y="Number of Funds")+ 
  theme_minimal()  + 
  scale_color_viridis_d() + 
  scale_fill_viridis_d() + 
  guides(fill=FALSE, color=FALSE) + 
  coord_flip()
```

## I HATE PIE CHARTS

A pie chart is fairly easy to do.  Let's go back and show something that I find pretty amazing.  A pie chart is a bar chart [the fill variety] with coordinates that fill a circle rather than a square.  We take the most basic bar plot -- Basic.Bar -- and add three things: new coordinates that are polar, labels, and a blank theme to eliminate axis labels.

```{r}
Basic.Bar + coord_polar("y", start=0) + labs(x="", y="") + theme_void()
```
