---
title: Socrata is amazingly handy for open data
author: RWW
date: '2020-11-25'
slug: socrata-is-amazingly-handy-for-open-data
categories:
  - R
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-11-25T13:16:28-08:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RSocrata)
SchoolSpend <- read.socrata("https://data.oregon.gov/resource/c7av-ntdz.csv")
options(scipen=7)
library(tidyverse)
```

The Socrata package makes it easy to access API calls built around SODA for open data access.  If you try to skip the Socrata part, you usually only get a fraction of the available data.

```
install.packages("RSocrata")
library(RSocrata)
SchoolSpend <- read.socrata("https://data.oregon.gov/resource/c7av-ntdz.csv")
```

The first bit of data that I found details various bits about spending and students in Oregon school districts.  I want to look at a few basics of this.  There is a lot more to plot but this is enough for now.

## The Data

I found this on Oregon's open data portal.  What do I have?

```{r}
library(skimr)
skim(SchoolSpend)
```
## How many school districts per county?

```{r}
library(magrittr); library(hrbrthemes)
SchoolSpend %>% group_by(county_name, school_year) %>% tally() %>% mutate(school_year = as.Date(school_year, format = "%m/%d/%Y")) %>% filter(school_year == max(school_year)) %>% ggplot() + aes(x=fct_reorder(county_name, n), y=n, fill=county_name) + geom_col() + coord_flip() + guides(fill=FALSE) + labs(x= "County", y="Number of School Districts") + theme_minimal()
```

## By Students?

```{r}
SchoolSpend %>% group_by(county_name) %>% mutate(school_year = as.Date(school_year, format = "%m/%d/%Y")) %>% filter(school_year == max(school_year)) %>% summarise(Students = sum(student_count), Year = mean(school_year), County = as.factor(county_name)) %>% unique() -> Dat
ggplot(Dat) + aes(x=fct_reorder(County, -Students), y=Students, fill=county_name) + geom_col() + coord_flip() + guides(fill=FALSE) + labs(x= "County", y="Students") + theme_minimal()
```

There are a number of other bits of data organized by year and district.  There is certainly more to examine, but then I found this.

# Voter Registration Data

The database of Voter Registrations in Oregon is also available and easily accessible.

```{r}
VoterReg <- read.socrata("https://data.oregon.gov/resource/6a4f-ecbi.csv")
VoterReg %>% filter(sysdate == "2020-11-03") %>% group_by(county) %>% summarise(Voters = sum(count_v_id)) %>% ggplot(., aes(x=fct_reorder(county, Voters), y=Voters, label=Voters)) + geom_col(fill="white", color="skyblue") + geom_text(size=2.2) + coord_flip() + labs(x="County", y="Registered Voters") + theme_minimal() -> Plot1
Plot1
```

```{r Plotly1, message=FALSE, warning=FALSE}
library(plotly); library(widgetframe)
ggp1 <- ggplotly(Plot1)
frameWidget(ggp1)
```


## The Balance of Registrations

```{r}
CurrVR <- VoterReg %>% filter(sysdate == "2020-11-03")
CurrVR$DRE <- "Other"
CurrVR$DRE[CurrVR$party=="Democrat"] <- "Democrat"
CurrVR$DRE[CurrVR$party=="Republican"] <- "Republican"
CurrVR %>% group_by(county) %>% mutate(Voters = sum(count_v_id)) %>% ggplot(., aes(x=fct_reorder(county, Voters), y=Voters, label=Voters)) + geom_col() + geom_text(size=2.2) + coord_flip() + labs(x="County", y="Registered Voters") + theme_minimal()
```

## The Plot by Party

Now let me split these up by grouping and plot them.

```{r}
CurrVR %>% group_by(county, DRE) %>% summarise(Voters = sum(count_v_id)) %>%
ggplot(.) +
 aes(x = fct_reorder(county, Voters), y=Voters, fill = DRE) +
 geom_col() + scale_fill_viridis_d() +
 coord_flip() +
 theme_minimal() + labs(x="County")
```
