---
title: "Patchwork"
author: "Robert W. Walker"
date: "9/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Patchwork

`Patchwork` is a really neat R package that allows us to combine graphics in a fairly intuitive and `ggplot`-friendly fashion.  Adding rows happens with `+` and dividing columns of plots works with `/`.  It also respects orders of operations with parentheses.  Let me use the Berkeley data to demonstrate a bit of this.  I will make use of three packages that you may or may not have.

```
install.packages(c("patchwork","janitor","DescTools"), dependencies=TRUE)
```

As a note, you can make use of a library::function approach as well as loading libraries to directly reference commands.  So `janitor::tabyl` references the tabyl function in the janitor package.

```{r}
library(patchwork)
# A first plot of the count by department.
UCBAdmissions %>% DescTools::Untable() %>% janitor::tabyl(Dept) %>% ggplot() + aes(x=Dept, y=n) + geom_col() + theme_minimal() -> Plot1
# A second plot of the proportion by department.  Though it is called a percent, it is not.
UCBAdmissions %>% DescTools::Untable() %>% janitor::tabyl(Dept) %>% ggplot() + aes(x=Dept, y=percent*100) + geom_col() + theme_minimal() + labs(y="Percent") -> Plot2
# A first patchwork
Plot1 + Plot2
```

Using the `/` to put them on top of one another.

```{r}
Plot1 / Plot2
```

Now to put the gender data together.

## Gender

```{r}
# A first plot of the count by gender.
UCBAdmissions %>% DescTools::Untable() %>% janitor::tabyl(Gender) %>% ggplot() + aes(x=Gender, y=n) + geom_col() + theme_minimal() -> Plot1A
# A second plot of the proportion by gender.
UCBAdmissions %>% DescTools::Untable() %>% janitor::tabyl(Gender) %>% ggplot() + aes(x=Gender, y=percent*100) + geom_col() + theme_minimal() + labs(y="Percent") -> Plot2A
Plot1 + Plot2 / Plot2 + Plot2A
```

That's not really what I wanted.  The parentheses separate it into parts.

```{r}
Plot1 + Plot2 / (Plot1A + Plot2A)
```

It wants a complete statement that fully respects the order of operations.  So put the top together in parentheses and the bottom, as well.

```{r}
(Plot1 + Plot2) / (Plot1A + Plot2A)
```
