---
title: "Natural Gas dashboard"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true            
    theme: yeti
---

```{r setup, include = FALSE}
library(ggplot2); library(ggthemes)
library(dplyr)
knitr::opts_chunk$set(fig.asp = 1/3) # It is a 2 column with 3 graphics and one table; the table is rendered for scrolling using DT::datatable()
load(url("https://github.com/robertwwalker/DADMStuff/raw/master/NaturalGas2019.RData"))
library(plotly)
library(radiant)
```


### Question 1

```{r}
result <- prob_lnorm(meanlog = 0, sdlog = 1, lb = 0, ub = 1)
summary(result)
plot(result)
```   

***

What is the probability that a log-normal random variable [in R, lnorm is the noun] whose logarithm has mean equal to 0 and standard deviation equal to 1, takes values less than 1?  

**0.5**

### Question 2

```{r}
result <- prob_lnorm(meanlog = 0, sdlog = 1, plb = 0, pub = 0.95)
summary(result, type = "probs")
plot(result, type = "probs")
```   


***

What is the value of a log-normal random variable [in R, lnorm is the noun] whose logarithm has mean equal to 0 and standard deviation equal to 1, such that 0.95 of the probability is below said value?

**5.18**
 
### Question 3
    
```{r}
data.frame(x=rlnorm(10000)) %>% ggplot(., aes(x=x)) + geom_density() + labs(x="Lognormal(0,1)")
```

***

Plot a random sample of 1000 random draws from the aforementioned lognormal distribution (mean 0 and std. dev. 1).  

**The purpose is to have you visualize the distribution as a sanity check for 1 and 2.**

### Question 4

```{r}
result <- prob_norm(
  mean = 0, 
  stdev = 1, 
  plb = 0.15865, 
  pub = 0.84135
)
summary(result, type = "probs")
plot(result, type = "probs")
```


***

The central probability in a standard normal distribution between -1 and 1 is 0.6827.

Figure out z such that the probability between XXX and XXX is 0.6827.  The middle of a z (normal 0, 1) is 0 so the probability below 0 is the same as the probability above zero which is 0.5.  Now we need 0.6827 to each side.  First, split it into two parts.  There will be 0.6827/2 on each side of zero.  So the first value must then be the solution to 0.5 - 0.34135 or 0.15865: **-1**.  The second value will be 0.5 + 0.34135 or 0.84135: **1**.



### Newspapers

```{r}
ggplot(Newspapers, aes(x=Price, fill=Location)) + geom_density(alpha=0.2) + scale_fill_viridis_d()
```


*** 

Two key features are of note:  

1. The average price is clearly lower at Henry Hub  
2. The amount of variation at Henry Hub is considerably larger than at Tianjin in spite of the fact that the average is lower.


### Newspapers: Summary

```{r}
skimr::skim(Newspapers)
```

*** 

Two key features are of note:  

1. The average price is clearly lower at Henry Hub  
2. The amount of variation at Henry Hub is considerably larger than at Tianjin in spite of the fact that the average is lower.



### Experts

```{r}
ggplot(Experts, aes(x=Location, fill=Build)) + geom_bar() + expand_limits(y=100) + scale_fill_viridis_d()
```

*** 

Almost everything that we wish to know can be discerned from this.  

1. Because we can see 100 on the y-axis, we can get a sense of the missing responses; there are far more for Tianjin than Henry Hub.  
2. Experts clearly favor Henry Hub; the split in Build/No is nearly even for Tianjin but overwhelmingly favors Build for Henry Hub.

### Experts: Tables


The Raw Table

<center>
```{r}
Experts %>% janitor::tabyl(Location,Build) %>% janitor::adorn_totals(c("row","col"))
```
</center>

A Percentage Table

<center>
```{r}
Experts %>% janitor::tabyl(Location,Build) %>% janitor::adorn_percentages()
```
</center>

*** 

1. Henry Hub has far more responses and more favorable responses than Tianjin.
2. Experts clearly favor Henry Hub; the split in Build/No is nearly even for Tianjin but overwhelmingly favors Build for Henry Hub.


### Forecast

```{r}
options(scipen=10)
ggplotly(ggplot(Forecast, aes(x=Period, y=Forecast, color=Location)) + geom_line() + geom_point() + scale_color_viridis_d())
```

*** 

Two things are of note:  
1. The data are paired by period; that is the point of the calibration exercise.  
2. *Henry Hub* is almost always forecast higher than Tianjin.  Choose a period and you can hover over the associated values to convince yourself of this.  Compare the two forecasts for any given period; they are almost always higher for Henry Hub.  


### Forecast: Data

```{r}
Forecast %>% mutate(Difference = HenryHubForecast - TianjinForecast) %>% select(Period, HenryHubForecast, TianjinForecast, Difference) %>% tidyr::drop_na(Difference) %>% DT::datatable(.)
```


*** 

*Henry Hub* is almost always forecast higher than Tianjin.  The difference column captures this perfectly and shows that it always favors Henry Hub.
