---
title: "Sliding Windows with Slider"
author: "RWW"
date: "2021-04-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, fig.retina = 2)
```

## Data

I will use the data from the New York Times on COVID.  I want to illustrate the use of `slider` for the creation of moving averages on `tsibble` structures.  To render some context for the data, let me import it, transform it a bit to make it more sensible [removing negative values], and turn it into a `tsibble`.

```{r}
library(tidyverse); library(fpp3); library(hrbrthemes)
NYT.COVIDN <- read.csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv"))
# Define a tsibble; the date is imported as character so mutate that first.
NYT.COVID <- NYT.COVIDN %>% 
  mutate(date=as.Date(date)) %>% 
  as_tsibble(index=date, key=state) %>% 
  group_by(state) %>% 
  mutate(New.Cases = difference(cases), New.Deaths = difference(deaths)) %>% 
  filter(!(state %in% c("Guam","Puerto Rico", "Virgin Islands","Northern Mariana Islands")))
NYT.COVID <- NYT.COVID %>% 
  mutate(
    New.Cases = (New.Cases >= 0)*New.Cases, 
    New.Deaths = (New.Deaths >= 0)*New.Deaths,
    cases = cases,
    deaths = deaths)
NYTAgg.COVID <- NYT.COVID %>% 
  aggregate_key(state, 
                cases = sum(cases, na.rm=TRUE),
                deaths = sum(deaths, na.rm=TRUE), 
                New.Cases = sum(New.Cases, na.rm=TRUE),
                New.Deaths = sum(New.Deaths, na.rm=TRUE)) %>% 
  filter(date > as.Date("2020-03-31")) %>% 
  mutate(Day.of.Week = as.factor(wday(date, label = TRUE)))
```

The `aggregate_key` generates national sums as a result of each individual unit.  This can be very handy in bottom up forecasting.  I will focus on the aggregates.

# Forecasting the US

I want to focus on the US data.

## A Basic Plot

Let me start with a plot of `New.Cases`.

```{r}
library(hrbrthemes)
options(scipen=6)
NYTAgg.COVID %>% filter(is_aggregated(state)) %>% autoplot(New.Cases) + theme_ipsum_rc() + labs(title="New COVID-19 Cases in the US")
```

## Some Summary Information

```{r}
NYTAgg.COVID %>% filter(is_aggregated(state)) %>% features(New.Cases, list(mean, sd, quantile))
```

```{r}
NYTAgg.COVID %>% filter(is_aggregated(state)) %>% features(New.Deaths, list(mean, sd, quantile))
```

## STL Characteristics

```{r}
NYTAgg.COVID %>% filter(is_aggregated(state)) %>% features(New.Deaths, feat_stl)
```

```{r}
NYTAgg.COVID %>% filter(is_aggregated(state)) %>% model(STL(New.Cases)) %>% components() %>% autoplot()
```



## Moving Averages using `slider::`

The `slider` packages makes this very straightforward.  The `mutate` line contains all the action.  If I want the moving average (mean) of 3 .before, 3 .after, and the current datum with a complete set, the following code defining `7-MA` will suffice.  `7-TA` defines a mean from the current and six prior observations.

```{r}
NYTAG <- NYTAgg.COVID %>% 
  filter(is_aggregated(state)) %>%
  mutate(`7-MA` = slider::slide_dbl(New.Cases, mean, .before=3, .after=3, .complete=TRUE)) %>% 
  mutate(`7-TA` = slider::slide_dbl(New.Cases, mean, .before=6, .after=0, .complete=TRUE))
NYTAG %>%
  autoplot(`7-MA`, color="red", alpha=0.2) + 
  autolayer(NYTAG %>% select(`7-TA`), color="blue", alpha=0.2) +
  autolayer(NYTAgg.COVID %>% 
              filter(is_aggregated(state)) %>% 
              select(New.Cases), alpha=0.2) + 
  labs(y="New COVID-19 Cases", title="New COVID-19 Cases in the US", subtitle="7 day moving average in red") + theme_ipsum_rc()
```

## Deaths: Moving Averages using `slider::`

Now I want a 14 day trailing average.  That's 13 before and 0 after.  What do new COVID-19 deaths in the US look like when measured in that way?

```{r D14TA}
NYTAgg.COVID %>% 
  filter(is_aggregated(state)) %>%
  mutate(`14-TA` = slider::slide_dbl(New.Deaths, mean, .before=13, .after=0, .complete=TRUE)) %>% 
  autoplot(`14-TA`, color="red") + 
  autolayer(NYTAgg.COVID %>% 
              filter(is_aggregated(state)) %>% 
              select(New.Deaths), alpha=0.2) + 
  labs(y="New COVID-19 Deaths", title="New COVID-19 Deaths in the US", subtitle="14 day trailing average in red") + theme_ipsum_rc()
```
# A Better Plot

My personal favorite plot.

```{r}
NYTAG %>% 
  autoplot(`7-TA`, color="blue") + 
  geom_point(aes(x=date, y=New.Cases), alpha=0.2, color="red") + labs(title="New COVID-19 Cases in the US", subtitle="7 Day trailing average in blue", y="New COVID-19 Cases")
```

