---
title: "A Look at VIX :`r Sys.time()`"
author: Robert W. Walker
date: '2020-02-27'
slug: a-look-at-vix
categories:
  - R
  - tidyquant
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: "`r Sys.time()`"
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

# Get Some VIX data

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
VIX <- read.csv(url("http://www.cboe.com/publish/scheduledtask/mktdata/datahouse/vixcurrent.csv"), skip = 1)
VIX$Dates <- as.Date(VIX$Date,
  format = "%m/%d/%Y")
```

The data was straightforward to get a hold of.  Now let me plot it.

```{r, message=FALSE, warning=FALSE}
library(plotly)
fig <- VIX  %>% plot_ly(x = ~Dates, type="candlestick",
          open = ~VIX.Open, close = ~VIX.Close,
          high = ~VIX.High, low = ~VIX.Low) 
fig <- fig %>% layout(title = "A Historical Look at VIX")
library(widgetframe)
frameWidget(fig, width = 1000)
```

As an overall it has been worse, but keep in mind, that big blip happened TODAY!  What does it look like in perspective [keeping in mind that the futures are currently just under 40] since 2012?

```{r}
fig2 <- VIX %>% filter(Dates > as.Date("01/01/2012", format = "%m/%d/%Y")) %>% plot_ly(x = ~Dates, type="candlestick",
          open = ~VIX.Open, close = ~VIX.Close,
          high = ~VIX.High, low = ~VIX.Low) 
fig2 <- fig2 %>% layout(title = "VIX Since 2012")
frameWidget(fig2, width = 1000)
```

## Day to Day Changes?

I originally wrote this on February 27, 2020.  I will touch the file about daily to track the evolution.

```{r, warning=FALSE}
VIX <- VIX %>% mutate(Percent.Change = (VIX.Close - lag(VIX.Close)) / lag(VIX.Close)) 
p <- ggplot(VIX, aes(x=Dates, y=Percent.Change)) + geom_line() + geom_smooth(color="orange", method="loess", span=0.05, se=FALSE) + geom_vline(xintercept = as.Date("02/27/2020", format = "%m/%d/%Y"), color="red", alpha=0.2, linetype = "dotted") + geom_vline(xintercept = as.Date("09/12/2008", format = "%m/%d/%Y"), color="red", alpha=0.4) + ggthemes::theme_economist() + geom_label(data = data.frame(x = as.Date("2008-02-12"),
y = 0.75,
label = "Lehman Brothers"),
mapping = aes(x = x,
y = y,
label = label),
size = 3.86605783866058,
angle = 0L,
lineheight = 1L,
hjust = 0.5,
vjust = 0.5,
colour = "red",
family = "sans",
fontface = "plain",
label.padding = structure(0.25,
class = "unit",
valid.unit = 3L,
unit = "lines"),
label.size = 0.25,
label.r = structure(0.15,
class = "unit",
valid.unit = 3L,
unit = "lines"),
inherit.aes = FALSE,
show.legend = FALSE)
fig <- ggplotly(p)
frameWidget(fig, width = 1000)
```




This doesn't look good.  The smooth on a small span is uncomfortably headed upward and today will shock it like no previous day in a very long while.
