---
title: "A Look at VIX :`r Sys.time()`"
author: Robert W. Walker
date: '2020-02-27'
slug: a-look-at-vix
categories:
  - R
  - tidyquant
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: "`r Sys.time()`"
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

# Get Some VIX data

**NB:  I originally wrote this on February 27, 2020 so there is commentary surrounding that date.  It was done on the quick for curiosity.**

Chicago Board Of Exchange (CBOE) makes data available regularly. To judge the currency of the data, I have tailed it below after converting the dates to a valid date format.  

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
VIX <- read.csv(url("http://www.cboe.com/publish/scheduledtask/mktdata/datahouse/vixcurrent.csv"), skip = 1)
VIX$Dates <- as.Date(VIX$Date,
  format = "%m/%d/%Y")
tail(VIX)
```

The data was straightforward to get a hold of.  Now let me plot it.  I want to do this with a candlestick plot -- a way of displaying intra-day volatility.  There's so much data that the views aren't great.

```{r, message=FALSE, warning=FALSE}
library(plotly)
fig <- VIX  %>% plot_ly(x = ~Dates, type="candlestick",
          open = ~VIX.Open, close = ~VIX.Close,
          high = ~VIX.High, low = ~VIX.Low) 
fig <- fig %>% layout(title = "A Historical Look at VIX")
library(widgetframe)
frameWidget(fig, width = 1000)
```

As an overall it has been worse, but keep in mind, that big blip happened TODAY!  What does it look like in perspective [keeping in mind that the futures are currently just under 40] since 2012?

```{r}
fig2 <- VIX %>% filter(Dates > as.Date("01/01/2012", format = "%m/%d/%Y")) %>% plot_ly(x = ~Dates, type="candlestick",
          open = ~VIX.Open, close = ~VIX.Close,
          high = ~VIX.High, low = ~VIX.Low) 
fig2 <- fig2 %>% layout(title = "VIX Since 2012")
frameWidget(fig2, width = 1000)
```

## Day to Day Changes?

I will touch the file about daily to track the evolution.

```{r, warning=FALSE, message=FALSE}
library(hrbrthemes); library(viridis)
VIX <- VIX %>% mutate(Percent.Change = (VIX.Close - lag(VIX.Close)) / lag(VIX.Close)) 
p <- ggplot(VIX, aes(x=Dates, y=Percent.Change, size=Percent.Change/10, color=Percent.Change)) + 
  geom_point(alpha=0.5, shape=21, inherit.aes = TRUE) +
  scale_size_continuous(range=c(0.05,2), guide=FALSE) +
  geom_line() + 
  geom_smooth(color="orange", method="loess", span=0.05, se=FALSE) + 
  geom_vline(xintercept = as.Date("02/27/2020", format = "%m/%d/%Y"), color="red", alpha=0.2, linetype = "dotted") + 
  geom_vline(xintercept = as.Date("09/12/2008", format = "%m/%d/%Y"), color="red", alpha=0.4) +
  geom_label(data = data.frame(x = as.Date("2008-02-12"),
    y = 0.75, label = "Lehman Brothers"),mapping = aes(x = x, y = y, label = label), size = 3.86605783866058, angle = 0L, lineheight = 1L, hjust = 0.5, vjust = 0.5, colour = "red", family = "sans", fontface = "plain", label.padding = structure(0.25, class = "unit", valid.unit = 3L, unit = "lines"), label.size = 0.25, label.r = structure(0.15, class = "unit", valid.unit = 3L, unit = "lines"), inherit.aes = FALSE, show.legend = FALSE) + 
  scale_color_viridis_c(guide=FALSE) +
  scale_fill_viridis_c(guide=FALSE) +
    theme_ipsum()
fig <- ggplotly(p)
frameWidget(fig, width = 1000)

```




This doesn't look good.  The smooth on a small span is uncomfortably headed upward and today will shock it like no previous day in a very long while.
