---
title: Stocks and gganimate
author: RWW
date: '2019-03-17'
slug: stocks-and-gganimate
categories:
  - R
  - tidyverse
tags:
  - plot
header:
  caption: ''
  image: ''
  preview: yes
---

## tidyquant

Automates a lot of equity research and calculation using *tidy* concepts.  Here, I will first use it to get the components of the S and P 500 and pick out those with weights over 1.25 percent.  In the next step, I download the data and finally calculate daily returns and a cumulative wealth index.

```{r cars, message=FALSE}
library(tidyquant)
library(tidyverse)
tq_index("SP500") %>% filter(weight > 0.0125) %>% select(symbol,company) -> Tickers
Tickers <- Tickers %>% filter(symbol!="BRK.B") %>% filter(symbol!="GOOGL")
Eq.P <- Tickers %>%  tq_get(., from="2018/01/01", to="2019/03/14") 
Returns <- Eq.P %>% group_by(symbol) %>% tq_transmute(., adjusted, periodReturn, period="daily")
C.Returns <- Eq.P %>% 
  group_by(symbol) %>% 
  tq_transmute(., adjusted, periodReturn, period="daily", type = "log", col_rename = "returns") %>% 
  mutate(wealth.index = 100 * cumprod(1 + returns))
library(skimr)
Returns %>% skim()
```

## Animating a plot

The goal of this was to play with `gganimate`.  I will take the big components and go through and plot them.  It is a big animation because it involves over a year of data.  The basic idea for the graphic was borrowed from a gganimate [sample](https://github.com/thomasp85/gganimate/wiki/Temperature-time-series).

```{r AnimPlot}
library(gganimate)
library(ggrepel)
p <- ggplot(C.Returns, aes(date, wealth.index, group = symbol, colour=symbol)) + 
  geom_point(size = 2) + 
  geom_line() + 
  geom_segment(aes(xend = as.Date("2019-03-15"), yend = wealth.index), linetype = 2) + 
    geom_text_repel(aes(y = wealth.index, x = as.Date("2019-03-15"), label = symbol), hjust = 1, nudge_x = 8) +
  transition_reveal(date) + 
  coord_cartesian(clip = 'off') + 
  labs(title = 'Cumulative Wealth Index for S&P Top 10', subtitle="Begins January 1, 2018: Base 100", y = 'Cumulative Change', x = 'Date') +
  theme_minimal() + theme(legend.position = "none")
animate(p, nframes=300)
```
