---
title: Visualizing Two Qualitative Variables
author: Robert W. Walker
date: '2020-09-13'
slug: visualize-two-qualities
categories:
  - R
tags:
  - plot
subtitle: ''
summary: ''
authors: []
lastmod: '2020-09-13T20:04:06-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=TRUE)
library(tidyverse)
```

# Bonds

A dataset for illustrating the various available visualizations needs a certain degree of richness with manageable size.  The dataset on *Bonds* contains three categorical and a few quantitative indicators sufficient to show what we might wish.

## Loading the Data

```{r}
Bonds <- read.csv(url("https://raw.githubusercontent.com/robertwwalker/DADMStuff/master/BondFunds.csv"))
```

## A Summary

```{r}
library(skimr)
Bonds %>% 
  skim()
```

Most data types are represented.  There is no time variable so dates and the visualizations that go with time series are omitted.

# Data Visualization

There are three primary visualizations that we might use for a combination of two qualities.  We will have a look at `geom_tile()`, `geom_point()`, and `geom_bar(aes(fill=))` to visualize these.  We can also make use of `facet`.  Let me work with Risk and Fees.  I will first display the relevant table.

## Building a Table

```{r}
BTDF <- Bonds %>% group_by(Risk,Fees) %>% summarise(Count = n()) %>% data.frame()
BTDF %>% pivot_wider(names_from=Fees, values_from=Count)
```
The table as a data.frame.

```{r}
BTDF
```

## `geom_tile`

```{r}
BTDF %>% 
  ggplot(., aes(x=Risk, y=Fees, fill=Count)) + 
  geom_tile() +
  scale_fill_viridis_c() + 
  theme_minimal() + labs(fill="Number of Funds")
```

## `geom_label` a visual table

```{r}
BTDF %>% 
  ggplot(., aes(x=Risk, y=Fees, label=Count)) + geom_label() + theme_minimal() + labs(subtitle="Counts of Funds Shown")
```

### A Tile Table

```{r}
BTDF %>% 
  ggplot(., aes(x=Risk, y=Fees, label=Count, fill=Count)) +   geom_tile(alpha=0.2) +
  scale_fill_viridis_c() + geom_text() + theme_minimal() + labs(subtitle="Counts of Funds Shown")
```



# Raw Data Plots

## `geom_count()`

```{r}
Bonds %>% ggplot() + aes(x=Risk, y=Fees) + geom_count() + theme_minimal()
```


# `geom_bar(fill=)`

Now let us look at the bar plot.  First, start with Risk.

```{r}
Bonds %>% 
  ggplot() + 
  aes(x=Risk) + 
  geom_bar()
```

To add Fees to the plot, we can fill the bars.

```{r}
Bonds %>% 
  ggplot() + 
  aes(x=Risk, fill=Fees) + 
  geom_bar()
```


## Conditional Probability: `(position="fill")`

We can also plot this normalized by the number in each category of x so that the plots represent conditional probability.

```{r}
Bonds %>% 
  ggplot() + 
  aes(x=Risk, fill=Fees) + 
  geom_bar(position="fill")
```

