---
title: 'A Fast Food Solution'
author: 'Robert W. Walker'
date: '2020-01-21'
header:
  caption: ''
  image: ''
  preview: yes
---



# Fast Food Data

These data came care of a Tidy Tuesday a while ago.  The data consist of Fast Food menu items for a selection of fast food chains.  The units are menu items.  We have the chain [restaurant], item [the item name], and a series of variables (columns) representing sodium, cholesterol, fat, calories, and other information.  Some is missing.  The data can be imported from the `tidytuesday` website on github as .csv.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(tidyverse); library(skimr)
```

```{r LoadData}
FFood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

## Basic Summary

A basic summary of the data.

```{r pressure, echo=FALSE, message=FALSE}
library(skimr)
skim(FFood)
```

## A Cautionary Note

The NA....

## For Next Time

1. In Excel, construct a pivot table of the data by fast food en
terprise that displays five key quantities: the count of the number of menu i
tems, the mean and sample standard deviation of calories, and the mean and sample standard deviation of sodium.
2. Which chain has the highest average calories?  **Mcdonalds**
3. Which chain has the lower average calories?  **Chick Fil-A**
4. Which chain has the highest average sodium content?  **Arbys**

** The pivot table is the first sheet in the Excel file.**

To answer them in R:

```{r}
FFood %>% group_by(restaurant) %>% skim(calories,sodium)
```


5. In R, construct the same pivot table equivalent using the tidyverse,the piping operator, and the skim function from the skim library

```{r}
FFood %>% group_by(restaurant) %>% summarise(Median.Calories = median(calories)) %>% arrange(Median.Calories)
```


6. Which chain has the highest median calories? **Sonic**
7. Which chain has the lowest median calories? **Chick Fil-A**

```{r}
FFood %>% group_by(restaurant) %>% summarise(Median.Sodium = median(sodium))
```

8. Which chain has the highest median sodium? **Arbys**

```{r}
FFood %>% group_by(restaurant) %>% summarise(Q3.Calories = quantile(calories, 0.75))
```


9. Which chain has the lowest 3rd quartile of calories? **Chick Fil-A**

```{r}
FFood %>% group_by(restaurant) %>% summarise(Q3.Protein = quantile(protein, 0.75, na.rm = TRUE))
```


10. Which chain has the highest 3rd quartile of protein? **Taco Bell**
11. In R, provide two graphics -- a boxplot and something resembling a density plot or histogram -- that shows the distributions of sodium and cholesterol.

```{r}
boxplot(FFood$sodium)
```

```{r}
hist(FFood$sodium)
```

```{r}
boxplot(FFood$cholesterol)
```

```{r}
hist(FFood$cholesterol)
```



12. In R, provide two graphics -- a boxplot and something resembling a density plot -- that compares the distributions of total fat and cholesterol by chain. ** I will use an R package called `patchwork` to create multipane graphics with add (+).

```
install.packages("patchwork")
```

The structure of each graphic is identical with only the `y` changing or the `geom` changing amogst violin and boxplot.

```
ggplot(FFood) + aes(x=restaurant, y=total_fat, fill=restaurant) + geom_boxplot() + coord_flip() + guides(fill=FALSE)
```

```{r}
library(patchwork)
ggplot(FFood) + aes(x=restaurant, y=total_fat, fill=restaurant) + geom_boxplot() + coord_flip() + guides(fill=FALSE) + 
ggplot(FFood) + aes(x=restaurant, y=total_fat, fill=restaurant) + geom_violin() + coord_flip() + guides(fill=FALSE) + 
ggplot(FFood) + aes(x=restaurant, y=cholesterol, fill=restaurant) + geom_boxplot() + coord_flip() + guides(fill=FALSE) + 
ggplot(FFood) + aes(x=restaurant, y=cholesterol, fill=restaurant) + geom_violin() + coord_flip() + guides(fill=FALSE)
```

13. In R, let’s construct some summary visualizations.  We will use the piping operator, group_by() and summarise, to plot by chain: (a) average calories and (b) average sodium.

```{r}
library(tidyverse)
( My.Plot <- FFood %>% group_by(restaurant) %>% summarise(calories = mean(calories, na.rm=TRUE)) %>% ggplot(.) + aes(x=reorder(x=restaurant, calories), y=calories) + geom_bar(stat="identity", fill="magenta") + labs(title="Average Calories for Fast Food Chains", x="Chain", y="Average Calories") + theme_light() + coord_flip() )
```

Ok.  Now, something quite fancy.

```{r}
library(plotly)
ggplotly(My.Plot)
```

# A Great Feature, filter grepl

```{r}
# Let's Fix the Chicken Variable
FFood <- FFood %>% mutate(Chicken = grepl('Chicken|Chick-n',item))
FFood$Chicken[FFood$restaurant=="Chick Fil-A"] <- TRUE
```
