---
title: "NYT COVID Forecast Aggregation (Box-Cox)"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)
## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75, fig.retina = 2, dev = "png", dev.args = list(type = "cairo-png"))
library(tidyverse)
library(fpp3)
library(distributional)
library(hrbrthemes)
```

## New York Times Data on COVID

I will grab the dataset from the NYT COVID data github.  I will create two variables, New Cases and New Deaths to model.  The final line use aggregation to create the national data.

```{r DataLoad}
NYT.COVIDN <- read.csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv"))
# Define a tsibble; the date is imported as character so mutate that first.
NYT.COVID <- NYT.COVIDN %>% 
  mutate(date=as.Date(date)) %>% 
  as_tsibble(index=date, key=state) %>% 
  group_by(state) %>% 
  mutate(New.Cases = difference(cases), New.Deaths = difference(deaths)) %>% 
  filter(!(state %in% c("Guam","Puerto Rico", "Virgin Islands","Northern Mariana Islands")))
NYT.COVID <- NYT.COVID %>% mutate(New.Cases = (New.Cases >= 0)*New.Cases, New.Deaths = (New.Deaths >= 0)*New.Deaths)
NYTAgg.COVID <- NYT.COVID %>% 
  aggregate_key(state, New.Cases = sum(New.Cases, na.rm=TRUE), New.Deaths = sum(New.Deaths, na.rm=TRUE)) %>% 
  filter(date > as.Date("2020-03-31")) %>% 
  mutate(Day.of.Week = as.factor(wday(date, label = TRUE)))
lambdaC <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>%
  features(New.Cases, features = guerrero) %>%
  pull(lambda_guerrero)
P1 <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>%
  autoplot(New.Cases)
P2 <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>%
  autoplot(box_cox(New.Cases, lambdaC)) + labs(y="Box-Cox(New.Cases)")
library(patchwork)
P1 / P2
```

The $\lambda$ for deaths...

```{r DBC}
lambdaD <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>%
  features(New.Deaths, features = guerrero) %>%
  pull(lambda_guerrero)
P1 <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>%
  autoplot(New.Deaths)
P2 <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>%
  autoplot(box_cox(New.Deaths, lambdaD)) + labs(y="Box-Cox(New.Deaths)")
library(patchwork)
P1 / P2
```

Plot the two aggregates.

```{r BasePlotA}
plot1 <- NYTAgg.COVID %>% filter(is_aggregated(state))  %>%
  autoplot(box_cox(New.Cases, lambdaC)) + labs(y="Box-Cox(New.Cases)")
plot2 <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>%
  autoplot(box_cox(New.Deaths, lambdaD)) + labs(y="Box-Cox(New.Deaths)")
plot1 / plot2
```

Are there day of week effects?

```{r}
NYTAgg.COVID %>% model(TSLM(box_cox(New.Cases, lambdaC) ~ Day.of.Week)) %>% glance() %>% filter(p_value < 0.05)
```

In 12 states, there appear to be and in a few of them, those effects are large.  Modelling this covariate seems useful.  At the same time, this does nothing about the broad trends.

```{r}
NYTAgg.COVID %>% model(TSLM(box_cox(New.Deaths, lambdaD) ~ Day.of.Week)) %>% glance() %>% filter(p_value < 0.05)
```

## AN STL

```{r}
NYTAgg.COVID %>% 
  filter(is_aggregated(state)) %>% 
  model(STLC = STL(box_cox(New.Cases, lambdaC) ~ trend(window = 14) + season(window = 21), robust = TRUE)) %>%
  components() %>%
  autoplot()
```

```{r}
NYTAgg.COVID %>% 
  filter(is_aggregated(state)) %>% 
  model(STLC = STL(box_cox(New.Deaths, lambdaD) ~ trend(window = 14) + season(window = 21), robust = TRUE)) %>%
  components() %>%
  autoplot()
```


## Training and Testing

That gives me the data that I want; now let me slice it up into training and test sets.  

```{r TestTrain}
COVID.Agg.Test <- NYTAgg.COVID %>% 
  as_tibble() %>% 
  group_by(state) %>% 
  filter(date > as.Date("2021-03-31")) %>% 
  ungroup() %>% 
  as_tsibble(index=date, key=state)
COVID.Agg.Train <- anti_join(NYTAgg.COVID, COVID.Agg.Test)  %>%
  as_tsibble(index=date, key=state)
```

## Model Fitting

Fit some models to the data.

```{r ModelEstC}
COVID.Models <- COVID.Agg.Train %>% filter(is_aggregated(state)) %>% model(
  `K = 2` = ARIMA(box_cox(New.Cases, lambdaC) ~ fourier(K=2) + PDQ(0,0,0)),
  ARIMA = ARIMA(box_cox(New.Cases, lambdaC)),
  ETS = ETS(box_cox(New.Cases, lambdaC)),
  NNET = NNETAR(box_cox(New.Cases, lambdaC)),
  NNETX = NNETAR(box_cox(New.Cases, lambdaC)~Day.of.Week),
  ARIMAX = ARIMA(box_cox(New.Cases, lambdaC)~Day.of.Week),
  ETSlog = ETS(log(New.Cases+1)),
  ETSLevel = ETS(New.Cases)
  ) %>% 
  mutate(Combo1 = (`K = 2` + ARIMA + ETS)/3, Combo2 = (`K = 2` + ARIMA + ETS + NNET)/4, Combo3 = (NNETX + ARIMAX) / 2, Combo4 = (ARIMAX + ETS) / 2, Combo5 = (ETS + ETSlog + ETSLevel) / 3)
```

Forecast the models.

```{r FCaster}
COVIDFC <- COVID.Models %>% filter(is_aggregated(state)) %>%
  forecast(h=14, new_data=COVID.Agg.Test)
```

```{r AccFD}
COVIDFC %>% filter(is_aggregated(state)) %>%
  accuracy(COVID.Agg.Test %>% filter(is_aggregated(state)))
```

Look at the aggregates.

```{r AggFD}
COVIDFC %>% 
  filter(is_aggregated(state)) %>% 
  autoplot(NYTAgg.COVID %>% filter(date > as.Date("2021-03-01")), level=NULL)
```

## Plot the Winner

```{r}
COVIDFC %>% 
  filter(is_aggregated(state) & .model=="ETS") %>% 
  autoplot(NYTAgg.COVID %>% filter(is_aggregated(state) & date > as.Date("2021-03-01")))
```

## Assess the Winner

```{r}
COVID.Models %>% select(ETS) %>% augment() %>% ACF(.resid) %>% autoplot()
```

## The Median Forecast?

```{r}
COVID.Model.ETS <- COVID.Agg.Train %>% filter(is_aggregated(state)) %>% model(ETS = ETS(New.Cases))
Med.FC <- COVID.Model.ETS %>% forecast(h=14, point_forecast = list(.median = median), simulate=TRUE, bootstrap = TRUE, times=10000)
Med.FC %>% accuracy(COVID.Agg.Test)
```

```{r}
Med.FC %>% autoplot(NYTAgg.COVID %>% filter(date > as.Date("2021-03-01")))
```

## What Does the Future Hold?

```{r}
ETSFA <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>% model(ETS = ETS(New.Cases)) %>% forecast(h=14, point_forecast = list(.median = median), simulate=TRUE, bootstrap = TRUE, times=10000)
ETSFA %>% autoplot(NYTAgg.COVID %>% filter(date > as.Date("2021-03-01")))
```

# Deaths

```{r ModelEstD}
COVID.ModelsD <- COVID.Agg.Train %>% filter(is_aggregated(state)) %>% model(
  `K = 2` = ARIMA(box_cox(New.Deaths, lambdaD) ~ fourier(K=2) + PDQ(0,0,0)),
  ARIMA = ARIMA(box_cox(New.Deaths, lambdaD)),
  ETS = ETS(box_cox(New.Deaths, lambdaD)),
  NNET = NNETAR(box_cox(New.Deaths, lambdaD)),
  NNETX = NNETAR(box_cox(New.Deaths, lambdaD)~Day.of.Week),
  ARIMAX = ARIMA(box_cox(New.Deaths, lambdaD)~Day.of.Week),
  ETSlog = ETS(log(New.Deaths+1)),
  ETSLevel = ETS(New.Deaths)
  ) %>% 
  mutate(Combo1 = (`K = 2` + ARIMA + ETS)/3, Combo2 = (`K = 2` + ARIMA + ETS + NNET)/4, Combo3 = (NNETX + ARIMAX) / 2, Combo4 = (ARIMAX + ETS) / 2, Combo5 = (ETS + ETSlog + ETSLevel) / 3)
```

Forecast the models.

```{r FCasterD}
COVIDFCD <- COVID.ModelsD %>% filter(is_aggregated(state)) %>%
  forecast(h=14, new_data=COVID.Agg.Test)
```


```{r AccFD1}
COVIDFCD %>% filter(is_aggregated(state)) %>%
  accuracy(COVID.Agg.Test %>% filter(is_aggregated(state)))
```

Look at the aggregates.

```{r AggFD2}
COVIDFCD %>% 
  filter(is_aggregated(state)) %>% 
  autoplot(NYTAgg.COVID %>% filter(date > as.Date("2021-03-01")), level=NULL)
```
## Diagnostics

```{r}
COVID.ModelsD %>% select(ARIMAX) %>% report()
```


```{r}
COVID.ModelsD %>% select(ARIMAX) %>% augment() %>% gg_tsdisplay(.resid)
```



## Plot the Winner

```{r}
COVIDFCD %>% 
  filter(is_aggregated(state) & .model=="ARIMAX") %>% 
  autoplot(NYTAgg.COVID %>% filter(is_aggregated(state) & date > as.Date("2021-03-01")))
```

## The Median Forecast?

```{r}
COVID.Model.ARIMAX <- COVID.Agg.Train %>% filter(is_aggregated(state)) %>% model(ARIMAX = ARIMA(box_cox(New.Deaths, lambdaD)~Day.of.Week))
Med.D.FC <- COVID.Model.ARIMAX %>% forecast(new_data=COVID.Agg.Test, point_forecast = list(.median = median), simulate=TRUE, bootstrap = TRUE, times=10000)
Med.D.FC %>% accuracy(COVID.Agg.Test)
```

## The Future

```{r}
Day.of.Week <- data.frame(date = Sys.Date() + days(0:13)) %>% mutate(Day.of.Week=wday(as.Date(date), label = TRUE)) %>% as_tsibble(., index=date)
AggD <- NYTAgg.COVID %>% filter(is_aggregated(state)) %>% as_tsibble(., index=date, key=NULL)
FutureFC <- AggD %>% model(ARIMAX = ARIMA(box_cox(New.Deaths, lambdaD)~Day.of.Week)) %>% forecast(new_data=Day.of.Week, point_forecast = list(.median = median), simulate=TRUE, bootstrap = TRUE, times=10000)
FutureFC %>% autoplot(AggD)
```

